---
title: "Congressional Incumbency in the Early Republic"
author: "Jordan F. Bratt"
year: "2018"
output:
  html_document:
    theme: default
  md_document:
    variant: markdown
always_allow_html: yes
layout: essay
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(mappingelections)
library(dplyr)
library(readr)
library(ggplot2)
library(stringr)
library(broom)
library(maptools)
library(knitr)
library(scales)
```

The issue of congressional turnover provides important insights into the
nature of political representation in Congress. Turnover measures the
number of representatives who fail to return to the next session of
Congress, either through a failure to be reelected or voluntary
retirement from office. Turnover has changed dramatically over time. In
recent Congresses, no more than ten percent of the membership has left,
or been replaced, during a typical election cycle. In one recent
Congress---the 115th, elected in 2016---only three percent of the
sitting members of Congress failed to be reelected. (In other words, 380
of the 393 members who sought reelection were successful.) In the early
Congresses, however, thirty percent or more of the membership typically
failed to return to their seat in the next Congress.

Another way to think about turnover is through the concept of
incumbency. Incumbency measures the percentage of members who remain in
office rather than the proportion of those who rotate out of office.
Incumbency can take two different forms: *party* incumbency and
*legislator* incumbency. The primary difference is between what is
measured. Whereas "legislator" incumbency focuses on whether or not a
*particular individual* remains in office, "party" incumbency focuses on
which *political party* remains in office, even if specific
representatives themselves are different. This approach has the
advantage of highlighting the persistence of particular parties in
various geographic regions. The Mapping Early American Elections (MEAE)
project provides a nuanced lens through which to explore reelection and
incumbency during the nation's formative years.

In the early republic, the political scene was quite different from that
of today. State legislators elected the Senate. Either state legislators
or the voters in a state elected the presidential electors who, in turn,
elected the president. The House of Representatives was the only part of
the federal government in which officials were directly elected by the
people. The first Congress in 1789 met in New York City; the Second
Congress, in Philadelphia. Then, in the 1801, the federal government
moved from Philadelphia to the newly built capital in Washington D.C.
The new federal city did not offer the comfortable services, amenities,
and cultural life that Philadelphia and New York City had provided. Even
more important, Congress met at a far distance from where most Americans
lived. Representatives had to spend long periods of time away from their
families and homes while Congress was in session. This isolation put a
strain on marriages, family relationships, and personal finances,
contributing to a high rate of voluntary retirements. In fact, about
one-third of those who did not return to the next Congress had done so
not because they had failed to be reelected, but because they chose to
leave their seat voluntarily. Serving in Congress thus often imposed
extreme burdens on the members of Congress as well as their families.

The framers of the Constitution did not include a provision establishing
a mandatory rotation in office for members of Congress. What may appear
to be a critical oversight was more accurately a point of debate. James
Madison, George Mason, and Thomas Jefferson supported such a provision
and many state constitutions included mandatory rotation of office for
their governors and legislatures. However, those who opposed the
provision thought that the weaknesses of the Articles of Confederation
highlighted the need for a stronger federal government, one in which
those elected did so on their merit and reputation. In the end, instead
of dictating how many terms members of Congress could serve, they left
it to the voters to decide who should be elected or reelected. The
framers did not, however, anticipate the emergence of political parties.

The emergence of political parties meant that voters could elect members
to Congress from the same political party (who presumably shared similar
basic party ideology), while electing different individuals to serve in
that position. The MEAE project enables us to visually track party
incumbency, or party persistence, over time. For example, beginning in
the 3rd Congress, Maryland's 1st, 3rd, and 8th districts (representing
the southern and western part of the state) continued to reelect
Federalists until the 18th Congress. During this time span, although
sixteen different candidates were elected, all were members of the
Federalist party in some form. Similarly, Maryland's 5th district,
encompassing the city of Baltimore and the surrounding area, remained
solidly Democratic-Republican. Maryland's remaining districts oscillated
between Federalist and Democratic-Republican. This persistence of these
patterns of incumbency highlight the regional differences within the
state as well as demonstrate the differences between an urban center and
more rural counties.

While career or professional politicians did not exist in the early
years of the country, there were a number of individuals who maintained
a sustained tenure in Congress. Thomas Newton Jr. of Virginia served as
a Representative from the 7th--22nd Congresses. (Note, however, that
MEAE has election data only for the 7th--19th Congresses.) Representing
the area surrounding Norfolk, Newton remained a popular candidate,
winning the majority of his elections in landslides. Even more
surprising is Newton's support of John Quincy Adams in the hotly
contested 1824 Presidential election. Newton represented one of only
seven Adams-Clay supporters in his entire state. Another Virginia
representative who had a long career was John Randolph who served in
twelve Congresses from 1800 to 1827. Randolph is of particular interest
because his party allegiance changes over the course of his political
life. Initially a Democratic-Republican, Randolph split from the party
and joined coalition of politicians known as Tertium Quids for
Congresses 9--12. Twice he ran unopposed, even after becoming a Tertium
Quid. Newton and Randolph represent a large group of incumbents who
continued to be reelected and maintained their voice and influence
within Congress over long periods of time.

Unopposed reelections represent an intriguing subsection of incumbency
in the early republic. Of all the congressional elections in the MEAE
dataset, 322 or twelve percent are unopposed elections. 160 of those
elections represent unopposed incumbents. William A. Burwell of Virginia
participated in the most unopposed elections, winning a seat in the 10th
through the 16th Congresses. Burwell was hardly the exception for
Virginia. Nine of the top fifteen representatives with the most
unopposed elections were from the state of Virginia accounting for
fifty-nine percent of the total 75 elections among them. Virginia
accounted for the most unopposed elections and the majority of unopposed
elections took place in the South (Virginia, Kentucky, South Carolina,
and North Carolina). The prevalence of unopposed incumbents in Virginia
illustrates both the district-wide support for the individual, as well
as the political clout such a person wielded. These elections also
reflect the persistence of an older form of deferential politics that
was quickly becoming obsolete in a democratizing nation.

Both in the early republic and today, high turnover can result from a
number of causes. Voters may turn their representatives out of office at
a high rate because of dissatisfaction with their member's views or
character, or from a desire to have a fresh face in Congress.
Alternatively, high turnover may result from representatives themselves
refusing to seek reelection, either because they fear losing their seat,
desire to remain at home with their families, or choose to seek other
political or economic opportunities. Turnover can be a healthy
development, by bringing new members to Congress who revitalize the
institution. Turnover can also be disadvantageous because it removes
experienced members from Congress, thus depriving the institution of
their knowledge and expertise. Despite the lack of formal restriction on
congressional terms, high turnover in the early congresses produced a
kind of de facto rotation in office during the new republic's first
decades. At the same time, incumbency rates tell a slightly different
story. During the first decades of the new nation, incumbency rates
reveal how and when different regions of the country, and different
areas within the states, chose to support one party or the other. The
maps in the MEAE project reveal the shifting fates of the Federalists
and Democratic-Republicans as well as emergence at different times of
splinter factions and new political parties. These maps then, illustrate
the story of the country's complex and uneven path toward a two-party
political system.

```{r}
candidates <- meae_congress_candidate_totals %>%
  mutate(state = substr(meae_id, 31, 32),
         congress = substr(meae_id, 28, 29) %>% as.numeric())
```

Table illustrating the incumbency/elections for Delaware
```{r}
#DE Incumbency Table
incumbent <- candidates %>%
  filter(state == "de",
         winner == TRUE) %>%
  select(congress, candidate, candidate_id, winner)  %>%
  spread(congress, winner)

kable(incumbent)
```

Thomas Newton Jr. incumbency graph

```{r, echo=FALSE, warning=FALSE}

newton_elections <- candidates %>% 
  filter(candidate_id == "NT0024") %>% 
  select (election_id)

newton_competition <- newton_elections %>%
  inner_join(candidates, by=c("election_id" = "election_id")) 

newton_remove <- newton_competition %>%
  filter(is.na(percent_vote),
         candidate_id != "NT0024")

newton_elect <- newton_competition %>%
  anti_join(newton_remove, by=c("election_id", "candidate_id"))

newton_elect$percent_vote[is.na(newton_elect$percent_vote)] <- 1


newton_elect <- newton_elect %>% 
  filter(election_id != "va.uscongress.8.1789",
         candidate != "scattering",
         percent_vote >= .10)

newton_elect$percent_vote[9] <- NA
newton_elect$percent_vote[16] <- NA

newton_elect %>%
  ggplot(aes(x = congress, y = percent_vote * 100, color = candidate_id))+
  geom_point(size = 2)+
  geom_line()+
  geom_hline(aes(yintercept=50))+
  scale_x_continuous(name="Congress", breaks = c(7, 9, 11, 13, 15, 17, 19))+
  scale_y_continuous(name="Percent of popular vote", breaks=c(40, 50, 60, 70, 80, 90, 100))+
  scale_colour_discrete(name = "Candidates", breaks=c("NT0024", "PJ0725", "TR0086", "WS0229"), labels=c("Thomas Newton, Jr.", "Josiah Parker", "Robert B. Tayler", "Swepson Whitehead"))+
  labs(title="The elections of Thomas Newton, Jr.", y = "Percent of the vote", x = 'Congress', colour = "Candidates")

```

Visualization of unopposed incumbent elections by state

```{r, echo=FALSE}

total_elections <- candidates %>%
  count(candidate_id)

total_elect_candidates <- candidates %>%
  inner_join(total_elections, by=c("candidate_id"="candidate_id"))

#colnames(total_elect_candidates)[14] <- "total_election"

total_elect_candidates <- total_elect_candidates%>%
  filter(winner==TRUE)

unopposed_candidates <- total_elect_candidates %>%
  count(candidate_id) %>%
  filter(nn>=2)

unopposed_incumbents <-unopposed_candidates %>%
  inner_join(total_elect_candidates, by=c("candidate_id" = "candidate_id"))

#colnames(unopposed_incumbents)[2] <- "total_unopposed"

test <- unopposed_incumbents %>%
  group_by(candidate_id) %>%
  mutate(incumbent = congress - lag(congress))

unopposed_inc<- test %>%
  filter(incumbent == 1,
         unopposed == TRUE)

state_unopposed <- unopposed_inc %>%
  ungroup() %>%
  count(state)

state_unopposed <- state_unopposed %>%
  mutate(state = str_to_upper(state)) %>% 
  mutate(total_unopposed_percent = as.double((nnn/240) * 100))

states_1825 <- us_states("1825-01-01")

unopposed_map <- states_1825 %>%
  left_join(state_unopposed, by=c("state_abbr" = "state"))

unopposed_map <- unopposed_map %>%
  filter(terr_type != "Territory",
         terr_type != "Unorganized Territory",
         terr_type != "Other")


#classInt::classIntervals(var = unopposed_map$total_unopposed_percent, n = 4, style = "jenks")

breaks <- c(0, 0.5, 3, 6, 14, 48)
labels <- c("[0.0 - 0.5%]", "[0.5 - 3.0%]", "[3.0 - 6.0%]", "[6.0 - 14.0%]", "[47.1%]")

unopposed_map$breaks <- cut(unopposed_map$total_unopposed_percent, breaks = breaks, labels = labels)

ggplot() +
  geom_sf(data = unopposed_map,
           aes(fill = breaks),
           color = "black", size = 0.25)+
  coord_sf(crs = "+proj=aea +lat_1=25 +lat_2=50 +lon_0=-100")+
  scale_fill_brewer("Percent of Elections", palette = "YlGnBu", na.value = "white")+
  labs(title = "Unopposed Incumbent Elections (1789-1825)", fill = "Percent of Unopposed Elections")+
  theme(plot.title = element_text(size=14, family = "Georgia"))

```
