---
meae-id: meae.congressional.congress18.al.county
type: congressional
level: state
state: Alabama
geography: county
congressnum: 18
congressordinal: 18th
title: '18th Congress: Alabama 1823'
year: 1823
legend: congress-18-19
nnv:
- id: al.uscongress.1.1823
  name: AL US Congress 1823 District 1
- id: al.uscongress.2.1823
  name: AL US Congress 1823 District 2
- id: al.uscongress.3.1823
  name: AL US Congress 1823 District 3
related-maps:
- id: meae.congressional.congress17.al.county
  name: AL 17th Congress
  type: previous
- id: meae.congressional.congress19.al.county
  name: AL 19th Congress
  type: next
- id: meae.congressional.congress18.national.county
  name: National 18th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress18.al.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  filter (id != "als_nca6",
          id != "als_nca7",
          id != "als_nca8",
          id != "als_nca9",
          id != "als_nca11",
          id != "als_nca12",
          id != "als_nca13") %>% 
  map_counties()
```

</div>

Alabama elected three Democratic-Republicans to the Eighteenth Congress. All three of the Democratic-Republicans were part of a faction led by Andrew Jackson.

The map for this election is incomplete due to the lack of returns in several counties.

Following the 1820 Census, Alabama gained 2 more seats in the House of Representatives.

Alabama used a statewide at-large system for electing members to Congress. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
