---
meae-id: meae.congressional.congress14.ky.county
type: congressional
level: state
state: Kentucky
geography: county
congressnum: 14
congressordinal: 14th
title: '14th Congress: Kentucky 1814'
year: 1814
legend: fed-vs-rep
nnv:
- id: ky.uscongress1.1814
  name: KY US Congress 1814 District 1
- id: ky.uscongress2.1814
  name: KY US Congress 1814 District 2
- id: ky.uscongress3.1814
  name: KY US Congress 1814 District 3
- id: ky.uscongress4.1814
  name: KY US Congress 1814 District 4
- id: ky.uscongress5.1814
  name: KY US Congress 1814 District 5
- id: ky.uscongress6.1814
  name: KY US Congress 1814 District 6
- id: ky.uscongress7.1814
  name: KY US Congress 1814 District 7
- id: ky.uscongress8.1814
  name: KY US Congress 1814 District 8
- id: ky.uscongress9.1814
  name: KY US Congress 1814 District 9
- id: ky.uscongress10.1814
  name: KY US Congress 1814 District 10
related-maps:
- id: meae.congressional.congress13.ky.county
  name: KY 13th Congress
  type: previous
- id: meae.congressional.congress15.ky.county
  name: KY 15th Congress
  type: next
- id: meae.congressional.congress14.national.county
  name: National 14th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress14.ky.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Kentucky elected ten Democratic-Republicans to the Fourteenth Congress.

The map for this election is incomplete due to the lack of returns at the town or county level.

Kentucky used a district system for electing members to Congress. 

In 1815, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ky.uscongress2.special.1815) was held to confirm the legality of Henry Clay’s election to the the Fourteenth Congress, as he was serving as a foreign minster during the regular election. Clay’s election was confirmed without opposition.

In 1816, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ky.specialuscongress1.1816) was held in which Thomas Fletcher was elected to replace James Clarke, who had resigned. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
