---
meae-id: meae.congressional.congress11.pa.county
type: congressional
level: state
state: Pennsylvania
geography: county
congressnum: 11
congressordinal: 11th
title: '11th Congress: Pennsylvania 1808'
year: 1808
legend: fed-vs-rep
nnv:
- id: pa.uscongress1.1808
  name: PA US Congress 1808 District 1
- id: pa.uscongress2.1808
  name: PA US Congress 1808 District 2
- id: pa.uscongress3.1808
  name: PA US Congress 1808 District 3
- id: pa.uscongress4.1808
  name: PA US Congress 1808 District 4
- id: pa.uscongress5.1808
  name: PA US Congress 1808 District 5
- id: pa.uscongress6.1808
  name: PA US Congress 1808 District 6
- id: pa.uscongress7.1808
  name: PA US Congress 1808 District 7
- id: pa.uscongress8.1808
  name: PA US Congress 1808 District 8
- id: pa.uscongress9.1808
  name: PA US Congress 1808 District 9
- id: pa.uscongress10.1808
  name: PA US Congress 1808 District 10
- id: pa.uscongress11.1808
  name: PA US Congress 1808 District 11
related-maps:
- id: meae.congressional.congress10.pa.county
  name: PA 10th Congress
  type: previous
- id: meae.congressional.congress12.pa.county
  name: PA 12th Congress
  type: next
#- id: meae.congressional.congress11.national.district
#  name: National 11th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress11.pa.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~federalist_vote, ~demrep_vote,
    "Philadelphia", 39.9526, -75.1652, 0.48, 0.52, 8124, 8800)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
 map_counties(height = "500px", cities = 0, congress = 11) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1<br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city) 
```

</div>

Pennsylvania elected six Federalists and twelve Democratic-Republicans to the Eleventh Congress.

The map for this election is incomplete due to the lack of returns in some areas.

Pennsylvania used the district system for electing members to Congress. Districts 1, 2, and 3 each elected three representatives. District 4 elected two representatives.

In 1809, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress1.specialelection.1809) was held in which Democratic-Republican Adam Seybert was elected to replace Benjamin Say, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
