---
meae-id: meae.congressional.congress01.ct.county
type: congressional
level: state
state: Connecticut
geography: county
congressnum: 1
congressordinal: 1st
title: '1st Congress: Connecticut 1788'
year: 1788
legend: fed-vs-anti
related-maps:
- id: meae.congressional.congress02.ct.county
  name: CT 2nd Congress
  type: next
# - id: meae.congressional.congress01.national.district
#   name: National 1st Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)
library(sf)

map_id <- "meae.congressional.congress01.ct.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>% 
  filter(id != "cts_wr") %>% 
  map_counties(height = "350px", congress = 1)
```

</div>

Connecticut elected five Federalists to the First Congress.

While no county- or town-level returns survive, the map depicts the state a solidly Federalist, since only Federalists were nominated for the First Congress.

Connecticut used a state-wide at-large system to elect members of Congress. Connecticut had a two-tiered system of election. A nomination election was held first to establish the congressional candidates. Then a general election was held to decide who would be seated in congress.

In 1790, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ct.special.congress.1790) was held to replace Pierpont Edwards who declined to serve. Jeremiah Wadsworth was elected.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
