---
meae-id: meae.congressional.congress17.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 17
congressordinal: 17th
title: '17th Congress: Delaware 1820'
year: 1820
legend: fed-vs-rep
nnv:
- id: de.uscongress.1820
  name: DE US Congress 1820 At Large
related-maps:
- id: meae.congressional.congress16.de.county
  name: DE 16th Congress
  type: previous
- id: meae.congressional.congress18.de.county
  name: DE 18th Congress
  type: next
- id: meae.congressional.congress17.national.county
  name: National 17th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress17.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Delaware elected one Federalist and one Democratic-Republican to the Seventeenth Congress.

Delaware used a statewide at-large system for electing members to Congress. Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. Two at-large winners were elected.

In 1822, a [special election](https://elections.lib.tufts.edu/catalog/tufts:de.uscongressspecial.1822) was held in which Daniel Rodney was elected to replace Caesar A. Rodney, who had resigned after being elected to the United States Senate.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
