---
meae-id: meae.staterepresentative.1808.md.county
type: state-rep
level: state
state: Maryland
geography: county
title: 'Maryland House of Delegates, 1808'
year: 1808
legend: fed-vs-rep
nnv:
- id: md.assembly.allegany.county.1808
  name: MD House of Delegates 1808, Allegany County 
- id: md.assembly.annapolis.city.1808
  name: MD House of Delegates 1808, City of Annapolis
- id: md.assembly.anne.arundel.county.1808
  name: MD House of Delegates 1808, Anne Arundel County
- id: md.assembly.baltimore.city.1808
  name: MD House of Delegates 1808, City of Baltimore
- id: md.assembly.baltimore.county.1808
  name: MD House of Delegates 1808, Baltimore County
- id: md.assembly.calvert.county.1808
  name: MD House of Delegates 1808, Calvert County
- id: md.assembly.caroline.county.1808
  name: MD House of Delegates 1808, Caroline County
- id: md.assembly.cecil.county.1808
  name: MD House of Delegates 1808, Cecil County 
- id: md.assembly.charles.county.1808
  name: MD House of Delegates 1808, Charles County
- id: md.assembly.dorchester.county.1808
  name: MD House of Delegates 1808, Dorchester County 
- id: md.assembly.frederick.county.1808
  name: MD House of Delegates 1808, Frederick County
- id: md.assembly.harford.county.1808
  name: MD House of Delegates 1808, Harford County
- id: md.assembly.kent.county.1808
  name: MD House of Delegates 1808, Kent County
- id: md.assembly.montgomery.county.1808
  name: MD House of Delegates 1808, Montgomery County
- id: md.assembly.prince.georges.county.1808
  name: MD House of Delegates 1808, Prince George's County
- id: md.assembly.queen.annes.county.1808
  name: MD House of Delegates 1808, Queen Anne's County
- id: md.assembly.saint.mary.county.1808
  name: MD House of Delegates 1808, Saint Mary's County
- id: md.assembly.somerset.county.1808
  name: MD House of Delegates 1808, Somerset County
- id: md.assembly.talbot.county.1808
  name: MD House of Delegates 1808, Talbot County
- id: md.assembly.washington.county.1808
  name: MD House of Delegates 1808, Washington County
- id: md.assembly.worcester.county.1808
  name: MD House of Delegates 1808, Worcester County
related-maps:
- id: meae.congressional.congress11.md.county
  name: MD 11th Congress
  type: congressional
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.staterepresentative.1808.md.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~federalist_vote, ~demrep_vote,
  "Baltimore", 39.30021, -76.61052, 0.197, 0.803, 1620, 6596,
  "Annapolis", 38.9784, -76.4922, 0.267, 0.733, 110, 302)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_staterep_map_data(state = "MD", election_date = "1808-10-01") %>%
  map_counties(height = "450px", cities = FALSE) %>%
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                   fillColor = mappingelections:::poli_chrome(cities),
                   opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                   popup = ~paste0("<b>City of ", city, "</b><br/>",
                                   "Federalists: ", federalist_percentage * 100, "% (", 
                                   prettyNum(federalist_vote, big.mark = ","), 
                                   " votes)<br/>",
                                   "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                   label = ~city) 
```

</div>

In 1808, Maryland elected eighty representatives to the state’s House of Delegates. At least thirty-nine of them were Federalists, and at least thirty-six of them were Democratic-Republicans.

Maryland had three legislative bodies: The House of Delegates, which was elected annually in October and had eighty members; a State Senate, comprised of fifteen members, chosen every five years in early September; and a Governor’s Council made up of five members chosen yearly by the Legislature. 

Members of Maryland’s House of Delegates were chosen through popular elections.
Each of Maryland’s nineteen counties elected four members using a county-level at-large method. Annapolis and the City of Baltimore each elected two members. 

After losing control of the state legislature in the 1801 to the Democratic-Republicans, the Federalists recaptured the Maryland House of Delegates with the 1808 election. Maryland’s election for the [Eleventh U.S. Congress](http://earlyamericanelections.org/maps/meae.congressional.congress11.md.county.html) was also held the same year, and shows similar party voting patterns. In both elections, Federalists received a majority of the vote in the southern and Potomac areas of the state, while the Democratic-Republicans received a greater majority of the vote in the upper Chesapeake and eastern shore. However, because Maryland used a district system for Congressional elections and a county-level at-large method for state legislative elections, the results of the two contests were dramatically different.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results_state_rep() %>%
  results_to_table_state_rep() %>%
  cat()
```

</div>
