---
meae-id: meae.congressional.congress03.sc.county
type: congressional
level: state
state: South Carolina
geography: county
congressnum: 3
congressordinal: 3rd
title: '3rd Congress: South Carolina 1793'
year: 1793
legend: fed-vs-anti
nnv:
- id: sc.uscongress.district1.1793
  name: SC US Congress 1793 District 1
- id: sc.uscongress.district2.1793
  name: SC US Congress 1793 District 2
- id: sc.uscongress.district3.1793
  name: SC US Congress 1793 District 3
- id: sc.uscongress.district4.1793
  name: SC US Congress 1793 District 4
- id: sc.uscongress.district5.1793
  name: SC US Congress 1793 District 5
- id: sc.uscongress.district6.1793
  name: SC US Congress 1793 District 6
related-maps:
- id: meae.congressional.congress02.sc.county
  name: SC 2nd Congress
  type: previous
- id: meae.congressional.congress04.sc.county
  name: SC 4th Congress
  type: next
# - id: meae.congressional.congress03.national.district
#   name: National 3rd Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress03.sc.county"
cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~other_percentage, ~federalist_vote, ~other_vote,
  "Charleston", 32.7765, -79.9311, 0.754, 0.246, 362, 118)

```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>% 
  map_counties(congress = 3, height = "600px", cities = FALSE) %>% 
 addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1<br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Unaffiliated or other parties: ", other_percentage * 100,
                                 "% (", 
                                 prettyNum(other_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city) 

```

</div>

South Carolina elected one Federalist and five Anti-Federalists to the Third Congress. John Hunter was a Federalist elector for president in 1792, but in 1796 he was elected a Democratic-Republican to the U.S. Senate.

South Carolina used a district system for electing members to Congress. Following the 1790 Census, South Carolina gained a seat in the House of Representatives. After Alexander Gillon died, a [special election](https://elections.lib.tufts.edu/catalog/tufts:sc.uscongress.district2.1794) was held in which Robert G. Harper was elected to replace him.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
