---
meae-id: meae.staterepresentative.1817.md.county
type: state-rep
level: state
state: Maryland
geography: county
title: 'Maryland House of Delegates, 1817'
year: 1817
legend: fed-vs-rep
nnv:
- id: md.assembly.annapolis.city.1817
  name: MD House of Delegates 1817, City of Annapolis
- id: md.assembly.baltimore.city.1817
  name: MD House of Delegates 1817, City of Baltimore
- id: md.assembly.baltimore.county.1817
  name: MD House of Delegates 1817, Baltimore County
- id: md.assembly.calvert.county.1817
  name: MD House of Delegates 1817, Calvert County
- id: md.assembly.caroline.county.1817
  name: MD House of Delegates 1817, Caroline County
- id: md.assembly.cecil.county.1817
  name: MD House of Delegates 1817, Cecil County 
- id: md.assembly.dorchester.county.1817
  name: MD House of Delegates 1817, Dorchester County 
- id: md.assembly.frederick.county.1817
  name: MD House of Delegates 1817, Frederick County
- id: md.assembly.harford.county.1817
  name: MD House of Delegates 1817, Harford County
- id: md.assembly.kent.county.1817
  name: MD House of Delegates 1817, Kent County
- id: md.assembly.somerset.county.1817
  name: MD House of Delegates 1817, Somerset County
- id: md.assembly.talbot.county.1817
  name: MD House of Delegates 1817, Talbot County
related-maps:
- id: meae.staterepresentative.1818.md.county
  name: MD 1818 House of Delegates
  type: next
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.staterepresentative.1817.md.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~federalist_vote, ~demrep_vote,
  "Baltimore", 39.30021, -76.61052, 0, 1.0, "No reported", "No reported",
  "Annapolis", 38.9784, -76.4922, 0.289, 0.711, 101, 249)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_staterep_map_data(state = "MD", election_date = "1817-10-01") %>%
  map_counties(height = "450px", cities = FALSE) %>%
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                   fillColor = mappingelections:::poli_chrome(cities),
                   opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                   popup = ~paste0("<b>City of ", city, "</b><br/>",
                                   "Federalists: ", federalist_percentage * 100, "% (", 
                                   prettyNum(federalist_vote, big.mark = ","), 
                                   " votes)<br/>",
                                   "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                   label = ~city) 
```

</div>

In 1817, Maryland elected eighty representatives to the state’s House of Delegates. At least nine of them were Federalists, and at least twenty of them were Democratic-Republicans.

The map for this election is incomplete due to the lack of returns at the county level.

Members of Maryland’s House of Delegates were chosen through popular elections.
Each of Maryland’s nineteen counties elected four members using a county-level at-large method. Annapolis and the City of Baltimore each elected two members. 

Maryland had three legislative bodies: The House of Delegates, which was elected annually in October and had eighty members; a State Senate, comprised of fifteen members, chosen every five years in early September; and a Governor’s Council made up of five members chosen yearly by the Legislature. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results_state_rep() %>%
  results_to_table_state_rep() %>%
  cat()
```

</div>
