---
meae-id: meae.congressional.congress01.ny.county
type: congressional
level: state
state: New York
geography: county
congressnum: 1
congressordinal: 1st
title: '1st Congress: New York 1789'
year: 1789
legend: fed-vs-anti
nnv:
- id: ny.uscongress1.1789
  name: NY US Congress 1789 District 1
- id: ny.uscongress2.1789
  name: NY US Congress 1789 District 2
- id: ny.uscongress3.1789
  name: NY US Congress 1789 District 3
- id: ny.uscongress4.1789
  name: NY US Congress 1789 District 4
- id: ny.uscongress5.1789
  name: NY US Congress 1789 District 5
- id: ny.uscongress6.1789
  name: NY US Congress 1789 District 6
related-maps:
- id: meae.congressional.congress02.ny.county
  name: NY 2nd Congress
  type: next
# - id: meae.congressional.congress01.national.district
#   name: National 1st Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress01.ny.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>% 
  get_county_map_data() %>% 
  map_counties(height = "550px")
```

</div>
New Yorkers sent three Federalists and three Anti-Federalists to the First Congress. Support for Federalists and Anti-Federalists appeared to be solidified in election districts closest to New York City. In the first district, Anti-Federalist William Floyd stood unopposed with the support of both Anti-Federalists and Federalists. In the second district, Federalist John Laurence was elected, defeating two Anti-Federalist opponents by a wide margin.


Anti-Federalist Benson Egbert was elected by a margin of just ten votes in the third district. John Hathorn, an Anti-Federalist stood unopposed in the fourth district. In the fifth district--composed of three entire counties and a portion of a fourth--Federalist Peter Sylvester was elected. However, he only carried Columbia County; he lost in the other regions of the district by close margins. In Clinton County, this margin was only thirteen votes. In the sixth district, Anti-Federalist Jeremiah Van Rensselaer was elected.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>% 
  candidate_results() %>% 
  results_to_table() %>% 
  cat()
```

</div>
