---
meae-id: meae.congressional.congress03.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 3
congressordinal: 3rd
title: '3rd Congress: Delaware 1792'
year: 1792
legend: fed-vs-anti
nnv:
- id: de.uscongress.1792
  name: DE US Congress 1792 At Large
related-maps:
- id: meae.congressional.congress02.de.county
  name: DE 2nd Congress
  type: previous
- id: meae.congressional.congress04.de.county
  name: DE 4th Congress
  type: next
- id: meae.congressional.congress03.national.county
  name: National 3rd Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress03.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

After initial returns were counted, Delaware elected John Patten, an Anti-Federalist, to Congress. But the U.S. House of Representatives threw out some irregular votes and seated Henry Lattimer, a Federalist. This map depicts the initial count of votes.

Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. The at-large winner was then declared the winner.  

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
