---
meae-id: meae.congressional.congress06.ma.county
type: congressional
level: state
state: Massachusetts
geography: county
congressnum: 6
congressordinal: 6th
title: '6th Congress: Massachusetts 1798'
year: 1798
legend: fed-vs-rep
nnv:
- id: ma.uscongress.western.1.1798
  name: MA US Congress 1798 District 1
- id: ma.uscongress.western.2.1798
  name: MA US Congress 1798 District 2
- id: ma.uscongress.western.3.1798
  name: MA US Congress 1798 District 3
- id: ma.uscongress.western.4.1798
  name: MA US Congress 1798 District 4
- id: ma.uscongress.southern.1.ballot5.1799
  name: MA US Congress 1799 District 5
- id: ma.uscongress.southern.2.1798
  name: MA US Congress 1798 District 6
- id: ma.uscongress.southern.3.ballot4.1799
  name: MA US Congress 1799 District 7
- id: ma.uscongress.middle.1.1798
  name: MA US Congress 1798 District 8
- id: ma.uscongress.middle.2.1798
  name: MA US Congress 1798 District 9
- id: ma.uscongress.middle.3.1798
  name: MA US Congress 1798 District 10
- id: ma.uscongress.middle.4.1798
  name: MA US Congress 1798 District 11
- id: ma.uscongress.eastern.1.1798
  name: MA US Congress 1798 District 12
- id: ma.uscongress.eastern.2.1798
  name: MA US Congress 1798 District 13
- id: ma.uscongress.eastern.3.1798
  name: MA US Congress 1798 District 14
related-maps:
- id: meae.congressional.congress05.ma.county
  name: MA 5th Congress
  type: previous
- id: meae.congressional.congress07.ma.county
  name: MA 7th Congress
  type: next
# - id: meae.congressional.congress06.national.district
#   name: National 6th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress06.ma.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties() %>% 
  fitBounds(-73.508, 41.186, -69.861, 43.75)
```

</div>

Massachusetts elected twelve Federalists and two Democratic-Republicans to the Sixth Congress.

Massachusetts used the district system for electing members to Congress.

On [August 25, 1800](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.middle.3.special.1800), and [October 20, 1800](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.middle.3.special.ballot2.1800), two special elections were held in which Federalist Nathan Read was elected to replace Samuel Sewall, who had resigned from office on January 10, 1800.

In 1800, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.western.3.special.1800) was held in which Federalist Ebenezer Mattoon was elected to replace Federalist Samuel Lyman, who had resigned from office on November 6, 1800.

Starting in August 1800, three special elections were held after which Democratic-Republican Levi Lincoln replaced Federalist Dwight Foster (listed as "Samuel Foster" in _A New Nation Votes_), who had resigned from the House of Representatives to replace Federalist Samuel Dexter in the Senate: [special election 1](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.western.4.special.1800),
[special election 2](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.western.4.special.ballot2.1800), [special election 3](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.western.4.special.ballot3.1800).

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
