---
title: '5th Congress: Rhode Island 1796'
congressnum: 5
congressordinal: 5th
output:
  html_document:
    theme: default
  md_document:
    variant: markdown
layout: maps-show
legend: fed-vs-rep
level: state
meae-id: meae.congressional.congress05.ri.county
nnv:
- id: ri.uscongress.firstcongressmen.1796
  name: RI US Congress 1796 Ticket 1
- id: ri.uscongress.secondcongressmen.1796
  name: RI US Congress 1796 Ticket 2
geography: county
related-maps:
- id: meae.congressional.congress04.ri.county
  name: RI 4th Congress
  type: previous
- id: meae.congressional.congress06.ri.county
  name: RI 6th Congress
  type: next
# - id: meae.congressional.congress05.national.district
#   name: National 5th Congress
#   type: national
state: Rhode Island
always_allow_html: yes
type: congressional
year: 1796
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress05.ri.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>% 
  map_counties(height = "300px", congress = 5)
```

</div>

Rhode Island elected two Federalists to the Fifth Congress. 

Rhode Island used a statewide at-large method for electing members to Congress, though each of the two representatives were elected on separate tickets. The candidates for the two different tickets are distinguished below in the district column.

Benjamin Bourne would resign before taking his seat in Congress and a [special election](https://elections.lib.tufts.edu/catalog/tufts:ri.uscongress.specialelection.1796) would elect Elisha R. Potter to fill his seat.

In 1797, Rhode Island held a [special election](https://elections.lib.tufts.edu/catalog/tufts:ri.uscongress1.1797) in which Thomas Tillinghast replaced Elisha R. Potter, who resigned his seat.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
