---
meae-id: meae.congressional.congress18.nj.county
type: congressional
level: state
state: New Jersey
geography: county
congressnum: 18
congressordinal: 18th
title: '18th Congress: New Jersey 1822'
year: 1822
legend: congress-18-19
nnv:
- id: nj.uscongress.1822
  name: NJ US Congress 1822 At Large
related-maps:
- id: meae.congressional.congress17.nj.county
  name: NJ 17th Congress
  type: previous
- id: meae.congressional.congress19.nj.county
  name: NJ 19th Congress
  type: next
- id: meae.congressional.congress18.national.county
  name: National 18th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress18.nj.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "700px", congress = 18)
```

</div>

New Jersey elected six Democratic-Republicans to the Eighteenth Congress. Five of those Democratic-Republicans were part of a faction led by Andrew Jackson, and one was part of a faction led by John Quincy Adams and Henry Clay.

The map for this election is incomplete due to the lack of returns at the town or county level.

New Jersey used a statewide at-large system for electing members to Congress. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
