---
meae-id: meae.congressional.congress17.ny.county
type: congressional
level: state
state: New York
geography: county
congressnum: 17
congressordinal: 17th
title: '17th Congress: New York 1821'
year: 1821
legend: dissrep
nnv:
- id: ny.uscongress1.1821
  name: NY US Congress 1821 District 1
- id: ny.uscongress2.1821
  name: NY US Congress 1821 District 2
- id: ny.uscongress3.1821
  name: NY US Congress 1821 District 3
- id: ny.uscongress4.1821
  name: NY US Congress 1821 District 4
- id: ny.uscongress5.1821
  name: NY US Congress 1821 District 5
- id: ny.uscongress6.1821
  name: NY US Congress 1821 District 6
- id: ny.uscongress7.1821
  name: NY US Congress 1821 District 7
- id: ny.uscongress8.1821
  name: NY US Congress 1821 District 8
- id: ny.uscongress9.1821
  name: NY US Congress 1821 District 9
- id: ny.uscongress10.1821
  name: NY US Congress 1821 District 10
- id: ny.uscongress11.1821
  name: NY US Congress 1821 District 11
- id: ny.uscongress12.1821
  name: NY US Congress 1821 District 12
- id: ny.uscongress13.1821
  name: NY US Congress 1821 District 13
- id: ny.uscongress14.1821
  name: NY US Congress 1821 District 14
- id: ny.uscongress15.1821
  name: NY US Congress 1821 District 15
- id: ny.uscongress16.1821
  name: NY US Congress 1821 District 16
- id: ny.uscongress17.1821
  name: NY US Congress 1821 District 17
- id: ny.uscongress18.1821
  name: NY US Congress 1821 District 18
- id: ny.uscongress19.1821
  name: NY US Congress 1821 District 19
- id: ny.uscongress20.1821
  name: NY US Congress 1821 District 20
- id: ny.uscongress21.1821
  name: NY US Congress 1821 District 21
- id: ny.uscongress22.1821
  name: NY US Congress 1821 District 22
related-maps:
- id: meae.congressional.congress16.ny.county
  name: NY 16th Congress
  type: previous
- id: meae.congressional.congress18.ny.county
  name: NY 18th Congress
  type: next
#- id: meae.congressional.congress17.national.district
#  name: National 17th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress17.ny.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "725px", congress = 17)
```

</div>

New York elected twenty-seven Democratic-Republicans to the Seventeenth Congress. Thirteen of the Republicans elected were members of an identifiable faction within the party. In New York, some candidates ran as Clintonians who supported internal improvements and soft money. 

New York used a district system for electing members to Congress. Each district elected one member of Congress, except Districts 1, 2, 12, 15, and 20, which each elected two members.

In 1821, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.specialcongress6.1821) was held in which Charles Borland, Jr. was elected to replace Selah Tuthill, who had died. 

In 1822, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.specialelectioncongress9.1822) was held in which Stephen Van Rensselaer was elected to replace Solomon Van Rensselaer, who had resigned from office. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
