---
meae-id: meae.congressional.congress10.nc.county
type: congressional
level: state
state: North Carolina
geography: county
congressnum: 10
congressordinal: 10th
title: '10th Congress: North Carolina 1806'
year: 1806
legend: fed-vs-rep
nnv:
- id: nc.uscongress1.1806
  name: NC US Congress 1806 District 1
- id: nc.uscongress2.1806
  name: NC US Congress 1806 District 2
- id: nc.uscongress3.1806
  name: NC US Congress 1806 District 3
- id: nc.uscongress4.1806
  name: NC US Congress 1806 District 4
- id: nc.uscongress5.1806
  name: NC US Congress 1806 District 5
- id: nc.uscongress6.1806
  name: NC US Congress 1806 District 6
- id: nc.uscongress7.1806
  name: NC US Congress 1806 District 7
- id: nc.uscongress8.1806
  name: NC US Congress 1806 District 8
- id: nc.uscongress9.1806
  name: NC US Congress 1806 District 9
- id: nc.uscongress10.1806
  name: NC US Congress 1806 District 10
- id: nc.uscongress11.1806
  name: NC US Congress 1806 District 11
- id: nc.uscongress12.1806
  name: NC US Congress 1806 District 12
related-maps:
- id: meae.congressional.congress09.nc.county
  name: NC 9th Congress
  type: previous
- id: meae.congressional.congress11.nc.county
  name: NC 11th Congress
  type: next
# - id: meae.congressional.congress10.national.district
#   name: National 10th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress10.nc.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", congress = 10)
```

</div>

North Carolina elected one Federalist and eleven Democratic-Republicans to the Tenth Congress.

The map for this election is incomplete due to the lack of returns at the county level.

North Carolina used the district system for electing members to Congress.

The election results in District 7 were contested and Congress ordered the seat vacated.

In 1808, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.essexsouth.special.1808) was held in which Federalist John Culpeper was elected to fill the seat in District 7.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
