---
meae-id: meae.staterepresentative.1796.de.county
type: state-rep
level: state
state: Delaware
geography: county
title: 'Delaware House of Representatives, 1796'
year: 1796
legend: fed-vs-rep
nnv:
- id: de.stateassembly.kent.1796
  name: DE House of Representatives 1796, Kent County 
- id: de.stateassembly.newcastle.1796
  name: DE House of Representatives 1796, New Castle County   
- id: de.stateassembly.sussex.1796
  name: DE House of Representatives 1796, Sussex County  
related-maps:
- id: meae.congressional.congress05.de.county
  name: DE 5th Congress
  type: congressional
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.staterepresentative.1796.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_staterep_map_data(state = "DE", election_date = "1796-10-01") %>%
  map_counties(height = "450px")
```

</div>

In 1796, Delaware elected fourteen Federalists and seven Democratic-Republicans to Delaware’s House of Representatives. Seven of the Federalists were elected from Kent County, and seven were elected from Sussex County. All seven Democratic-Republicans were elected from New Castle County.

Delaware’s House of Representatives was elected annually in early October. Delaware used a county-level at-large system, in which the seven candidates receiving the highest number of votes in each of Delaware’s three counties were elected.

Delaware’s state legislature, comprised of nine State Senators and twenty-one Representatives, was the smallest in the new nation. The party alignment represented in the 1796 House of Representatives election was typical in Delaware during the First Party System. This resulted in a State Legislature that was almost always controlled by Federalists. 

Often, when elections for Delaware’s House of Representatives and the U.S. House of Representatives occurred during the same year, as it did in 1796, the county-level party percentages in both elections closely matched. For example, in Delaware’s 1796 House of Representatives election and Delaware’s [Fifth Congressional](http://earlyamericanelections.org/maps/meae.congressional.congress05.de.county.html) election, the party percentages in each county only varied by about one or two percent. 

Delaware’s 1796 House of Representatives election is also historically significant as the first time that Delaware voters elected Caesar A. Rodney to a state-level political office. Caesar A. Rodney, nephew of Caesar Rodney (signer of the Declaration of Independence) would go on to become a leader in the Democratic-Republican party, serve six terms as a Delaware State Representative (1797-1802), two terms in the U.S. House of Representatives (the [Eighth](http://earlyamericanelections.org/maps/meae.congressional.congress08.de.county.html) and [Seventeenth](http://earlyamericanelections.org/maps/meae.congressional.congress17.de.county.html) congresses), and serve as the Attorney General of the United States under presidents Thomas Jefferson and James Madison. 


<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results_state_rep() %>%
  results_to_table_state_rep() %>%
  cat()
```

</div>
