---
meae-id: meae.congressional.congress02.vt.county
type: congressional
level: state
state: Vermont
geography: county
congressnum: 2
congressordinal: 2nd
title: '2nd Congress: Vermont 1791'
year: 1791
legend: fed-vs-anti
nnv:
- id: vt.uscongress.western.secondballot.1791
  name: VT US Congress 1791 District 1
- id: vt.uscongress.eastern.1791
  name: VT US Congress 1791 District 2
related-maps:
- id: meae.congressional.congress03.vt.county
  name: VT 3rd Congress
  type: next
# - id: meae.congressional.congress02.national.district
#   name: National 2nd Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress02.vt.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties()
```

</div>

Vermont elected two Anti-Federalists to the Second Congress.

Mapping this election is not possible because there are no returns at the town and county levels.

Vermont used a district system for electing members to Congress. Vermont required that candidates receive a majority of the votes in their districts. The first district thus required a second ballot to elect the candidate.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
