---
meae-id: meae.congressional.congress19.md.county
type: congressional
level: state
state: Maryland
geography: county
congressnum: 19
congressordinal: 19th
title: '19th Congress: Maryland 1824'
year: 1824
legend: congress-18-19
nnv:
- id: md.uscongress1.1824
  name: MD US Congress 1824 District 1
- id: md.uscongress2.1824
  name: MD US Congress 1824 District 2
- id: md.uscongress3.1824
  name: MD US Congress 1824 District 3
- id: md.uscongress4.1824
  name: MD US Congress 1824 District 4
- id: md.uscongress5.1824
  name: MD US Congress 1824 District 5
- id: md.uscongress6.1824
  name: MD US Congress 1824 District 6
- id: md.uscongress7.1824
  name: MD US Congress 1824 District 7
- id: md.uscongress8.1824
  name: MD US Congress 1824 District 8
related-maps:
- id: meae.congressional.congress18.md.county
  name: MD 18th Congress
  type: previous
- id: meae.congressional.congress19.national.county
  name: National 19th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress19.md.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~demrep_percentage, ~demrep_vote,
  "Baltimore", 39.30021, -76.61052, 1.0, 13215)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px", cities = FALSE) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city)

```

</div>

Maryland elected six Democratic-Republicans, one Federalist, and two dissenting Federalists to the Nineteenth Congress. Two of those Democratic-Republicans were part of a faction led by Andrew Jackson, and two of those Democratic-Republicans were part of a faction led by John Quincy Adams and Henry Clay. Both dissenting Federalists supported Adams and Clay. As the Federalist Party declined, many Federalists distanced themselves from the main party. Instead, their political affiliation more closely aligned with their choice of candidate for the 1824 presidential election. 

Maryland used a district system for electing members to Congress. Each district elected one member of Congress except District 5, which elected two members.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
