---
meae-id: meae.congressional.congress08.ma.county
type: congressional
level: state
state: Massachusetts
geography: county
congressnum: 8
congressordinal: 8th
title: '8th Congress: Massachusetts 1802'
year: 1802
legend: fed-vs-rep
nnv:
- id: ma.uscongress.suffolk.1802
  name: MA US Congress 1802 District 1
- id: ma.uscongress.essexsouth.1802
  name: MA US Congress 1802 District 2
- id: ma.uscongress.essexnorth.1802
  name: MA US Congress 1802 District 3
- id: ma.uscongress.middlesex.1802
  name: MA US Congress 1802 District 4
- id: ma.uscongress.hampshiresouth.1802
  name: MA US Congress 1802 District 5
- id: ma.uscongress.hampshirenorth.ballot3.1803
  name: MA US Congress 1803 District 6
- id: ma.uscongress.plymouth.1802
  name: MA US Congress 1802 District 7
- id: ma.uscongress.barnstable.1802
  name: MA US Congress 1802 District 8
- id: ma.uscongress.bristol.1802
  name: MA US Congress 1802 District 9
- id: ma.uscongress.worcestersouth.1802
  name: MA US Congress 1802 District 10
- id: ma.uscongress.worcesternorth.1802
  name: MA US Congress 1802 District 11
- id: ma.uscongress.berkshire.1802
  name: MA US Congress 1802 District 12
- id: ma.uscongress.norfolk.1802
  name: MA US Congress 1802 District 13
- id: ma.uscongress.york.1802
  name: MA US Congress 1802 District 14
- id: ma.uscongress.cumberland.1802
  name: MA US Congress 1802 District 15
- id: ma.uscongress.lincoln.1802
  name: MA US Congress 1802 District 16
- id: ma.uscongress.kennebec.1802
  name: MA US Congress 1802 District 17
related-maps:
- id: meae.congressional.congress07.ma.county
  name: MA 7th Congress
  type: previous
- id: meae.congressional.congress09.ma.county
  name: MA 9th Congress
  type: next
- id: meae.congressional.congress08.national.county
  name: National 8th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress08.ma.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties() %>% 
  fitBounds(-73.508, 41.186, -69.861, 43.75)
```

</div>

Massachusetts elected ten Federalists and seven Democratic-Republicans to the Eighth Congress.

Following the 1800 Census, Massachusetts gained three seats in the House of Representatives.

Massachusetts used the district system for electing members to Congress. 

In 1804, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.berkshire.special.1804) was held in which Simon Larned was elected to replace Thompson J. Skinner, who had resigned from office on August 10th, 1804.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
