---
meae-id: meae.congressional.congress15.nc.county
type: congressional
level: state
state: North Carolina
geography: county
congressnum: 15
congressordinal: 15th
title: '15th Congress: North Carolina 1817'
year: 1817
legend: fed-vs-rep
nnv:
- id: nc.uscongress1.1817
  name: NC US Congress 1817 District 1
- id: nc.uscongress2.1817
  name: NC US Congress 1817 District 2
- id: nc.uscongress3.1817
  name: NC US Congress 1817 District 3
- id: nc.uscongress4.1817
  name: NC US Congress 1817 District 4
- id: nc.uscongress5.1817
  name: NC US Congress 1817 District 5
- id: nc.uscongress6.1817
  name: NC US Congress 1817 District 6
- id: nc.uscongress7.1817
  name: NC US Congress 1817 District 7
- id: nc.uscongress8.1817
  name: NC US Congress 1817 District 8
- id: nc.uscongress9.1817
  name: NC US Congress 1817 District 9
- id: nc.uscongress10.1817
  name: NC US Congress 1817 District 10
- id: nc.uscongress11.1817
  name: NC US Congress 1817 District 11
- id: nc.uscongress12.1817
  name: NC US Congress 1817 District 12
- id: nc.uscongress13.1817
  name: NC US Congress 1817 District 13
related-maps:
- id: meae.congressional.congress14.nc.county
  name: NC 14th Congress
  type: previous
- id: meae.congressional.congress16.nc.county
  name: NC 16th Congress
  type: next
#- id: meae.congressional.congress15.national.district
#  name: National 15th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress15.nc.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", congress = 15)
```

</div>

North Carolina elected three Federalists and ten Democratic-Republicans to the Fifteenth Congress.

The map for this election is incomplete due to the lack of returns at the county level.

North Carolina used a district system for electing members to Congress. 

In 1818, a [special election](https://elections.lib.tufts.edu/catalog/tufts:nc.uscongress11.specialelection.1818) was held in which William Davidson was elected to replace Daniel M. Forney, who had resigned from office. 

In 1818, a [special election](https://elections.lib.tufts.edu/catalog/tufts:nc.uscongress7.specialelection.1818) was held in which James Stewart was elected to replace Alexander MacMillan, who had died.

In 1819, a [special election](https://elections.lib.tufts.edu/catalog/tufts:nc.uscongress.10.special.1819) was held in which Charles Fisher was elected to replace George Mumford, who had died.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
