---
meae-id: meae.congressional.congress04.nh.county
type: congressional
level: state
state: New Hampshire
geography: county
congressnum: 4
congressordinal: 4th
title: '4th Congress: New Hampshire 1794'
year: 1794
legend: fed-vs-rep
nnv:
- id: nh.uscongress.1794
  name: NH US Congress 1794 At Large
related-maps:
- id: meae.congressional.congress03.nh.county
  name: NH 3rd Congress
  type: previous
- id: meae.congressional.congress05.nh.county
  name: NH 5th Congress
  type: next
# - id: meae.congressional.congress04.national.district
#   name: National 4th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress04.nh.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>% 
  map_counties(height = "700px", congress = 4)
```

</div>

New Hampshire elected four Federalists to the Fourth Congress.

Mapping this election is not possible because of insufficient returns at the town or county level.

Although New Hampshire used a statewide at-large method for electing members to Congress, state law required that candidates receive a majority of votes in order to win. In a second runoff election, Abiel Foster beat the incumbent Paine Wingate.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
