---
meae-id: meae.congressional.congress15.ny.county
type: congressional
level: state
state: New York
geography: county
congressnum: 15
congressordinal: 15th
title: '15th Congress: New York 1816'
year: 1816
legend: fed-vs-rep
nnv:
- id: ny.uscongress1.1816
  name: NY US Congress 1816 District 1
- id: ny.uscongress2.1816
  name: NY US Congress 1816 District 2
- id: ny.uscongress3.1816
  name: NY US Congress 1816 District 3
- id: ny.uscongress4.1816
  name: NY US Congress 1816 District 4
- id: ny.uscongress5.1816
  name: NY US Congress 1816 District 5
- id: ny.uscongress6.1816
  name: NY US Congress 1816 District 6
- id: ny.uscongress7.1816
  name: NY US Congress 1816 District 7
- id: ny.uscongress8.1816
  name: NY US Congress 1816 District 8
- id: ny.uscongress9.1816
  name: NY US Congress 1816 District 9
- id: ny.uscongress10.1816
  name: NY US Congress 1816 District 10
- id: ny.uscongress11.1816
  name: NY US Congress 1816 District 11
- id: ny.uscongress12.1816
  name: NY US Congress 1816 District 12
- id: ny.uscongress13.1816
  name: NY US Congress 1816 District 13
- id: ny.uscongress14.1816
  name: NY US Congress 1816 District 14
- id: ny.uscongress15.1816
  name: NY US Congress 1816 District 15
- id: ny.uscongress16.1816
  name: NY US Congress 1816 District 16
- id: ny.uscongress17.1816
  name: NY US Congress 1816 District 17
- id: ny.uscongress18.1816
  name: NY US Congress 1816 District 18
- id: ny.uscongress19.1816
  name: NY US Congress 1816 District 19
- id: ny.uscongress20.1816
  name: NY US Congress 1816 District 20
- id: ny.uscongress21.1816
  name: NY US Congress 1816 District 21
related-maps:
- id: meae.congressional.congress14.ny.county
  name: NY 14th Congress
  type: previous
- id: meae.congressional.congress16.ny.county
  name: NY 16th Congress
  type: next
- id: meae.congressional.congress15.national.county
  name: National 15th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress15.ny.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "725px", congress = 15)
```

</div>

New York elected five Federalists and twenty-two Democratic-Republicans to the Fifteenth Congress. 

New York used a district system for electing members to Congress. Each district elected one member of Congress, except Districts 1, 2, 12, 15, 20, and 21, which each elected two members. 

In 1817, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.uscongress4.special.1817) was held in which James Tallmadge, Jr. was elected to replace Henry B. Lee, who had died. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
