---
meae-id: meae.congressional.congress05.nh.county
type: congressional
level: state
state: New Hampshire
geography: county
congressnum: 5
congressordinal: 5th
title: '5th Congress: New Hampshire 1796'
year: 1796
legend: fed-vs-rep
nnv:
- id: nh.uscongress.1796
  name: NH US Congress 1796 At Large
related-maps:
- id: meae.congressional.congress04.nh.county
  name: NH 4th Congress
  type: previous
# - id: meae.congressional.congress06.nh.county
#   name: NH 6th Congress
#   type: next
# - id: meae.congressional.congress05.national.district
#   name: National 5th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress05.nh.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>% 
  map_counties(height = "500px", congress = 5)
```

</div>

New Hampshire elected three Federalists to the Fifth Congress.

Mapping this election is not possible because of the lack of returns at the town or county level.
 
New Hampshire used a statewide at-large method for electing members to Congress.

In November 1797, New Hampshire held a [special election](https://elections.lib.tufts.edu/catalog/tufts:nh.uscongress.special.1797), which went to a [second ballot](https://elections.lib.tufts.edu/catalog/tufts:nh.uscongress.special.2.1797), in which Peleg Sprague was elected to replace Jeremiah Smith, who resigned.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
