---
meae-id: meae.congressional.congress18.me.county
type: congressional
level: state
state: Maine
geography: county
congressnum: 18
congressordinal: 18th
title: '18th Congress: Maine 1823'
year: 1823
legend: congress-18-19
nnv:
- id: me.uscongress1.fourth.1823
  name: ME US Congress 1823 District 1
- id: me.uscongress2.1823
  name: ME US Congress 1823 District 2
- id: me.uscongress3.third.1823
  name: ME US Congress 1823 District 3
- id: me.uscongress4.second.1823
  name: ME US Congress 1823 District 4
- id: me.uscongress5.1823
  name: ME US Congress 1823 District 5
- id: me.uscongress6.third.1823
  name: ME US Congress 1823 District 6
- id: me.uscongress7.1823
  name: ME US Congress 1823 District 7
related-maps:
- id: meae.congressional.congress17.me.county
  name: ME 17th Congress
  type: previous
- id: meae.congressional.congress19.me.county
  name: ME 19th Congress
  type: next
#- id: meae.congressional.congress18.national.district
#  name: National 18th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress18.me.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties()
```

</div>

Maine elected two Federalists and five Democratic-Republicans to the Eighteenth Congress. All five of those Democratic-Republicans were part of a faction led by John Quincy Adams and Henry Clay. 

Maine used a district system for electing members to Congress. 

In 1822, a [special election](https://elections.lib.tufts.edu/catalog/tufts:me.uscongress2.1822) was held in which Mark Harris was elected to replace Ezekiel Whitman, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
