---
meae-id: meae.congressional.congress18.ny.county
type: congressional
level: state
state: New York
geography: county
congressnum: 18
congressordinal: 18th
title: '18th Congress: New York 1822'
year: 1822
legend: dissrep
nnv:
- id: ny.uscongress1.1822
  name: NY US Congress 1822 District 1
- id: ny.uscongress2.1822
  name: NY US Congress 1822 District 2
- id: ny.uscongress3.1822
  name: NY US Congress 1822 District 3
- id: ny.uscongress4.1822
  name: NY US Congress 1822 District 4
- id: ny.uscongress5.1822
  name: NY US Congress 1822 District 5
- id: ny.uscongress6.1822
  name: NY US Congress 1822 District 6
- id: ny.uscongress7.1822
  name: NY US Congress 1822 District 7
- id: ny.uscongress8.1822
  name: NY US Congress 1822 District 8
- id: ny.uscongress9.1822
  name: NY US Congress 1822 District 9
- id: ny.uscongress10.1822
  name: NY US Congress 1822 District 10
- id: ny.uscongress11.1822
  name: NY US Congress 1822 District 11
- id: ny.uscongress12.1822
  name: NY US Congress 1822 District 12
- id: ny.uscongress13.1822
  name: NY US Congress 1822 District 13
- id: ny.uscongress14.1822
  name: NY US Congress 1822 District 14
- id: ny.uscongress15.1822
  name: NY US Congress 1822 District 15
- id: ny.uscongress16.1822
  name: NY US Congress 1822 District 16
- id: ny.uscongress17.1822
  name: NY US Congress 1822 District 17
- id: ny.uscongress18.1822
  name: NY US Congress 1822 District 18
- id: ny.uscongress19.1822
  name: NY US Congress 1822 District 19
- id: ny.uscongress20.1822
  name: NY US Congress 1822 District 20
- id: ny.uscongress21.1822
  name: NY US Congress 1822 District 21
- id: ny.uscongress22.1822
  name: NY US Congress 1822 District 22
- id: ny.uscongress23.1822
  name: NY US Congress 1822 District 23
- id: ny.uscongress24.1822
  name: NY US Congress 1822 District 24
- id: ny.uscongress25.1822
  name: NY US Congress 1822 District 25
- id: ny.uscongress26.1822
  name: NY US Congress 1822 District 26
- id: ny.uscongress27.1822
  name: NY US Congress 1822 District 27
- id: ny.uscongress28.1822
  name: NY US Congress 1822 District 28
- id: ny.uscongress29.1822
  name: NY US Congress 1822 District 29
- id: ny.uscongress30.1822
  name: NY US Congress 1822 District 30
related-maps:
- id: meae.congressional.congress17.ny.county
  name: NY 17th Congress
  type: previous
- id: meae.congressional.congress19.ny.county
  name: NY 19th Congress
  type: next
- id: meae.congressional.congress18.national.county
  name: National 18th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress18.ny.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "725px", congress = 18)
```

</div>

New York elected thirty-four Democratic-Republicans to the Eighteenth Congress. Twelve of the Democratic-Republicans were part of an identifiable faction within the party. In New York, some candidates ran as Clintonians who supported internal improvements and soft money. 

Following the 1820 Census, New York gained seven seats in the House of Representatives. 

New York used a district system for electing members to Congress. Each district elected one member of Congress, except Districts 20 and 26, which each elected two members, and District 3, which elected three members.

In 1823, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.congress.1823) was held in which William Woods was elected to replace William B. Rochester, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
