---
meae-id: meae.congressional.congress09.nc.county
type: congressional
level: state
state: North Carolina
geography: county
congressnum: 9
congressordinal: 9th
title: '9th Congress: North Carolina 1804'
year: 1804
legend: fed-vs-rep
nnv:
- id: nc.uscongress1.1804
  name: NC US Congress 1804 District 1
- id: nc.uscongress2.1804
  name: NC US Congress 1804 District 2
- id: nc.uscongress3.1804
  name: NC US Congress 1804 District 3
- id: nc.uscongress4.1804
  name: NC US Congress 1804 District 4
- id: nc.uscongress5.specialelection.1805
  name: NC US Congress 1805 District 5
- id: nc.uscongress6.1804
  name: NC US Congress 1804 District 6
- id: nc.uscongress7.1804
  name: NC US Congress 1804 District 7
- id: nc.uscongress8.1804
  name: NC US Congress 1804 District 8
- id: nc.uscongress9.1804
  name: NC US Congress 1804 District 9
- id: nc.uscongress10.1804
  name: NC US Congress 1804 District 10
- id: nc.uscongress11.1804
  name: NC US Congress 1804 District 11
- id: nc.uscongress12.1804
  name: NC US Congress 1804 District 12
related-maps:
- id: meae.congressional.congress08.nc.county
  name: NC 8th Congress
  type: previous
- id: meae.congressional.congress10.nc.county
  name: NC 10th Congress
  type: next
# - id: meae.congressional.congress09.national.district
#   name: National 9th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress09.nc.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", congress = 9)
```

</div>

North Carolina elected twelve Democratic-Republicans to the Ninth Congress.

Mapping this election is incomplete because of the lack of local returns in many areas.

North Carolina used the district system for electing members to Congress.

In 1805, a [special election](https://elections.lib.tufts.edu/catalog/tufts:nc.uscongress5.specialelection.1805) was held in which Democratic-Republican Thomas Kenan was elected to replace James Gillespie, who died while in office.

In 1806, a [special election](https://elections.lib.tufts.edu/catalog/tufts:nc.uscongress10.special.1806) was held in which Evan Alexander was elected to replace Nathaniel Alexander, who had resigned after being elected as the Governor of North Carolina.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
