---
meae-id: meae.congressional.congress08.ny.county
type: congressional
level: state
state: New York
geography: county
congressnum: 8
congressordinal: 8th
title: '8th Congress: New York 1803'
year: 1803
legend: fed-vs-rep
nnv:
- id: ny.uscongress1.1802
  name: NY US Congress 1802 District 1
- id: ny.uscongress2.1802
  name: NY US Congress 1802 District 2
- id: ny.uscongress3.1802
  name: NY US Congress 1802 District 3
- id: ny.uscongress4.1802
  name: NY US Congress 1802 District 4
- id: ny.uscongress5.1802
  name: NY US Congress 1802 District 5
- id: ny.uscongress6.1802
  name: NY US Congress 1802 District 6
- id: ny.specialuscongress7.1803
  name: NY US Congress 1803 District 7
- id: ny.uscongress8.1802
  name: NY US Congress 1802 District 8
- id: ny.uscongress9.1802
  name: NY US Congress 1802 District 9
- id: ny.uscongress10.1802
  name: NY US Congress 1802 District 10
- id: ny.uscongress11.1802
  name: NY US Congress 1802 District 11
- id: ny.uscongress12.1802
  name: NY US Congress 1802 District 12
- id: ny.uscongress13.1802
  name: NY US Congress 1802 District 13
- id: ny.uscongress14.1802
  name: NY US Congress 1802 District 14
- id: ny.uscongress15.1802
  name: NY US Congress 1802 District 15
- id: ny.uscongress16.1802
  name: NY US Congress 1802 District 16
- id: ny.uscongress17.1802
  name: NY US Congress 1802 District 17
related-maps:
- id: meae.congressional.congress07.ny.county
  name: NY 7th Congress
  type: previous
- id: meae.congressional.congress09.ny.county
  name: NY 9th Congress
  type: next
# - id: meae.congressional.congress08.national.district
#   name: National 8th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress08.ny.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "725px", congress = 8)
```

</div>

New York elected five Federalists and twelve Democratic-Republicans to the Eighth Congress.

Following the 1800 Census, New York gained seven seats in the House of Representatives.

New York used the district system for electing members to Congress.

In 1803, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.specialuscongress6.1803) was held in which Daniel C. Verplanck was elected to replace Isaac Bloom, who died while in office.

In 1804, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.uscongress1.special.1804) was held in which Samuel Riker was elected to replace Democratic-Republican John Smith, who had resigned from office on February 23, 1804.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
