---
meae-id: meae.congressional.congress13.oh.county
type: congressional
level: state
state: Ohio
geography: county
congressnum: 13
congressordinal: 13th
title: '13th Congress: Ohio 1812'
year: 1812
legend: fed-vs-rep
nnv:
- id: oh.ushouseofrepresentatives.district1.1812
  name: OH US Congress 1812 District 1
- id: oh.ushouseofrepresentatives.district2.1812
  name: OH US Congress 1812 District 2
- id: oh.ushouseofrepresentatives.district3.1812
  name: OH US Congress 1812 District 3
- id: oh.ushouseofrepresentatives.district4.1812
  name: OH US Congress 1812 District 4
- id: oh.ushouseofrepresentatives.district5.1812
  name: OH US Congress 1812 District 5
- id: oh.ushouseofrepresentatives.district6.1812
  name: OH US Congress 1812 District 6
related-maps:
- id: meae.congressional.congress12.oh.county
  name: OH 12th Congress
  type: previous
- id: meae.congressional.congress14.oh.county
  name: OH 14th Congress
  type: next
#- id: meae.congressional.congress13.national.district
#  name: National 13th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress13.oh.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  filter(id != "ohs_nca4",
         id != "ohs_nca5") %>% 
  map_counties(height = "650px", congress = 13)
```

</div>

Ohio elected one Federalist and five Democratic-Republican to the Thirteenth Congress. 

The map for this election is incomplete due to the lack of returns at the town or county level.

Following the 1810 Census, Ohio gained five more seats in the House of Representatives. 

For the first time, Ohio used a district system for electing members to Congress.

In 1813, a [special election](https://elections.lib.tufts.edu/catalog/tufts:oh.ushouseofrepresentatives.3.special.1813) was held in which William Creighton was elected to replace Duncan MacArthur, who had resigned. 

In 1813, a [special election](https://elections.lib.tufts.edu/catalog/tufts:oh.ushouseofrepresentatives.6.special.1813) was held in which Reasin Beall was elected to replace John S. Edward, who had died. 

In 1814, a [special election](https://elections.lib.tufts.edu/catalog/tufts:oh.uscongress6.special.1814) was held in which David Clendenin was elected to replace Reasin Beall, who had resigned. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
