---
meae-id: meae.congressional.congress09.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 9
congressordinal: 9th
title: '9th Congress: Delaware 1804'
year: 1804
legend: fed-vs-rep
nnv:
- id: de.uscongress.1804
  name: DE US Congress 1804 At Large
related-maps:
- id: meae.congressional.congress08.de.county
  name: DE 8th Congress
  type: previous
- id: meae.congressional.congress10.de.county
  name: DE 10th Congress
  type: next
# - id: meae.congressional.congress09.national.district
#   name: National 9th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress09.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Delaware elected one Federalist to the Ninth Congress.

Delaware used a statewide at-large method for electing a member to Congress. Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. The at-large winner was then declared the winner.  This map depicts the initial winner.

In 1805, a [special election](https://elections.lib.tufts.edu/catalog/tufts:de.uscongress.1805) was held in which Federalist James M. Broom was elected to replace James A. Bayard, who had resigned from office after his election to the Senate.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
