---
meae-id: meae.congressional.congress16.pa.county
type: congressional
level: state
state: Pennsylvania
geography: county
congressnum: 16
congressordinal: 16th
title: '16th Congress: Pennsylvania 1818'
year: 1818
legend: fed-vs-rep
nnv:
- id: pa.congress.1.1818
  name: PA US Congress 1818 District 1
- id: pa.congress.2.1818
  name: PA US Congress 1818 District 2
- id: pa.congress.3.1818
  name: PA US Congress 1818 District 3
- id: pa.congress.4.1818
  name: PA US Congress 1818 District 4
- id: pa.congress.5.1818
  name: PA US Congress 1818 District 5
- id: pa.congress.6.1818
  name: PA US Congress 1818 District 6
- id: pa.congress.7.1818
  name: PA US Congress 1818 District 7
- id: pa.congress.8.1818
  name: PA US Congress 1818 District 8
- id: pa.congress.9.1818
  name: PA US Congress 1818 District 9
- id: pa.congress.10.1818
  name: PA US Congress 1818 District 10
- id: pa.congress.11.1818
  name: PA US Congress 1818 District 11
- id: pa.congress.12.1818
  name: PA US Congress 1818 District 12
- id: pa.congress.13.1818
  name: PA US Congress 1818 District 13
- id: pa.congress.14.1818
  name: PA US Congress 1818 District 14
- id: pa.congress.15.1818
  name: PA US Congress 1818 District 15
related-maps:
- id: meae.congressional.congress15.pa.county
  name: PA 15th Congress
  type: previous
- id: meae.congressional.congress17.pa.county
  name: PA 17th Congress
  type: next
- id: meae.congressional.congress16.national.county
  name: National 16th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress16.pa.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~federalist_vote, ~demrep_vote,
    "Philadelphia", 39.9526, -75.1652, 0.643, 0.357, 10552, 5871)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", cities = 0, congress = 16) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1<br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city) 
```

</div>

Pennsylvania elected six Federalists and seventeen Democratic-Republicans to the Sixteenth Congress. 

The map for this election is incomplete due to the lack of returns in many areas.

Pennsylvania used a district system for electing members to Congress. Each district elected one member of Congress except District 1, which elected four members, and Districts 2, 3, 5, 6, and 10, which each elected two members. The votes cast in Warren County are included in the Venango County totals.

In 1820, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress5.special.1820) was held in which Thomas G. MacCullough was elected to replace David Fullerton, who had resigned from office. 

In 1820, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress7.special.1820) was held in which Daniel Udree was elected to replace Joseph Hiester, who had resigned from office. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
