---
meae-id: meae.congressional.congress09.ct.county
type: congressional
level: state
state: Connecticut
geography: county
congressnum: 9
congressordinal: 9th
title: '9th Congress: Connecticut 1804'
year: 1804
legend: fed-vs-rep
nnv:
- id: ct.congress.1804
  name: CT US Congress 1804 At Large
related-maps:
- id: meae.congressional.congress08.ct.county
  name: CT 8th Congress
  type: previous
- id: meae.congressional.congress10.ct.county
  name: CT 10th Congress
  type: next
- id: meae.congressional.congress09.national.county
  name: National 9th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)
library(sf)

map_id <- "meae.congressional.congress09.ct.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  filter(id != "cts_wr") %>% 
  map_counties(height = "350px", congress = 9)
```

</div>

Connecticut elected seven Federalists to the Ninth Congress.

Mapping this election is not possible because of the lack of returns at the town or county level.

Connecticut used a statewide at-large method for electing members to Congress.

In 1805, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ct.congress.special.1805) was held in which Federalist Timothy Pitkin, Jr. and Federalist Lewis B. Sturges were elected to replace Calvin Goddard and Roger Griswold, who both had resigned before the 9th Congress convened.

In 1806, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ct.congress.special.1806) was held in which Theodore Dwight was elected to replace John C. Smith, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
