---
meae-id: meae.congressional.congress16.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 16
congressordinal: 16th
title: '16th Congress: Delaware 1818'
year: 1818
legend: fed-vs-rep
nnv:
- id: de.uscongress.1818
  name: DE US Congress 1818 At Large
related-maps:
- id: meae.congressional.congress15.de.county
  name: DE 15th Congress
  type: previous
- id: meae.congressional.congress17.de.county
  name: DE 17th Congress
  type: next
#- id: meae.congressional.congress16.national.district
#  name: National 16th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress16.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Delaware elected one Federalist and one Democratic-Republican to the Sixteenth Congress.

Delaware used a statewide at-large system for electing members to Congress. Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. The at-large winner was then declared the winner.  This map depicts the initial winners.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
