---
meae-id: meae.congressional.congress19.ny.county
type: congressional
level: state
state: New York
geography: county
congressnum: 19
congressordinal: 19th
title: '19th Congress: New York 1824'
year: 1824
legend: dissrep
nnv:
- id: ny.uscongress1.1824
  name: NY US Congress 1824 District 1
- id: ny.uscongress2.1824
  name: NY US Congress 1824 District 2
- id: ny.uscongress3.1824
  name: NY US Congress 1824 District 3
- id: ny.uscongress4.1824
  name: NY US Congress 1824 District 4
- id: ny.uscongress5.1824
  name: NY US Congress 1824 District 5
- id: ny.uscongress6.1824
  name: NY US Congress 1824 District 6
- id: ny.uscongress7.1824
  name: NY US Congress 1824 District 7
- id: ny.uscongress8.1824
  name: NY US Congress 1824 District 8
- id: ny.uscongress9.1824
  name: NY US Congress 1824 District 9
- id: ny.uscongress10.1824
  name: NY US Congress 1824 District 10
- id: ny.uscongress11.1824
  name: NY US Congress 1824 District 11
- id: ny.uscongress12.1824
  name: NY US Congress 1824 District 12
- id: ny.uscongress13.1824
  name: NY US Congress 1824 District 13
- id: ny.uscongress14.1824
  name: NY US Congress 1824 District 14
- id: ny.uscongress15.1824
  name: NY US Congress 1824 District 15
- id: ny.uscongress16.1824
  name: NY US Congress 1824 District 16
- id: ny.uscongress17.1824
  name: NY US Congress 1824 District 17
- id: ny.uscongress18.1824
  name: NY US Congress 1824 District 18
- id: ny.uscongress19.1824
  name: NY US Congress 1824 District 19
- id: ny.uscongress20.1824
  name: NY US Congress 1824 District 20
- id: ny.uscongress21.1824
  name: NY US Congress 1824 District 21
- id: ny.uscongress22.1824
  name: NY US Congress 1824 District 22
- id: ny.uscongress23.1824
  name: NY US Congress 1824 District 23
- id: ny.uscongress24.1824
  name: NY US Congress 1824 District 24
- id: ny.uscongress25.1824
  name: NY US Congress 1824 District 25
- id: ny.uscongress26.1824
  name: NY US Congress 1824 District 26
- id: ny.uscongress27.1824
  name: NY US Congress 1824 District 27
- id: ny.uscongress28.1824
  name: NY US Congress 1824 District 28
- id: ny.uscongress29.1824
  name: NY US Congress 1824 District 29
- id: ny.uscongress30.1824
  name: NY US Congress 1824 District 30
related-maps:
- id: meae.congressional.congress18.ny.county
  name: NY 18th Congress
  type: previous
#- id: meae.congressional.congress19.national.district
#  name: National 19th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress19.ny.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "725px", congress = 19)
```

</div>

New York elected thirty-four Democratic-Republicans to the Nineteenth Congress. Twenty-four of the Democratic-Republicans were part of an identifiable faction within the party. In New York, some candidates ran as Clintonians who supported internal improvements and soft money. 

New York used a district system for electing members to Congress. Each district elected one member of Congress, except Districts 20 and 26, which each elected two members, and District 3, which elected three members.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
