---
meae-id: meae.congressional.congress04.ma.county
type: congressional
level: state
state: Massachusetts
geography: county
congressnum: 4
congressordinal: 4th
title: '4th Congress: Massachusetts 1794'
year: 1794
legend: fed-vs-rep
nnv:
- id: ma.uscongress.western.1.1794
  name: MA US Congress 1794 District 1
- id: ma.uscongress.western.2.1794
  name: MA US Congress 1794 District 2
- id: ma.uscongress.western.3.1794
  name: MA US Congress 1794 District 3
- id: ma.uscongress.western.4.1794
  name: MA US Congress 1794 District 4
- id: ma.uscongress.southern.1.1794
  name: MA US Congress 1794 District 5
- id: ma.uscongress.southern.2.1794
  name: MA US Congress 1794 District 6
- id: ma.uscongress.southern.3.ballot4.1795
  name: MA US Congress 1795 District 7
- id: ma.uscongress.middle.1.1794
  name: MA US Congress 1794 District 8
- id: ma.uscongress.middle.2.ballot3.1795
  name: MA US Congress 1795 District 9
- id: ma.uscongress.middle.3.1794
  name: MA US Congress 1794 District 10
- id: ma.uscongress.middle.4.ballot3.1795
  name: MA US Congress 1795 District 11
- id: ma.uscongress.eastern.1.1794
  name: MA US Congress 1794 District 12
- id: ma.uscongress.eastern.2.ballot2.1795
  name: MA US Congress 1795 District 13
- id: ma.uscongress.eastern.3.ballot2.1795
  name: MA US Congress 1795 District 14
related-maps:
- id: meae.congressional.congress03.ma.county
  name: MA 3rd Congress
  type: previous
- id: meae.congressional.congress05.ma.county
  name: MA 5th Congress
  type: next
# - id: meae.congressional.congress04.national.district
#   name: National 4th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress04.ma.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>% 
  map_counties() %>% 
  fitBounds(-73.508, 41.186, -69.861, 43.75)
```

</div>

Massachusetts elected eleven Federalists and three Democratic-Republicans to the Fourth Congress.  

Although Massachusetts used the district system for electing members to Congress, state law required that candidates receive a majority of votes in order to win. As a result, four districts required multiple ballots to elect their members in elections November 1794 through April 1795:

[Massachusetts 1795 U.S. House of Representatives, District Southern 3, Ballot 4](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.southern.3.ballot4.1795)
[Massachusetts 1795 U.S. House of Representatives, District Middle 2, Ballot 3](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.middle.2.ballot3.1795)
[Massachusetts 1795 U.S. House of Representatives, District Middle 4, Ballot 3](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.middle.4.ballot3.1795)
[Massachusetts 1795 U.S. House of Representatives, District Eastern 2, Ballot 2](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.eastern.2.ballot2.1795)
[Massachusetts 1795 U.S. House of Representatives, District Eastern 3, Ballot 2](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.eastern.3.ballot2.1795)

Massachusetts held a special election in which Thompson Skinner was elected to replace Theodore Sedgwick, who resigned to serve in the US Senate:
[Massachusetts 1796 U.S. House of Representatives, District Western 1, Special](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.western.1.special.1796)
[Massachusetts 1796 U.S. House of Representatives, District Western 1, Special, Ballot 2](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.western.1.special2.1796)

Massachusetts held a special election in which Samuel Sewall was elected to replace Benjamin Goodhue, who resigned to serve in the US Senate:
[Massachusetts 1796 U.S. House of Representatives, District Middle 3, Special](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.middle.3.special.1796)
[Massachusetts 1796 U.S. House of Representatives, District Middle 3, Special, Ballot 2](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.middle.3.special2.1796)

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
