---
meae-id: meae.congressional.congress14.va.county
type: congressional
level: state
state: Virginia
geography: county
congressnum: 14
congressordinal: 14th
title: '14th Congress: Virginia 1815'
year: 1815
legend: fed-vs-rep
nnv:
- id: va.uscongress.1.1815
  name: VA US Congress 1815 District 1
- id: va.uscongress.2.1815
  name: VA US Congress 1815 District 2
- id: va.uscongress.3.1815
  name: VA US Congress 1815 District 3
- id: va.uscongress.4.1815
  name: VA US Congress 1815 District 4
- id: va.uscongress.5.1815
  name: VA US Congress 1815 District 5
- id: va.uscongress.6.1815
  name: VA US Congress 1815 District 6
- id: va.uscongress.7.1815
  name: VA US Congress 1815 District 7
- id: va.uscongress.8.1815
  name: VA US Congress 1815 District 8
- id: va.uscongress.9.1815
  name: VA US Congress 1815 District 9
- id: va.uscongress.10.1815
  name: VA US Congress 1815 District 10
- id: va.uscongress.11.1815
  name: VA US Congress 1815 District 11
- id: va.uscongress.12.1815
  name: VA US Congress 1815 District 12
- id: va.uscongress.13.1815
  name: VA US Congress 1815 District 13
- id: va.uscongress.14.1815
  name: VA US Congress 1815 District 14
- id: va.uscongress.15.1815
  name: VA US Congress 1815 District 15
- id: va.uscongress.16.1815
  name: VA US Congress 1815 District 16
- id: va.uscongress.17.1815
  name: VA US Congress 1815 District 17
- id: va.uscongress.18.1815
  name: VA US Congress 1815 District 18
- id: va.uscongress.19.1815
  name: VA US Congress 1815 District 19
- id: va.uscongress.20.1815
  name: VA US Congress 1815 District 20
- id: va.uscongress.21.1815
  name: VA US Congress 1815 District 21
- id: va.uscongress.22.1815
  name: VA US Congress 1815 District 22
- id: va.uscongress.23.1815
  name: VA US Congress 1815 District 23
related-maps:
- id: meae.congressional.congress13.va.county
  name: VA 13th Congress
  type: previous
- id: meae.congressional.congress15.va.county
  name: VA 15th Congress
  type: next
#- id: meae.congressional.congress14.national.district
#  name: National 14th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress14.va.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "550px", congress = 14)
```

</div>

Virginia elected six Federalist and seventeen Democratic-Republicans to the Fourteenth Congress.

The map for this election is incomplete due to the lack of returns in several counties.

Virginia used a district system for electing members to Congress.

In 1815, a [special election](https://elections.lib.tufts.edu/catalog/tufts:va.uscongress.15.special.1815) was held in which John W. Kerr was elected to replace Mathew Clay, who had died before the Fourteenth Congress began.

In 1816, a [special election](https://elections.lib.tufts.edu/catalog/tufts:va.special.uscongress.18.1816) was held in which Thomas M. Nelson was elected to replace Thomas Gholson, who had died.

In 1816, a [special election](https://elections.lib.tufts.edu/catalog/tufts:va.uscongress.23.special.1816) was held in which John Tyler was elected to replace John Clopton, Sr., who had died.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
