---
meae-id: meae.congressional.congress19.ri.county
type: congressional
level: state
state: Rhode Island
geography: county
congressnum: 19
congressordinal: 19th
title: '19th Congress: Rhode Island 1825'
year: 1825
legend: congress-18-19
nnv:
- id: ri.uscongress.1825
  name: RI US Congress 1825 At Large
related-maps:
- id: meae.congressional.congress18.ri.county
  name: RI 18th Congress
  type: previous
#- id: meae.congressional.congress19.national.district
#  name: National 19th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress19.ri.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", congress = 19)
```

</div>

Rhode Island elected two Democratic-Republicans to the Nineteenth Congress. Both of those Democratic-Republicans were part of a faction led by John Quincy Adams and Henry Clay.

Rhode Island used a statewide at-large system for electing members to Congress.

Rhode Island’s election law allowed voters to cast two ballots, and required candidates to receive a majority of votes to be elected. Since two candidates did not receive the required majority in the general election, on November 25, 1825 a [runoff ballot](https://elections.lib.tufts.edu/catalog/tufts:ri.uscongress1.1825) elected Dutee J. Pearce to Rhode Island’s second seat.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
