---
meae-id: meae.congressional.congress12.va.county
type: congressional
level: state
state: Virginia
geography: county
congressnum: 12
congressordinal: 12th
title: '12th Congress: Virginia 1811'
year: 1811
legend: dissrep
nnv:
- id: va.uscongress.1.1811
  name: VA US Congress 1811 District 1
- id: va.uscongress.2.1811
  name: VA US Congress 1811 District 2
- id: va.uscongress.3.1811
  name: VA US Congress 1811 District 3
- id: va.uscongress.4.1811
  name: VA US Congress 1811 District 4
- id: va.uscongress.5.1811
  name: VA US Congress 1811 District 5
- id: va.uscongress.6.1811
  name: VA US Congress 1811 District 6
- id: va.uscongress.7.1811
  name: VA US Congress 1811 District 7
- id: va.uscongress.8.1811
  name: VA US Congress 1811 District 8
- id: va.uscongress.9.1811
  name: VA US Congress 1811 District 9
- id: va.uscongress.10.1811
  name: VA US Congress 1811 District 10
- id: va.uscongress.11.1811
  name: VA US Congress 1811 District 11
- id: va.uscongress.12.1811
  name: VA US Congress 1811 District 12
- id: va.uscongress.13.1811
  name: VA US Congress 1811 District 13
- id: va.uscongress.14.1811
  name: VA US Congress 1811 District 14
- id: va.uscongress.15.1811
  name: VA US Congress 1811 District 15
- id: va.uscongress.16.1811
  name: VA US Congress 1811 District 16
- id: va.uscongress.17.1811
  name: VA US Congress 1811 District 17
- id: va.uscongress.18.1811
  name: VA US Congress 1811 District 18
- id: va.uscongress.19.1811
  name: VA US Congress 1811 District 19
- id: va.uscongress.20.1811
  name: VA US Congress 1811 District 20
- id: va.uscongress.21.1811
  name: VA US Congress 1811 District 21
- id: va.uscongress.22.1811
  name: VA US Congress 1811 District 22
related-maps:
- id: meae.congressional.congress11.va.county
  name: VA 11th Congress
  type: previous
- id: meae.congressional.congress13.va.county
  name: VA 13th Congress
  type: next
#- id: meae.congressional.congress12.national.district
#  name: National 12th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress12.va.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "550px", congress = 12)
```

</div>

Virginia elected six Federalist, fifteen Democratic-Republicans, and one Republican who was part of a faction within the party to the Twelfth Congress. The dissenting Republican in this election was a Tertium Quid (or just Quid), a coalition of Federalists and moderate Democratic-Republicans.

Mapping this election is incomplete because of the lack of local returns in many areas.

Virginia used the district system for electing members to Congress.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
