---
meae-id: meae.congressional.congress10.vt.county
type: congressional
level: state
state: Vermont
geography: county
congressnum: 10
congressordinal: 10th
title: '10th Congress: Vermont 1806'
year: 1806
legend: fed-vs-rep
nnv:
- id: vt.uscongress.southwest.1806
  name: VT US Congress 1806 District 1
- id: vt.uscongress.southeast.1806
  name: VT US Congress 1806 District 2
- id: vt.uscongress.northeast.1806
  name: VT US Congress 1806 District 3
- id: vt.uscongress.northwest.1806
  name: VT US Congress 1806 District 4
related-maps:
- id: meae.congressional.congress09.vt.county
  name: VT 9th Congress
  type: previous
- id: meae.congressional.congress11.vt.county
  name: VT 11th Congress
  type: next
# - id: meae.congressional.congress10.national.district
#   name: National 10th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress10.vt.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "600px", congress = 10)
```

</div>

Vermont elected two Federalists and two Democratic-Republicans to the Tenth Congress.

The map for this election is incomplete due to the lack of returns at the town or county level.

Vermont used the district system for electing members to Congress.

In 1808, a [special election](https://elections.lib.tufts.edu/catalog/tufts:vt.uscongress.southwest.special.1808) was held in which Democrat Samuel Shaw was elected to replace James Witherell, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
