---
meae-id: meae.congressional.congress06.nh.county
type: congressional
level: state
state: New Hampshire
geography: county
congressnum: 6
congressordinal: 6th
title: '6th Congress: New Hampshire 1798'
year: 1798
legend: fed-vs-rep
nnv:
- id: nh.uscongress.1798
  name: NH US Congress 1798 At Large
related-maps:
- id: meae.congressional.congress05.nh.county
  name: NH 5th Congress
  type: previous
- id: meae.congressional.congress07.nh.county
  name: NH 7th Congress
  type: next
# - id: meae.congressional.congress06.national.district
#   name: National 6th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress06.nh.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "700px", congress = 6)
```

</div>

New Hampshire elected four Federalists to the Sixth Congress.

New Hampshire used a statewide at-large method for electing members to Congress.

In November 1799, a [special election](https://elections.lib.tufts.edu/catalog/tufts:nh.uscongress.special.1799) was held in which Federalist James Sheafe was elected to replace Federalist Peleg Sprague, who had resigned from office.

In [August 1800](https://elections.lib.tufts.edu/catalog/tufts:nh.uscongress.special.1800) and [October 1800](https://elections.lib.tufts.edu/catalog/tufts:nh.uscongress.special.2.1800), two special elections were held in which Federalist Samuel Tenney was elected to replace Federalist William Gordon, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
