---
meae-id: meae.congressional.congress19.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 19
congressordinal: 19th
title: '19th Congress: Delaware 1824'
year: 1824
legend: fed-vs-rep
nnv:
- id: de.uscongress.1824
  name: DE US Congress 1824 At Large
related-maps:
- id: meae.congressional.congress18.de.county
  name: DE 18th Congress
  type: previous
#- id: meae.congressional.congress19.national.district
#  name: National 19th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress19.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Delaware elected one Federalist to the Nineteenth Congress.

Delaware used a statewide at-large system for electing members to Congress. Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. The at-large winner was then declared the winner.  This map depicts the initial winner.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
