---
meae-id: meae.congressional.congress10.nj.county
type: congressional
level: state
state: New Jersey
geography: county
congressnum: 10
congressordinal: 10th
title: '10th Congress: New Jersey 1806'
year: 1806
legend: fed-vs-rep
nnv:
- id: nj.uscongress.1806
  name: NJ US Congress 1806 At Large
related-maps:
- id: meae.congressional.congress09.nj.county
  name: NJ 9th Congress
  type: previous
- id: meae.congressional.congress11.nj.county
  name: NJ 11th Congress
  type: next
- id: meae.congressional.congress10.national.county
  name: National 10th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress10.nj.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "700px", congress = 10)
```

</div>

New Jersey elected six Democratic-Republicans to the Tenth Congress.

The map for this election is incomplete due to the lack of returns at the town or county level.

New Jersey used a statewide at-large method for electing members to Congress.

In 1808, a [special election](http://earlyamericanelections.org/dev/maps/meae.congressional.congress10.nj.county.html) was held in which Democratic-Republican Adam Boyd was elected to replace Ezra Darby, who died while in office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
