---
meae-id: meae.congressional.congress10.ny.county
type: congressional
level: state
state: New York
geography: county
congressnum: 10
congressordinal: 10th
title: '10th Congress: New York 1806'
year: 1806
legend: dissrep
nnv:
- id: ny.uscongress1.1806
  name: NY US Congress 1806 District 1
- id: ny.uscongress2and3.1806
  name: NY US Congress 1806 District 2
- id: ny.uscongress4.1806
  name: NY US Congress 1806 District 4
- id: ny.uscongress5.1806
  name: NY US Congress 1806 District 5
- id: ny.uscongress6.1806
  name: NY US Congress 1806 District 6
- id: ny.uscongress7.1806
  name: NY US Congress 1806 District 7
- id: ny.uscongress8.1806
  name: NY US Congress 1806 District 8
- id: ny.uscongress9.1806
  name: NY US Congress 1806 District 9
- id: ny.uscongress10.1806
  name: NY US Congress 1806 District 10
- id: ny.uscongress11.1806
  name: NY US Congress 1806 District 11
- id: ny.uscongress12.1806
  name: NY US Congress 1806 District 12
- id: ny.uscongress13.1806
  name: NY US Congress 1806 District 13
- id: ny.uscongress14.1806
  name: NY US Congress 1806 District 14
- id: ny.uscongress15.1806
  name: NY US Congress 1806 District 15
- id: ny.uscongress16.1806
  name: NY US Congress 1806 District 16
- id: ny.uscongress17.1806
  name: NY US Congress 1806 District 17
related-maps:
- id: meae.congressional.congress09.ny.county
  name: NY 9th Congress
  type: previous
- id: meae.congressional.congress11.ny.county
  name: NY 11th Congress
  type: next
# - id: meae.congressional.congress10.national.district
#   name: National 10th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress10.ny.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "550px", congress = 10)
```

</div>

New York elected two Federalists, fourteen Democratic-Republicans, and one other Republican who was part of a faction within the party to the Tenth Congress. The Republican faction in this election was the Tertium Quids (or just Quids), a coalition of Federalists and moderate Democratic-Republicans.

New York used the district system for electing members to Congress. Districts 2 and 3 (New York City and Brooklyn) voted together as a single district and elected two members to Congress.

In 1808, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.uscongress12.special.1808) was held in which Democratic-Republican Nathan Wilson was elected to replace David Thomas, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
