---
meae-id: meae.congressional.congress17.me.county
type: congressional
level: state
state: Maine
geography: county
congressnum: 17
congressordinal: 17th
title: '17th Congress: Maine 1820'
year: 1820
legend: fed-vs-rep
nnv:
- id: me.uscongress1.1820
  name: ME US Congress 1820 District 1
- id: me.uscongress2.1820
  name: ME US Congress 1820 District 2
- id: me.uscongress3.1820
  name: ME US Congress 1820 District 3
- id: me.uscongress4.thirdrunoff.1821
  name: ME US Congress 1821 District 4
- id: me.uscongress5.second.1821
  name: ME US Congress 1821 District 5
- id: me.uscongress6.1820
  name: ME US Congress 1820 District 6
- id: me.uscongress7.1820
  name: ME US Congress 1820 District 7
related-maps:
- id: meae.congressional.congress16.ma.county
  name: MA 16th Congress
  type: previous
- id: meae.congressional.congress18.me.county
  name: ME 18th Congress
  type: next
#- id: meae.congressional.congress17.national.district
#  name: National 17th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress17.me.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data(election_date = "1820-03-16") %>%
  map_counties()
```

</div>

Maine elected two Federalists and five Democratic-Republican to the Seventeenth Congress.

The map for this election is incomplete due to the lack of returns at the town or county level.

Maine used a district system for electing members to Congress. 

In 1822, a [special election](https://elections.lib.tufts.edu/catalog/tufts:me.uscongress2.1822) was held in which Mark Harris was elected to replace Ezekial Whitman, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
