---
meae-id: meae.congressional.congress08.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 8
congressordinal: 8th
title: '8th Congress: Delaware 1802'
year: 1802
legend: fed-vs-rep
nnv:
- id: de.uscongress.1802
  name: DE US Congress 1802 At Large
related-maps:
- id: meae.congressional.congress07.de.county
  name: DE 7th Congress
  type: previous
- id: meae.congressional.congress09.de.county
  name: DE 9th Congress
  type: next
# - id: meae.congressional.congress08.national.district
#   name: National 8th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress08.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Delaware elected one Democratic-Republican to the Eighth Congress.

Delaware used a statewide at-large method for electing a member to Congress. Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. The at-large winner was then declared the winner. This map depicts the initial winners.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
