---
meae-id: meae.congressional.congress10.pa.county
type: congressional
level: state
state: Pennsylvania
geography: county
congressnum: 10
congressordinal: 10th
title: '10th Congress: Pennsylvania 1806'
year: 1806
legend: dissrep
nnv:
- id: pa.uscongress1.1806
  name: PA US Congress 1806 District 1
- id: pa.uscongress2.1806
  name: PA US Congress 1806 District 2
- id: pa.uscongress3.1806
  name: PA US Congress 1806 District 3
- id: pa.uscongress4.1806
  name: PA US Congress 1806 District 4
- id: pa.uscongress5.1806
  name: PA US Congress 1806 District 5
- id: pa.uscongress6.1806
  name: PA US Congress 1806 District 6
- id: pa.uscongress7.1806
  name: PA US Congress 1806 District 7
- id: pa.uscongress8.1806
  name: PA US Congress 1806 District 8
- id: pa.uscongress9.1806
  name: PA US Congress 1806 District 9
- id: pa.uscongress10.1806
  name: PA US Congress 1806 District 10
- id: pa.uscongress11.1806
  name: PA US Congress 1806 District 11
related-maps:
- id: meae.congressional.congress09.pa.county
  name: PA 9th Congress
  type: previous
- id: meae.congressional.congress11.pa.county
  name: PA 11th Congress
  type: next
# - id: meae.congressional.congress10.national.district
#   name: National 10th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress10.pa.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~federalist_vote, ~demrep_vote,
    "Philadelphia", 39.9526, -75.1652, 0.54, 0.46, 6298, 5355)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", cities = 0, congress = 10) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1<br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city) 
```

</div>

Pennsylvania elected four Federalists, twelve Democratic-Republicans, and two other Republicans who were part of a faction within the party to the Tenth Congress. The Republican faction in this election was the Tertium Quids (or just Quids), a coalition of Federalists and moderate Democratic-Republicans.

Pennsylvania used a district system for electing members to Congress. Each district elected one member of Congress except District 4, which elected two members, and Districts 1, 2, and 3, which each elected three members. The votes cast in Warren County are included in the Venango County totals. 

In 1808, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress1.specialelection.1808) was held in which Democratic-Republican Benjamin Say was elected to replace Joseph Clay, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
