---
meae-id: meae.congressional.congress15.pa.county
type: congressional
level: state
state: Pennsylvania
geography: county
congressnum: 15
congressordinal: 15th
title: '15th Congress: Pennsylvania 1816'
year: 1816
legend: dissrep
nnv:
- id: pa.uscongress1.1816
  name: PA US Congress 1816 District 1
- id: pa.uscongress2.1816
  name: PA US Congress 1816 District 2
- id: pa.uscongress3.1816
  name: PA US Congress 1816 District 3
- id: pa.uscongress4.1816
  name: PA US Congress 1816 District 4
- id: pa.uscongress5.1816
  name: PA US Congress 1816 District 5
- id: pa.uscongress6.1816
  name: PA US Congress 1816 District 6
- id: pa.uscongress7.1816
  name: PA US Congress 1816 District 7
- id: pa.uscongress8.1816
  name: PA US Congress 1816 District 8
- id: pa.uscongress9.1816
  name: PA US Congress 1816 District 9
- id: pa.uscongress10.1816
  name: PA US Congress 1816 District 10
- id: pa.uscongress11.1816
  name: PA US Congress 1816 District 11
- id: pa.uscongress12.1816
  name: PA US Congress 1816 District 12
- id: pa.uscongress13.1816
  name: PA US Congress 1816 District 13
- id: pa.uscongress14.1816
  name: PA US Congress 1816 District 14
- id: pa.uscongress15.1816
  name: PA US Congress 1816 District 15
related-maps:
- id: meae.congressional.congress14.pa.county
  name: PA 14th Congress
  type: previous
- id: meae.congressional.congress16.pa.county
  name: PA 16th Congress
  type: next
#- id: meae.congressional.congress15.national.district
#  name: National 15th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress15.pa.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~repfac_percentage, ~federalist_vote, ~demrep_vote, ~repfac_vote,
    "Philadelphia", 39.9526, -75.1652, 0.568, 0.212, 0.219, 10602, 3963, 4086)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", cities = 0, congress = 15) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1<br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)<br/>",
                                 "Republican Factions: ", repfac_percentage * 100, "% (", 
                                 prettyNum(repfac_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city) 
```

</div>

Pennsylvania elected five Federalists and eighteen Democratic-Republicans to the Fifteenth Congress. Three of the Republicans elected were members of an identifiable faction within the party. In Pennsylvania some candidates ran as Old School or New School Republicans, and were divided by disputes over banking, credit, and paper currency.

Mapping this election is incomplete because of the lack of local returns in many areas.

Pennsylvania used a district system for electing members to Congress. District 1 elected four representatives. Districts 2, 3, 5, 6, and 10 each elected two representatives. 

In 1817, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.special.congress.1817) was held in which John Murray was elected to replace David Scott, who had resigned his office. 

In 1818, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress.4.special.1818) was held in which Jacob Hostetterwas elected to replace Jacob Spengler, who had resigned from office. 

In 1818, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress.6.specialelection2.1818) was held in which Thomas J. Rogers was elected to replace John Ross, who had resigned from office. 

In 1818, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress.6.specialelection.1818) was held in which Samuel Moore was elected to replace Samuel D. Ingham, who had resigned from office. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
