---
meae-id: meae.congressional.congress19.va.county
type: congressional
level: state
state: Virginia
geography: county
congressnum: 19
congressordinal: 19th
title: '19th Congress: Virginia 1825'
year: 1825
legend: congress-18-19
nnv:
- id: va.congress.1.1825
  name: VA US Congress 1825 District 1
- id: va.congress.2.1825
  name: VA US Congress 1825 District 2
- id: va.congress.3.1825
  name: VA US Congress 1825 District 3
- id: va.congress.4.1825
  name: VA US Congress 1825 District 4
- id: va.congress.5.1825
  name: VA US Congress 1825 District 5
- id: va.congress.6.1825
  name: VA US Congress 1825 District 6
- id: va.congress.7.1825
  name: VA US Congress 1825 District 7
- id: va.congress.8.1825
  name: VA US Congress 1825 District 8
- id: va.congress.9.1825
  name: VA US Congress 1825 District 9
- id: va.congress.10.1825
  name: VA US Congress 1825 District 10
- id: va.congress.11.1825
  name: VA US Congress 1825 District 11
- id: va.congress.12.1825
  name: VA US Congress 1825 District 12
- id: va.congress.13.1825
  name: VA US Congress 1825 District 13
- id: va.congress.14.1825
  name: VA US Congress 1825 District 14
- id: va.congress.15.1825
  name: VA US Congress 1825 District 15
- id: va.congress.16.1825
  name: VA US Congress 1825 District 16
- id: va.congress.17.1825
  name: VA US Congress 1825 District 17
- id: va.congress.18.1825
  name: VA US Congress 1825 District 18
- id: va.congress.19.1825
  name: VA US Congress 1825 District 19
- id: va.congress.20.1825
  name: VA US Congress 1825 District 20
- id: va.congress.21.1825
  name: VA US Congress 1825 District 21
- id: va.congress.22.1825
  name: VA US Congress 1825 District 22
related-maps:
- id: meae.congressional.congress18.va.county
  name: VA 18th Congress
  type: previous
#- id: meae.congressional.congress19.national.district
#  name: National 19th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress19.va.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "550px", congress = 19)
```

</div>

Virginia elected three twenty-two Democratic-Republicans to the Nineteenth Congress. Fourteen of those Democratic-Republicans were part of a faction led by Andrew Jackson, and seven of the Democratic-Republicans was part of a faction led by John Quincy Adams and Henry Clay.

The map for this election is incomplete due to the lack of returns in several counties.

Virginia used a district system for electing members to Congress.

In 1826, a [special election](https://elections.lib.tufts.edu/catalog/tufts:va.congress.5.special.1826) was held in which George W. Crump was elected to replace John Randolph, who had resigned after being appointed to the United States Senate.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
