---
meae-id: meae.congressional.congress14.pa.county
type: congressional
level: state
state: Pennsylvania
geography: county
congressnum: 14
congressordinal: 14th
title: '14th Congress: Pennsylvania 1814'
year: 1814
legend: fed-vs-rep
nnv:
- id: pa.uscongress1.1814
  name: PA US Congress 1814 District 1
- id: pa.uscongress2.1814
  name: PA US Congress 1814 District 2
- id: pa.uscongress3.1814
  name: PA US Congress 1814 District 3
- id: pa.uscongress4.1814
  name: PA US Congress 1814 District 4
- id: pa.uscongress5.1814
  name: PA US Congress 1814 District 5
- id: pa.uscongress6.1814
  name: PA US Congress 1814 District 6
- id: pa.uscongress7.1814
  name: PA US Congress 1814 District 7
- id: pa.uscongress8.1814
  name: PA US Congress 1814 District 8
- id: pa.uscongress9.1814
  name: PA US Congress 1814 District 9
- id: pa.uscongress10.1814
  name: PA US Congress 1814 District 10
- id: pa.uscongress11.1814
  name: PA US Congress 1814 District 11
- id: pa.uscongress12.1814
  name: PA US Congress 1814 District 12
- id: pa.uscongress13.1814
  name: PA US Congress 1814 District 13
- id: pa.uscongress14.1814
  name: PA US Congress 1814 District 14
- id: pa.uscongress15.1814
  name: PA US Congress 1814 District 15
related-maps:
- id: meae.congressional.congress13.pa.county
  name: PA 13th Congress
  type: previous
- id: meae.congressional.congress15.pa.county
  name: PA 15th Congress
  type: next
#- id: meae.congressional.congress14.national.district
#  name: National 14th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress14.pa.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~federalist_vote, ~demrep_vote,
    "Philadelphia", 39.9526, -75.1652, 0.571, 0.429, 11860, 8908)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", cities = 0, congress = 14) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1<br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city) 
```

</div>

Pennsylvania elected seven Federalist and sixteen Democratic-Republicans to the Fourteenth Congress.

Pennsylvania used a district system for electing members to Congress. Each district elected one member of Congress except District 1, which elected four members, and Districts 2, 3, 5, 6, and 10, which each elected two members. The votes cast in Warren County are included in the Venango County totals.

In 1815, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress1.specialelection.1815) was held in which John Sergeant was elected to replace Jonathan Williams, who had died. 

In 1815, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress3.specialelection.1815) was held in which James Wallace was elected to replace Amos Ellmaker, who had resigned his office. 

In 1815, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress9.specialelection.1815) was held in which Thomas Burnside was elected to replace David Bard, who had died.

In 1816, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress9.specialelection.1816) was held in which William P. Maclay was elected to replace Thomas Burnside, who had resigned his office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
