---
meae-id: meae.congressional.congress14.ma.county
type: congressional
level: state
state: Massachusetts
geography: county
congressnum: 14
congressordinal: 14th
title: '14th Congress: Massachusetts 1814'
year: 1814
legend: fed-vs-rep
nnv:
- id: ma.uscongress.suffolk.1814
  name: MA US Congress 1814 District 1
- id: ma.uscongress.essexsouth.1814
  name: MA US Congress 1814 District 2
- id: ma.uscongress.essexnorth.1814
  name: MA US Congress 1814 District 3
- id: ma.uscongress.middlesex.1814
  name: MA US Congress 1814 District 4
- id: ma.uscongress.hampshiresouth.1814
  name: MA US Congress 1814 District 5
- id: ma.uscongress.hampshirenorth.1814
  name: MA US Congress 1814 District 6
- id: ma.uscongress.berkshire.1814
  name: MA US Congress 1814 District 7
- id: ma.uscongress.plymouth.1814
  name: MA US Congress 1814 District 8
- id: ma.uscongress.barnstable.1814
  name: MA US Congress 1814 District 9
- id: ma.uscongress.bristol.1814
  name: MA US Congress 1814 District 10
- id: ma.uscongress.worcestersouth.1814
  name: MA US Congress 1814 District 11
- id: ma.uscongress.worcesternorth.1814
  name: MA US Congress 1814 District 12
- id: ma.uscongress.norfolk.1814
  name: MA US Congress 1814 District 13
- id: ma.uscongress.eastern1.1814
  name: MA US Congress 1814 District 14
- id: ma.uscongress.eastern2.1814
  name: MA US Congress 1814 District 15
- id: ma.uscongress.eastern3.1814
  name: MA US Congress 1814 District 16
- id: ma.uscongress.eastern4.ballot2.1815
  name: MA US Congress 1815 District 17
- id: ma.uscongress.eastern5.1814
  name: MA US Congress 1814 District 18
- id: ma.uscongress.eastern6.ballot2.1815
  name: MA US Congress 1815 District 19
- id: ma.uscongress.eastern7.1814
  name: MA US Congress 1814 District 20
related-maps:
- id: meae.congressional.congress13.ma.county
  name: MA 13th Congress
  type: previous
- id: meae.congressional.congress15.ma.county
  name: MA 15th Congress
  type: next
#- id: meae.congressional.congress14.national.district
#  name: National 14th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress14.ma.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties() %>% 
  fitBounds(-73.508, 41.186, -69.861, 43.75)
```

</div>

Massachusetts elected eighteen Federalists and two Democratic-Republicans to the Fourteenth Congress.

Massachusetts used a district system for electing members to Congress. 

In 1815, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.essexnorth.special.1815) was held in which Jeremiah Nelson was elected to replace Daniel A White, who had resigned his office. 

In 1816, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.worcestersouth.special.1816) was held in which Benjamin Adams was elected to replace Elijah Brigham, who died.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
