---
meae-id: meae.congressional.congress02.ga.county
type: congressional
level: state
state: Georgia
geography: county
congressnum: 2
congressordinal: 2nd
title: '2nd Congress: Georgia 1791'
year: 1791
legend: fed-vs-anti
nnv:
- id: ga.uscongress.SouthernDistrict.1791
  name: GA US Congress 1791 District 1
- id: ga.uscongress.MiddleDistrict.1791
  name: GA US Congress 1791 District 2
- id: ga.uscongress.NorthernDistrict.1791
  name: GA US Congress 1791 District 3
related-maps:
- id: meae.congressional.congress01.ga.county
  name: GA 1st Congress
  type: previous
- id: meae.congressional.congress03.ga.county
  name: GA 3rd Congress
  type: next
- id: meae.congressional.congress02.national.county
  name: National 2nd Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)
library(sf)

map_id <- "meae.congressional.congress02.ga.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  filter(id != "gas_nca") %>% 
  map_counties(height = "525px") 
```

</div>

Georgia elected two Anti-Federalists and one Federalist to the Second Congress. 

Georgia used a state-wide at-large system for electing members to Congress, but candidates had to be resident in the district to which they were elected.

The election between Anthony Wayne and James Jackson in the first district was contested, and the results from Effingham and Camden counties were ruled invalid. A [special election](http://elections.lib.tufts.edu/catalog/tufts:ga.uscongress.special.1792) was held in July, 1792, in which Republican John Millage defeated the Federalist Matthew McAllister.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
