---
meae-id: meae.congressional.congress14.ny.county
type: congressional
level: state
state: New York
geography: county
congressnum: 14
congressordinal: 14th
title: '14th Congress: New York 1815'
year: 1815
legend: fed-vs-rep
nnv:
- id: ny.uscongress1.1814
  name: NY US Congress 1814 District 1
- id: ny.uscongress2.1814
  name: NY US Congress 1814 District 2
- id: ny.uscongress3.1814
  name: NY US Congress 1814 District 3
- id: ny.uscongress4.1814
  name: NY US Congress 1814 District 4
- id: ny.uscongress5.1814
  name: NY US Congress 1814 District 5
- id: ny.uscongress6.1814
  name: NY US Congress 1814 District 6
- id: ny.uscongress7.1814
  name: NY US Congress 1814 District 7
- id: ny.uscongress8.1814
  name: NY US Congress 1814 District 8
- id: ny.uscongress9.1814
  name: NY US Congress 1814 District 9
- id: ny.uscongress10.1814
  name: NY US Congress 1814 District 10
- id: ny.uscongress11.1814
  name: NY US Congress 1814 District 11
- id: ny.uscongress12.special.1815
  name: NY US Congress 1815 District 12
- id: ny.uscongress13.1814
  name: NY US Congress 1814 District 13
- id: ny.uscongress14.1814
  name: NY US Congress 1814 District 14
- id: ny.uscongress15.1814
  name: NY US Congress 1814 District 15
- id: ny.uscongress16.1814
  name: NY US Congress 1814 District 16
- id: ny.uscongress17.1814
  name: NY US Congress 1814 District 17
- id: ny.uscongress18.1814
  name: NY US Congress 1814 District 18
- id: ny.uscongress19.1814
  name: NY US Congress 1814 District 19
- id: ny.uscongress20.1814
  name: NY US Congress 1814 District 20
- id: ny.uscongress21.1814
  name: NY US Congress 1814 District 21
related-maps:
- id: meae.congressional.congress13.ny.county
  name: NY 13th Congress
  type: previous
- id: meae.congressional.congress15.ny.county
  name: NY 15th Congress
  type: next
#- id: meae.congressional.congress14.national.district
#  name: National 14th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress14.ny.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "725px", congress = 14)
```

</div>

New York elected six Federalists and twenty Democratic-Republicans to the Fourteenth Congress. 

New York used a district system for electing members to Congress. Districts 1, 2, 15, 20, and 21 elected two representatives each. 

In 1815, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.uscongress12.special.1815) was held in which Asa Adgate was elected to replace Benjamin Bond, who had died. 

In 1815, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.uscongress6.special.1815) was held in which James W. Wilkin was elected to replace Jonathan Fisk, who had resigned. 

In 1816, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.uscongress20.special.1816) was held in which Daniel Avery was elected to replace Enos T. Throo, who had resigned. 

In 1816, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.uscongress21.special.1816) was held in which Archibald S. Clark was elected to replace Peter B. Porter, who had resigned. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
