---
meae-id: meae.congressional.congress18.va.county
type: congressional
level: state
state: Virginia
geography: county
congressnum: 18
congressordinal: 18th
title: '18th Congress: Virginia 1823'
year: 1823
legend: fed-vs-rep
nnv:
- id: va.congress.1.1823
  name: VA US Congress 1823 District 1
- id: va.congress.2.1823
  name: VA US Congress 1823 District 2
- id: va.congress.3.1823
  name: VA US Congress 1823 District 3
- id: va.congress.4.1823
  name: VA US Congress 1823 District 4
- id: va.congress.5.1823
  name: VA US Congress 1823 District 5
- id: va.congress.6.1823
  name: VA US Congress 1823 District 6
- id: va.congress.7.1823
  name: VA US Congress 1823 District 7
- id: va.congress.8.1823
  name: VA US Congress 1823 District 8
- id: va.congress.9.1823
  name: VA US Congress 1823 District 9
- id: va.congress.10.1823
  name: VA US Congress 1823 District 10
- id: va.congress.11.1823
  name: VA US Congress 1823 District 11
- id: va.congress.12.1823
  name: VA US Congress 1823 District 12
- id: va.congress.13.1823
  name: VA US Congress 1823 District 13
- id: va.congress.14.1823
  name: VA US Congress 1823 District 14
- id: va.congress.15.1823
  name: VA US Congress 1823 District 15
- id: va.congress.16.1823
  name: VA US Congress 1823 District 16
- id: va.congress.17.1823
  name: VA US Congress 1823 District 17
- id: va.congress.18.1823
  name: VA US Congress 1823 District 18
- id: va.congress.19.1823
  name: VA US Congress 1823 District 19
- id: va.congress.20.1823
  name: VA US Congress 1823 District 20
- id: va.congress.21.1823
  name: VA US Congress 1823 District 21
- id: va.congress.22.1823
  name: VA US Congress 1823 District 22
related-maps:
- id: meae.congressional.congress17.va.county
  name: VA 17th Congress
  type: previous
- id: meae.congressional.congress19.va.county
  name: VA 19th Congress
  type: next
#- id: meae.congressional.congress18.national.district
#  name: National 18th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress18.va.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "550px", congress = 18)
```

</div>

Virginia elected three Federalists and nineteen Democratic-Republicans to the Eighteenth Congress.

Mapping this election is incomplete because of the lack of local returns in many areas.

Virginia used a district system for electing members to Congress. Virginia was apportioned one less seat in the House of Representatives. 

In 1822, a [special election](https://elections.lib.tufts.edu/catalog/tufts:va.special.uscongress.13.1824) was held in which John Taliaferro was elected to replace William Lee Ball, who had died.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
