---
meae-id: meae.congressional.congress04.ct.county
type: congressional
level: state
state: Connecticut
geography: county
congressnum: 4
congressordinal: 4th
title: '4th Congress: Connecticut 1794'
year: 1794
legend: fed-vs-rep
nnv:
- id: ct.congress.1794
  name: CT US Congress 1794 At Large
related-maps:
- id: meae.congressional.congress03.ct.county
  name: CT 3rd Congress
  type: previous
- id: meae.congressional.congress05.ct.county
  name: CT 5th Congress
  type: next
- id: meae.congressional.congress04.national.county
  name: National 4th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)
library(sf)

map_id <- "meae.congressional.congress04.ct.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  filter(id != "cts_wr") %>% 
  map_counties(height = "350px", congress = 4)
```

</div>

Connecticut elected seven Federalists to the Fourth Congress, five of whom were incumbents. 

Mapping this election is not possible because there are insufficient returns at the town and county levels. 

Connecticut used a statewide at-large system for electing members to Congress. 

In May 1795, Nathaniel Smith was elected in a [special election](https://elections.lib.tufts.edu/catalog/tufts:ct.special.congress.1795) to fill the seat vacated by Jonathan Trumbull after he was elected to the U.S. Senate.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
