---
meae-id: meae.congressional.congress08.ct.county
type: congressional
level: state
state: Connecticut
geography: county
congressnum: 8
congressordinal: 8th
title: '8th Congress: Connecticut 1802'
year: 1802
legend: fed-vs-rep
nnv:
- id: ct.congress.1802
  name: CT US Congress 1802 At Large
related-maps:
- id: meae.congressional.congress07.ct.county
  name: CT 7th Congress
  type: previous
- id: meae.congressional.congress09.ct.county
  name: CT 9th Congress
  type: next
# - id: meae.congressional.congress08.national.district
#   name: National 8th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)
library(sf)

map_id <- "meae.congressional.congress08.ct.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  filter(id != "cts_wr") %>% 
  map_counties(height = "350px", congress = 8)
```

</div>

Connecticut elected seven Federalists to the Eighth Congress.

Mapping this election is not possible because of the lack of returns at the town or county level.

Connecticut used a statewide at-large method for electing members to Congress.

In 1803, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ct.uscongress.1803) was held in which Federalist Simeon Baldwin was elected to replace Elias Perkins, who had resigned before the 8th Congress convened.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table(keep_percentage = 0.01) %>%
  cat()
```

</div>
