---
meae-id: meae.congressional.congress19.in.county
type: congressional
level: state
state: Indiana
geography: county
congressnum: 19
congressordinal: 19th
title: '19th Congress: Indiana 1824'
year: 1824
legend: congress-18-19
nnv:
- id: in.usrepresentative.1st.1824
  name: IN US Congress 1824 District 1
- id: in.usrepresentative.2nd.1824
  name: IN US Congress 1824 District 2
- id: in.usrepresentative.3rd.1824
  name: IN US Congress 1824 District 3
related-maps:
- id: meae.congressional.congress18.in.county
  name: IN 18th Congress
  type: previous
#- id: meae.congressional.congress19.national.district
#  name: National 19th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress19.in.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  filter(id != "ins_nca4",
         id != "ins_nca6") %>%
  map_counties(height = "775px")
```

</div>

Indiana elected three Democratic-Republican to the Nineteenth Congress. Two of those Democratic-Republicans were part of a faction led by John Quincy Adams and Henry Clay, and the other Democratic-Republican was part of a faction led by Andrew Jackson.

Indiana used a statewide at-large system for electing members to Congress.

In 1823, a [special election](https://elections.lib.tufts.edu/catalog/tufts:in.usrepresentative.1st.special.1824) was held in which Jacob Call was elected to replace William Prince, who had died.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
