---
meae-id: meae.congressional.congress11.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 11
congressordinal: 11th
title: '11th Congress: Delaware 1808'
year: 1808
legend: fed-vs-rep
nnv:
- id: de.uscongress.1808
  name: DE US Congress 1808 At Large
related-maps:
- id: meae.congressional.congress10.de.county
  name: DE 10th Congress
  type: previous
- id: meae.congressional.congress12.de.county
  name: DE 12th Congress
  type: next
#- id: meae.congressional.congress11.national.district
#  name: National 11th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress11.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Delaware elected one Federalist to the Eleventh Congress.

Delaware used a statewide at-large method for electing members to Congress. Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. The at-large winner was then declared the winner.  This map depicts the initial winner.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
