---
meae-id: meae.congressional.congress13.tn.county
type: congressional
level: state
state: Tennessee
geography: county
congressnum: 13
congressordinal: 13th
title: '13th Congress: Tennessee 1813'
year: 1813
legend: fed-vs-rep
nnv:
- id: tn.congress.1.1813
  name: TN US Congress 1813 District 1
- id: tn.congress.2.1813
  name: TN US Congress 1813 District 2
- id: tn.congress.3.1813
  name: TN US Congress 1813 District 3
- id: tn.congress.4.1813
  name: TN US Congress 1813 District 4
- id: tn.congress.5.1813
  name: TN US Congress 1813 District 5
- id: tn.congress.6.1813
  name: TN US Congress 1813 District 6
related-maps:
- id: meae.congressional.congress12.tn.county
  name: TN 12th Congress
  type: previous
- id: meae.congressional.congress14.tn.county
  name: TN 14th Congress
  type: next
#- id: meae.congressional.congress13.national.district
#  name: National 13th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress13.tn.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>% 
  filter(id != "tns_nca4",
         id != "tns_nca7") %>% 
  map_counties(height = "300px", congress = 13)
```

</div>

Tennessee elected six Democratic-Republicans to the Thirteenth Congress.

The map for this election is incomplete due to the lack of returns at the town or county level.

Tennessee used a district system for electing members to Congress. Tennessee was apportioned three more seats in the House of Representatives.

In 1814, a [special election](https://elections.lib.tufts.edu/catalog/tufts:tn.special.congress.5.1814) was held in which Newton Cannon was elected to replace Felix Grundy, who had resigned. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
