---
meae-id: meae.congressional.congress01.pa.county
type: congressional
level: state
state: Pennsylvania
geography: county
congressnum: 1
congressordinal: 1st
title: '1st Congress: Pennsylvania 1788'
year: 1788
nnv:
- id: pa.congress.atlarge.1788
  name: PA US Congress 1788 At Large
related-maps:
- id: meae.congressional.congress02.pa.county
  name: PA Second Congress
  type: next
- id: meae.congressional.congress01.national.district
  name: National First Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress01.pa.county"
cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~antifederalist_percentage, ~federalist_vote, ~antifederalist_vote,
  "Philadelphia", 39.9526, -75.1652, 0.783, 0.217, 12805, 3550)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "475px", cities = 0) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: At-large<br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Anti-Federalists: ", antifederalist_percentage * 100,
                                 "% (", 
                                 prettyNum(antifederalist_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city) 
```

</div>

Elections to the First Congress from Pennsylvania were held at-large in the entire state, without residency requirements for the eight spots in the House of Representatives. 

The primary breakdown in the election was between the heavily populated counties in the southeastern part of the state near Philadelphia and the more sparsely populated counties in the rest of the state. Philadelphia and its environs voted heavily for the Federalists, while the rest of the state voted mostly Anti-Federalist. But the larger populations of the southeastern counties, especially the city of Philadelphia and the counties of York, Chester, and Bucks, produced state-wide majorities for the Federalists. Cumberland County was the only heavily populated county to vote overwhelmingly for the Federalists.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>% 
  results_to_table() %>% 
  cat()
```

</div>
