---
meae-id: meae.congressional.congress14.sc.county
type: congressional
level: state
state: South Carolina
geography: county
congressnum: 14
congressordinal: 14th
title: '14th Congress: South Carolina 1814'
year: 1814
legend: fed-vs-rep
nnv:
- id: sc.uscongress.charleston.1814
  name: SC US Congress 1814 District 1
- id: sc.uscongress.beaufort.1814
  name: SC US Congress 1814 District 2
- id: sc.uscongress.georgetown.1814
  name: SC US Congress 1814 District 3
- id: sc.uscongress.orangeburg.1814
  name: SC US Congress 1814 District 4
- id: sc.uscongress.newberry.1814
  name: SC US Congress 1814 District 5
- id: sc.uscongress.edgefield.1814
  name: SC US Congress 1814 District 6
- id: sc.uscongress.pendleton.1814
  name: SC US Congress 1814 District 7
- id: sc.uscongress.chester.1814
  name: SC US Congress 1814 District 8
- id: sc.uscongress.sumpter.1814
  name: SC US Congress 1814 District 9
related-maps:
- id: meae.congressional.congress13.sc.county
  name: SC 13th Congress
  type: previous
- id: meae.congressional.congress15.sc.county
  name: SC 15th Congress
  type: next
- id: meae.congressional.congress14.national.county
  name: National 14th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress14.sc.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~federalist_vote, ~demrep_vote,
  "Charleston", 32.7765, -79.9311, 0.382, 0.618, 751, 1216)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  filter(id != "scs_nca5") %>% 
  arrange(!is.na(federalist_percentage), !is.na(demrep_percentage), 
          cnty_type == "District") %>%
  map_counties(cities = FALSE, height = "600px") %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
               fillColor = mappingelections:::poli_chrome(cities),
               opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1<br/>",
                                 "Federalists: ", federalist_percentage * 100,
                                 "% (", 
                                 prettyNum(federalist_vote, big.mark = ","),
                                 " votes)<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city)
```

</div>

South Carolina elected one Federalist and eight Democratic-Republicans to the Fourteenth Congress.

The map for this election is incomplete due to the lack of returns in many areas.

South Carolina used a district system for electing members to Congress. 

In 1816, a [special election](https://elections.lib.tufts.edu/catalog/tufts:sc.uscongress.camden.special.1816) was held in which Stephen D. Miller was elected to replace William Mayrant, who had resigned his office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
