---
meae-id: meae.congressional.congress12.nh.county
type: congressional
level: state
state: New Hampshire
geography: county
congressnum: 12
congressordinal: 12th
title: '12th Congress: New Hampshire 1810'
year: 1810
legend: fed-vs-rep
nnv:
- id: nh.uscongress.1810
  name: NH US Congress 1810 At Large
related-maps:
- id: meae.congressional.congress11.nh.county
  name: NH 11th Congress
  type: previous
- id: meae.congressional.congress13.nh.county
  name: NH 13th Congress
  type: next
- id: meae.congressional.congress12.national.county
  name: National 12th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress12.nh.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "700px", congress = 12)
```

</div>

New Hampshire elected three Federalists and two Democratic-Republicans to the Twelfth Congress.

New Hampshire used a statewide at-large method for electing members to Congress. New Hampshire law required a majority to elect for the U.S. House of Representatives. Each voter was allotted five votes for the five seats. The percentages reflect the percent of the total votes cast. The first ballot resulted in only two representatives elected. Therefore, a [second ballot](https://elections.lib.tufts.edu/catalog/tufts:nh.uscongress.2.1811) was held to elect John A. Harper, Obed Hall, and George Sullivan. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
