---
meae-id: meae.congressional.congress07.ma.county
type: congressional
level: state
state: Massachusetts
geography: county
congressnum: 7
congressordinal: 7th
title: '7th Congress: Massachusetts 1800'
year: 1800
legend: fed-vs-rep
nnv:
- id: ma.uscongress.western.1.ballot2.1801
  name: MA US Congress 1801 District 1
- id: ma.uscongress.western.2.1800
  name: MA US Congress 1800 District 2
- id: ma.uscongress.western.3.1800
  name: MA US Congress 1800 District 3
- id: ma.uscongress.western.4.1800
  name: MA US Congress 1800 District 4
- id: ma.uscongress.southern.1.1800
  name: MA US Congress 1800 District 5
- id: ma.uscongress.southern.2.ballot2.1801
  name: MA US Congress 1801 District 6
- id: ma.uscongress.southern.3.1800
  name: MA US Congress 1800 District 7
- id: ma.uscongress.middle.1.1800
  name: MA US Congress 1800 District 8
- id: ma.uscongress.middle.2.1800
  name: MA US Congress 1800 District 9
- id: ma.uscongress.middle.3.1800
  name: MA US Congress 1800 District 10
- id: ma.uscongress.middle.4.1800
  name: MA US Congress 1800 District 11
- id: ma.uscongress.eastern.1.1800
  name: MA US Congress 1800 District 12
- id: ma.uscongress.eastern.2.1800
  name: MA US Congress 1800 District 13
- id: ma.uscongress.eastern.3.special.1801
  name: MA US Congress 1801 District 14
related-maps:
- id: meae.congressional.congress06.ma.county
  name: MA 6th Congress
  type: previous
- id: meae.congressional.congress08.ma.county
  name: MA 8th Congress
  type: next
- id: meae.congressional.congress07.national.county
  name: National 7th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress07.ma.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties() %>% 
  fitBounds(-73.508, 41.186, -69.861, 43.75)
```

</div>

Massachusetts elected seven Federalists and seven Democratic-Republicans to the Seventh Congress.

Massachusetts used the district system for electing members to Congress.

In July 1801, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.eastern.3.special.1801) was held in which Democratic-Republican Richard Cutts was elected to replace George Thatcher, who had resigned before the 7th Congress convened.

On June 22, 1801, and August 24, 1801, two special elections were held in which Federalist Seth Hastings was elected to replace Levi Lincoln, who had resigned on March 5, 1801, before the 7th Congress convened.
[Election 1](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.western.4.special.1801)
[Election 2](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.western.4.special.ballot2.1801)

Between September 25, 1801, and July 29, 1802, five special elections were held in which Federalist Samuel Thacher was elected to replace Silas Lee, who had resigned on August 20, 1801, before the 7th congress convened.
[Election 1](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.eastern.1.special.1801)
[Election 2](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.eastern.1.special.ballot2.1801)
[Election 3](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.eastern.1.special.ballot3.1802)
[Election 4](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.eastern.1.special.ballot4.1802)
[Election 5](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.eastern.1.special.ballot5.1802)

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
