---
meae-id: meae.congressional.congress13.va.county
type: congressional
level: state
state: Virginia
geography: county
congressnum: 13
congressordinal: 13th
title: '13th Congress: Virginia 1813'
year: 1813
legend: fed-vs-rep
nnv:
- id: va.uscongress.1.1813
  name: VA US Congress 1813 District 1
- id: va.uscongress.2.1813
  name: VA US Congress 1813 District 2
- id: va.uscongress.3.1813
  name: VA US Congress 1813 District 3
- id: va.uscongress.4.1813
  name: VA US Congress 1813 District 4
- id: va.uscongress.5.1813
  name: VA US Congress 1813 District 5
- id: va.uscongress.6.1813
  name: VA US Congress 1813 District 6
- id: va.uscongress.7.1813
  name: VA US Congress 1813 District 7
- id: va.uscongress.8.1813
  name: VA US Congress 1813 District 8
- id: va.uscongress.9.1813
  name: VA US Congress 1813 District 9
- id: va.uscongress.10.1813
  name: VA US Congress 1813 District 10
- id: va.uscongress.11.1813
  name: VA US Congress 1813 District 11
- id: va.uscongress.12.1813
  name: VA US Congress 1813 District 12
- id: va.uscongress.13.1813
  name: VA US Congress 1813 District 13
- id: va.uscongress.14.1813
  name: VA US Congress 1813 District 14
- id: va.uscongress.15.1813
  name: VA US Congress 1813 District 15
- id: va.uscongress.16.1813
  name: VA US Congress 1813 District 16
- id: va.uscongress.17.1813
  name: VA US Congress 1813 District 17
- id: va.uscongress.18.1813
  name: VA US Congress 1813 District 18
- id: va.uscongress.19.1813
  name: VA US Congress 1813 District 19
- id: va.uscongress.20.1813
  name: VA US Congress 1813 District 20
- id: va.uscongress.21.1813
  name: VA US Congress 1813 District 21
- id: va.uscongress.22.1813
  name: VA US Congress 1813 District 22
- id: va.uscongress.23.1813
  name: VA US Congress 1813 District 23
related-maps:
- id: meae.congressional.congress12.va.county
  name: VA 12th Congress
  type: previous
- id: meae.congressional.congress14.va.county
  name: VA 14th Congress
  type: next
#- id: meae.congressional.congress13.national.district
#  name: National 13th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress13.va.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "550px", congress = 13)
```

</div>

Virginia elected seven Federalist and sixteen Democratic-Republicans to the Thirteenth Congress.

The map for this election is incomplete due to the lack of returns in a few counties.

Virginia used a district system for electing members to Congress. Virginia was apportioned one more seat in the House of Representatives. 

In 1814, a [special election](https://elections.lib.tufts.edu/catalog/tufts:va.uscongress.11.special.1814) was held in which Philip Barbour was elected to replace John Dawson, who had died. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
