---
meae-id: meae.congressional.congress12.nh.county
type: congressional
level: state
state: New Hampshire
geography: county
congressnum: 12
congressordinal: 12th
title: '12th Congress: New Hampshire 1810'
year: 1810
legend: fed-vs-rep
nnv:
- id: nh.uscongress.1810
  name: NH US Congress 1810 At Large
related-maps:
- id: meae.congressional.congress11.nh.county
  name: NH 11th Congress
  type: previous
- id: meae.congressional.congress13.nh.county
  name: NH 13th Congress
  type: next
#- id: meae.congressional.congress12.national.district
#  name: National 12th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress12.nh.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "700px", congress = 12)
```

</div>

New Hampshire elected 3 Federalists and 2 Democratic-Republicans to the Twelfth Congress.

New Hampshire used a statewide at-large method for electing members to Congress. New Hampshire law required a majority to elect for the U.S. House of Representatives. The first ballot resulted in only two representatives elected. Therefore, a [second ballot](https://elections.lib.tufts.edu/catalog/tufts:nh.uscongress.2.1811) was held to elect the other three. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
