---
meae-id: meae.congressional.congress19.pa.county
type: congressional
level: state
state: Pennsylvania
geography: county
congressnum: 19
congressordinal: 19th
title: '19th Congress: Pennsylvania 1824'
year: 1824
legend: congress-18-19
nnv:
- id: pa.congress.1.1824
  name: PA US Congress 1824 District 1
- id: pa.congress.2.1824
  name: PA US Congress 1824 District 2
- id: pa.congress.3.1824
  name: PA US Congress 1824 District 3
- id: pa.congress.4.1824
  name: PA US Congress 1824 District 4
- id: pa.congress.5.1824
  name: PA US Congress 1824 District 5
- id: pa.congress.6.1824
  name: PA US Congress 1824 District 6
- id: pa.congress.7.1824
  name: PA US Congress 1824 District 7
- id: pa.congress.8.1824
  name: PA US Congress 1824 District 8
- id: pa.congress.9.1824
  name: PA US Congress 1824 District 9
- id: pa.congress.10.1824
  name: PA US Congress 1824 District 10
- id: pa.congress.11.1824
  name: PA US Congress 1824 District 11
- id: pa.congress.12.1824
  name: PA US Congress 1824 District 12
- id: pa.congress.13.1824
  name: PA US Congress 1824 District 13
- id: pa.congress.14.1824
  name: PA US Congress 1824 District 14
- id: pa.congress.15.1824
  name: PA US Congress 1824 District 15
- id: pa.congress.16.1824
  name: PA US Congress 1824 District 16
- id: pa.congress.17.1824
  name: PA US Congress 1824 District 17
- id: pa.congress.18.1824
  name: PA US Congress 1824 District 18
related-maps:
- id: meae.congressional.congress18.pa.county
  name: PA 18th Congress
  type: previous
#- id: meae.congressional.congress19.national.district
#  name: National 19th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress19.pa.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~jacksonian_percentage,  ~federalist_vote, ~demrep_vote, ~jacksonian_vote,
    "Philadelphia", 39.9526, -75.1652, 0.103, 0.417, 0.480, 472, 1908, 2196)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", cities = 0, congress = 19) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1, 2<br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)<br/>",
                                  "Jacksonian supporters: ", jacksonian_percentage * 100,
                                 "% (",
                                  prettyNum(jacksonian_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city)
```

</div>

Pennsylvania elected one Federalist and twenty-five Democratic-Republicans to the Nineteenth Congress. Seventeen of those Democratic-Republicans were part of a faction led by Andrew Jackson and three of those Democratic-Republicans were part of a faction led by John Quincy Adams and Henry Clay. 

The map for this election is incomplete due to the lack of returns for some counties.

Pennsylvania was apportioned three more seats in the House of Representatives.

Pennsylvania used a district system for electing members to Congress. Districts 4 and 9 elected three representatives. Districts 7, 8, 11, and 16 each elected two representatives.

In 1825, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress16.special.1825) was held in which Robert Orr was elected to replace James Allison, Jr., who had resigned from office. 

In 1826, a special election was held in which Thomas Kittera was elected to replace Joseph Hemphill, who had resigned from office. 

In 1826, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress7.special.1826) was held in which Jacob Krebs was elected to replace Henry Wilson, who had died. 

In 1826, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress13.special.1826) was held in which Chauncey Forward was elected to replace Alexander Thompson, who had resigned from office. 

In 1826, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress18.special.1826) was held in which Thomas H. Sill was elected to replace Patrick Farrelly, who had died. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
