---
meae-id: meae.congressional.congress18.ma.county
type: congressional
level: state
state: Massachusetts
geography: county
congressnum: 18
congressordinal: 18th
title: '18th Congress: Massachusetts 1822'
year: 1822
legend: congress-18-19
nnv:
- id: ma.uscongress.suffolk.1822
  name: MA US Congress 1822 District 1
- id: ma.uscongress.essexsouth.ballot2.1823
  name: MA US Congress 1823 District 2
- id: ma.uscongress.essexnorth.1822
  name: MA US Congress 1822 District 3
- id: ma.uscongress.middlesex.1822
  name: MA US Congress 1822 District 4
- id: ma.uscongress.worcestersouth.ballot2.1823
  name: MA US Congress 1823 District 5
- id: ma.uscongress.worcesternorth.ballot3.1823
  name: MA US Congress 1823 District 6
- id: ma.uscongress.franklin.1822
  name: MA US Congress 1822 District 7
- id: ma.uscongress.hampden.1822
  name: MA US Congress 1822 District 8
- id: ma.uscongress.berkshire.1822
  name: MA US Congress 1822 District 9
- id: ma.uscongress.norfolk.1822
  name: MA US Congress 1822 District 10
- id: ma.uscongress.plymouth.1822
  name: MA US Congress 1822 District 11
- id: ma.uscongress.bristol.1822
  name: MA US Congress 1822 District 12
- id: ma.uscongress.barnstable.1822
  name: MA US Congress 1822 District 13
related-maps:
- id: meae.congressional.congress17.ma.county
  name: MA 17th Congress
  type: previous
- id: meae.congressional.congress19.ma.county
  name: MA 19th Congress
  type: next
#- id: meae.congressional.congress18.national.district
#  name: National 18th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress18.ma.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Massachusetts elected eight Federalists and five Democratic-Republicans to the Eighteenth Congress. One of those Democratic-Republicans was part of a faction led by John Quincy Adams and Henry Clay. 

Massachusetts used a district system for electing members to Congress. 

Between September 1823 and November 1824, a series of [special elections](https://elections.lib.tufts.edu/catalog/BJ0321) were held to elect a replacement for William Eustis, who had resigned from office after being elected Governor of Massachusetts. Ultimately, John Baily was elected to replace him.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
