---
meae-id: meae.congressional.congress19.ky.county
type: congressional
level: state
state: Kentucky
geography: county
congressnum: 19
congressordinal: 19th
title: '19th Congress: Kentucky 1824'
year: 1824
legend: congress-18-19
nnv:
- id: ky.uscongress1.1824
  name: KY US Congress 1824 District 1
- id: ky.uscongress2.1824
  name: KY US Congress 1824 District 2
- id: ky.uscongress3.1824
  name: KY US Congress 1824 District 3
- id: ky.uscongress4.1824
  name: KY US Congress 1824 District 4
- id: ky.uscongress5.1824
  name: KY US Congress 1824 District 5
- id: ky.uscongress6.1824
  name: KY US Congress 1824 District 6
- id: ky.uscongress7.1824
  name: KY US Congress 1824 District 7
- id: ky.uscongress8.1824
  name: KY US Congress 1824 District 8
- id: ky.uscongress9.1824
  name: KY US Congress 1824 District 9
- id: ky.uscongress10.1824
  name: KY US Congress 1824 District 10
- id: ky.uscongress11.1824
  name: KY US Congress 1824 District 11
- id: ky.uscongress12.1824
  name: KY US Congress 1824 District 12
related-maps:
- id: meae.congressional.congress18.ky.county
  name: KY 18th Congress
  type: previous
#- id: meae.congressional.congress19.national.district
#  name: National 19th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress19.ky.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Kentucky elected twelve Democratic-Republicans to the Nineteenth Congress. Seven of those Democratic-Republicans were part of a faction led by John Quincy Adams and Henry Clay, and five of those Democratic-Republicans were part of a faction led by Andrew Jackson.

The map for this election is incomplete due to the lack of returns at the town or county level.

Kentucky used a district system for electing members to Congress.

In 1825, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ky.specialcongress3.1825) was held in which James Clarke was elected to replace Henry Clay, who had resigned from office after being appointed United States Secretary of State.

In 1826, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ky.uscongress5.1826) was held in which Robert L. MacHatton was elected to replace James Johnson, who had died.

In 1826, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ky.uscongress12.1826) was held in which John F. Henry was elected to replace Robert P. Henry, who had died.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
