---
meae-id: meae.staterepresentative.1800.nj.county
type: state-rep
level: state
state: New Jersey
geography: county
title: 'New Jersey General Assembly, 1800'
year: 1800
legend: fed-vs-rep
nnv:
- id: nj.generalassembly.bergen.1800
  name: NJ General Assembly 1800, Bergen County
- id: nj.generalassembly.cumberland.1800
  name: NJ General Assembly 1800, Cumberland County
- id: nj.generalassembly.essex.1800
  name: NJ General Assembly 1800, Essex County
- id: nj.generalassembly.gloucester.1800
  name: NJ General Assembly 1800, Gloucester County
- id: nj.generalassembly.hunterdon.1800
  name: NJ General Assembly 1800, Hunterdon County
- id: nj.generalassembly.middlesex.1800
  name: NJ General Assembly 1800, Middlesex County
- id: nj.generalassembly.monmouth.1800
  name: NJ General Assembly 1800, Monmouth County            
- id: nj.generalassembly.morris.1800
  name: NJ General Assembly 1800, Morris County
- id: nj.generalassembly.salem.1800
  name: NJ General Assembly 1800, Salem County
- id: nj.generalassembly.somerset.1800
  name: NJ General Assembly 1800, Somerset County
- id: nj.generalassembly.sussex.1800
  name: NJ General Assembly 1800, Sussex County        
related-maps:
- id: meae.staterepresentative.1801.nj.county
  name: NJ 1801 General Assembly
  type: next
- id: meae.congressional.congress07.nj.county
  name: NJ 7th Congress
  type: congressional
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.staterepresentative.1800.nj.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_staterep_map_data(state = "NJ", election_date = "1800-10-01") %>%
  map_counties(height = "700px")
```

</div>

In 1800, New Jersey elected thirty-nine assemblymen to the state’s General Assembly. At least twenty-three were Federalists, and at least nine were Democratic-Republicans.

New Jersey’s state legislature was comprised of an upper house called the Legislative Council and a lower house called the General Assembly. Each of the state's thirteen counties elected one councilor and three assemblymen to the legislature. Elections for both houses were held annually. 

In 1800, New Jersey allowed unmarried women (single and widowed) and free blacks (who met the property requirement) to vote. New Jersey was the only state to allow women to vote, and one of a few that allowed African Americans to vote. However, this unique makeup of the electorate only lasted a short time. An 1807 law did away with property restrictions, but also limited the franchise to white males. 

This era of New Jersey politics was marked by intense party competition between the Federalists and the Democratic-Republicans. In 1800, elections for New Jersey’s General Assembly and for New Jersey’s delegation to the [Seventh U.S. Congress](http://earlyamericanelections.org/maps/meae.congressional.congress07.nj.county.html) show the beginning of a shift in party control in New Jersey’s state and federal elections. During the 1790s, New Jersey almost exclusively elected Federalist candidates to state and federal office. However after 1800, New Jersey Republicans gained control of the state legislature, the governorship, and the congressional delegation.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results_state_rep() %>%
  results_to_table_state_rep() %>%
  cat()
```

</div>
