---
meae-id: meae.congressional.congress13.pa.county
type: congressional
level: state
state: Pennsylvania
geography: county
congressnum: 13
congressordinal: 13th
title: '13th Congress: Pennsylvania 1812'
year: 1812
legend: fed-vs-rep
nnv:
- id: pa.uscongress1.1812
  name: PA US Congress 1812 District 1
- id: pa.uscongress2.1812
  name: PA US Congress 1812 District 2
- id: pa.uscongress3.1812
  name: PA US Congress 1812 District 3
- id: pa.uscongress4.1812
  name: PA US Congress 1812 District 4
- id: pa.uscongress5.1812
  name: PA US Congress 1812 District 5
- id: pa.uscongress6.1812
  name: PA US Congress 1812 District 6
- id: pa.uscongress7.1812
  name: PA US Congress 1812 District 7
- id: pa.uscongress8.1812
  name: PA US Congress 1812 District 8
- id: pa.uscongress9.1812
  name: PA US Congress 1812 District 9
- id: pa.uscongress10.1812
  name: PA US Congress 1812 District 10
- id: pa.uscongress11.1812
  name: PA US Congress 1812 District 11
- id: pa.uscongress12.1812
  name: PA US Congress 1812 District 12
- id: pa.uscongress13.1812
  name: PA US Congress 1812 District 13
- id: pa.uscongress14.1812
  name: PA US Congress 1812 District 14
- id: pa.uscongress15.1812
  name: PA US Congress 1812 District 15
related-maps:
- id: meae.congressional.congress12.pa.county
  name: PA 12th Congress
  type: previous
- id: meae.congressional.congress14.pa.county
  name: PA 14th Congress
  type: next
#- id: meae.congressional.congress13.national.district
#  name: National 13th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress13.pa.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~federalist_vote, ~demrep_vote,
    "Philadelphia", 39.9526, -75.1652, 0.486, 0.514, 11223, 11875)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", cities = 0, congress = 13) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1<br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city)
```

</div>

Pennsylvania elected one Federalist and twenty-two Democratic-Republicans to the Thirteenth Congress.

The map for this election is incomplete due to the lack of returns in a few counties.

Pennsylvania used a district system for electing members to Congress. District 1 elected four representatives. Districts 2, 3, 5, 6, and 10 each elected two representatives. Pennsylvania was apportioned 5 more seats in the House of Representatives.

In 1813, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress3.specialelection.1813) was held in which Edward Crouch was elected to replace John Gloninger, who had resigned. 

In 1813, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress5.specialelection.1813) was held in which John Rhea was elected to replace Robert Whitehalll, who had died.

In 1813, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress7.specialelection.1813) was held in which Daniel Udree was elected to replace John M. Hyneman, who had resigned. 

In 1813, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress13.specialelection.1813) was held in which Isaac Griffin was elected to replace John Smiie, who had died. 

In 1813, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress15.specialelection.1813) was held in which Thomas Wilson was elected to replace Abner Lacock, who had resigned after being elected to the United States Senate.

In 1814, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress2.special.1814) was held in which Samuel Henderson was elected to replace Jonathan Roberts, who had resigned. 

In 1814, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.uscongress3.special.1814) was held in which Amos Slaymaker was elected to replace James Whitehill, who had resigned.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
