---
meae-id: meae.congressional.congress01.va.county
type: congressional
level: state
state: Virginia
geography: county
congressnum: 1
congressordinal: 1st
title: '1st Congress: Virginia 1789'
year: 1789
legend: fed-vs-anti
nnv:
- id: va.uscongress.1.1789
  name: VA US Congress 1789 District 1
- id: va.uscongress.2.1789
  name: VA US Congress 1789 District 2
- id: va.uscongress.3.1789
  name: VA US Congress 1789 District 3
- id: va.uscongress.4.1789
  name: VA US Congress 1789 District 4
- id: va.uscongress.5.1789
  name: VA US Congress 1789 District 5
- id: va.uscongress.6.1789
  name: VA US Congress 1789 District 6
- id: va.uscongress.7.1789
  name: VA US Congress 1789 District 7
- id: va.uscongress.8.1789
  name: VA US Congress 1789 District 8
- id: va.uscongress.9.1789
  name: VA US Congress 1789 District 9
- id: va.uscongress.10.1789
  name: VA US Congress 1789 District 10
related-maps:
- id: meae.congressional.congress02.va.county
  name: VA 2nd Congress
  type: next
# - id: meae.congressional.congress01.national.district
#   name: National 1st Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress01.va.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "405px")
```

</div>

Virginia’s first Congressional election utilized a district-based electoral system. Because the state was to seat ten representatives in Congress, the state was divided into ten districts, with each district electing a candidate from their own district. Because political parties had not been fully developed in Virginia at the time, all ten representatives elected were unaffiliated with a party. Three candidates, White from District 1, Brown from District 2, and Coles from District 3 stood unopposed. The other candidates listed did have opponents, but in many districts, insufficient returns make it impossible to report specific vote totals or percentages. In fact, out of all ten districts, only District 5 had full returns. Therefore, we do know that James Monroe lost to James Madison by 336 votes. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
