---
meae-id: meae.congressional.congress18.pa.county
type: congressional
level: state
state: Pennsylvania
geography: county
congressnum: 18
congressordinal: 18th
title: '18th Congress: Pennsylvania 1822'
year: 1822
legend: fed-vs-rep
nnv:
- id: pa.congress.1.1822
  name: PA US Congress 1822 District 1
- id: pa.congress.2.1822
  name: PA US Congress 1822 District 2
- id: pa.congress.3.1822
  name: PA US Congress 1822 District 3
- id: pa.congress.4.1822
  name: PA US Congress 1822 District 4
- id: pa.congress.5.1822
  name: PA US Congress 1822 District 5
- id: pa.congress.6.1822
  name: PA US Congress 1822 District 6
- id: pa.congress.7.1822
  name: PA US Congress 1822 District 7
- id: pa.congress.8.1822
  name: PA US Congress 1822 District 8
- id: pa.congress.9.1822
  name: PA US Congress 1822 District 9
- id: pa.congress.10.1822
  name: PA US Congress 1822 District 10
- id: pa.congress.11.1822
  name: PA US Congress 1822 District 11
- id: pa.congress.12.1822
  name: PA US Congress 1822 District 12
- id: pa.congress.13.1822
  name: PA US Congress 1822 District 13
- id: pa.congress.14.1822
  name: PA US Congress 1822 District 14
- id: pa.congress.15.1822
  name: PA US Congress 1822 District 15
- id: pa.congress.16.1822
  name: PA US Congress 1822 District 16
- id: pa.congress.17.1822
  name: PA US Congress 1822 District 17
- id: pa.congress.18.1822
  name: PA US Congress 1822 District 18
related-maps:
- id: meae.congressional.congress17.pa.county
  name: PA 17th Congress
  type: previous
- id: meae.congressional.congress19.pa.county
  name: PA 19th Congress
  type: next
#- id: meae.congressional.congress18.national.district
#  name: National 18th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress18.pa.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~federalist_vote, ~demrep_vote,
    "Philadelphia", 39.9526, -75.1652, 0.624, 0.376, 2857, 1723)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", cities = 0, congress = 17) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1, 2<br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city) 
```

</div>

Pennsylvania elected eight Federalists and eighteen Democratic-Republicans to the Eighteenth Congress. 

The map for this election is incomplete due to the lack of returns for some counties.

Pennsylvania was apportioned three more seats in the House of Representatives.

Pennsylvania used a district system for electing members to Congress. Districts 4 and 9 elected three representatives. Districts 7, 8, 11, and 16 each elected two representatives. 

In 1824, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress.8.special.1824) was held in which George Wolf was elected to replace Thomas J. Rogers, who had resigned from office.

In 1824, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress.13.special.1824) was held in which Alexander Thomson was elected to replace John Tod, who had resigned from office. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
