---
meae-id: meae.congressional.congress06.ri.county
type: congressional
level: state
state: Rhode Island
geography: county
congressnum: 6
congressordinal: 6th
title: '6th Congress: Rhode Island 1798'
year: 1798
legend: fed-vs-rep
nnv:
- id: ri.uscongress.1strep.1798
  name: RI US Congress 1798 Ticket 1
- id: ri.uscongress.2ndrep.1798
  name: RI US Congress 1798 Ticket 2
related-maps:
- id: meae.congressional.congress05.ri.county
  name: RI 5th Congress
  type: previous
- id: meae.congressional.congress07.ri.county
  name: RI 7th Congress
  type: next
# - id: meae.congressional.congress06.national.district
#   name: National 6th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress06.ri.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "300px", congress = 6)
```

</div>

Rhode Island elected two Federalists to the Sixth Congress.

Rhode Island used a statewide at-large method for electing members to Congress, though each of the two representatives was elected on separate tickets. This map shows returns for the contested election between John Brown and Thomas Tillinghast. Christopher Champlin won the other ticket virtually unopposed.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
