---
meae-id: meae.congressional.congress09.ny.county
type: congressional
level: state
state: New York
geography: county
congressnum: 9
congressordinal: 9th
title: '9th Congress: New York 1804'
year: 1804
legend: fed-vs-rep
nnv:
- id: ny.uscongress1.1804
  name: NY US Congress 1804 District 1
- id: ny.uscongress2and3.1804
  name: NY US Congress 1804 District 2
- id: ny.uscongress4.1804
  name: NY US Congress 1804 District 4
- id: ny.uscongress5.1804
  name: NY US Congress 1804 District 5
- id: ny.uscongress6.1804
  name: NY US Congress 1804 District 6
- id: ny.uscongress7.1804
  name: NY US Congress 1804 District 7
- id: ny.uscongress8.1804
  name: NY US Congress 1804 District 8
- id: ny.uscongress9.1804
  name: NY US Congress 1804 District 9
- id: ny.uscongress10.1804
  name: NY US Congress 1804 District 10
- id: ny.uscongress11.1804
  name: NY US Congress 1804 District 11
- id: ny.uscongress12.1804
  name: NY US Congress 1804 District 12
- id: ny.uscongress13.1804
  name: NY US Congress 1804 District 13
- id: ny.uscongress14.1804
  name: NY US Congress 1804 District 14
- id: ny.uscongress15.1804
  name: NY US Congress 1804 District 15
- id: ny.uscongress16.1804
  name: NY US Congress 1804 District 16
- id: ny.uscongress17.1804
  name: NY US Congress 1804 District 17
related-maps:
- id: meae.congressional.congress08.ny.county
  name: NY 8th Congress
  type: previous
- id: meae.congressional.congress10.ny.county
  name: NY 10th Congress
  type: next
- id: meae.congressional.congress09.national.county
  name: National 9th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress09.ny.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "725px", congress = 9)
```

</div>

New York elected two Federalists and fifteen Democratic-Republicans to the Ninth Congress.

New York used a district system for electing members to Congress. Each district elected one member of Congress, except Districts 2 and 3 (New York City and Brooklyn), which voted together as a single district and elected two members of Congress.

In 1805, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.uscongress2and3.special.1805) was held in which George Clinton, Jr. was elected to replace Samuel L. Mitchell, who had resigned from office after his appointment to the Senate.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
