---
meae-id: meae.congressional.congress19.nc.county
type: congressional
level: state
state: North Carolina
geography: county
congressnum: 19
congressordinal: 19th
title: '19th Congress: North Carolina 1825'
year: 1825
legend: dissrep
nnv:
- id: nc.uscongress1.1825
  name: NC US Congress 1825 District 1
- id: nc.uscongress2.1825
  name: NC US Congress 1825 District 2
- id: nc.uscongress3.1825
  name: NC US Congress 1825 District 3
- id: nc.uscongress4.1825
  name: NC US Congress 1825 District 4
- id: nc.uscongress5.1825
  name: NC US Congress 1825 District 5
- id: nc.uscongress6.1825
  name: NC US Congress 1825 District 6
- id: nc.uscongress7.1825
  name: NC US Congress 1825 District 7
- id: nc.uscongress8.1825
  name: NC US Congress 1825 District 8
- id: nc.uscongress9.1825
  name: NC US Congress 1825 District 9
- id: nc.uscongress10.1825
  name: NC US Congress 1825 District 10
- id: nc.uscongress11.1825
  name: NC US Congress 1825 District 11
- id: nc.uscongress12.1825
  name: NC US Congress 1825 District 12
- id: nc.uscongress13.1825
  name: NC US Congress 1825 District 13
related-maps:
- id: meae.congressional.congress18.nc.county
  name: NC 18th Congress
  type: previous
#- id: meae.congressional.congress19.national.district
#  name: National 19th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress19.nc.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", congress = 19)
```

</div>

North Carolina elected thirteen Democratic-Republicans to the Nineteenth Congress. All thirteen of those Democratic-Republicans were part of an identifiable faction within the party. Anti-Caucus and Caucus...

Mapping this election is not possible because of the lack of returns at the town or county level.

North Carolina used a district system for electing members to Congress. 

In 1826, a [special election](https://elections.lib.tufts.edu/catalog/tufts:nc.uscongress8.special.1826) was held in which Daniel L. Barringer was elected to replace Willie P. Mangum, who had resigned from office. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
