---
meae-id: meae.congressional.congress17.oh.county
type: congressional
level: state
state: Ohio
geography: county
congressnum: 17
congressordinal: 17th
title: '17th Congress: Ohio 1820'
year: 1820
legend: fed-vs-rep
nnv:
- id: oh.uscongress1.1820
  name: OH US Congress 1820 District 1
- id: oh.uscongress2.1820
  name: OH US Congress 1820 District 2
- id: oh.uscongress3.1820
  name: OH US Congress 1820 District 3
- id: oh.uscongress4.1820
  name: OH US Congress 1820 District 4
- id: oh.uscongress5.1820
  name: OH US Congress 1820 District 5
- id: oh.uscongress6.1820
  name: OH US Congress 1820 District 6
related-maps:
- id: meae.congressional.congress16.oh.county
  name: OH 16th Congress
  type: previous
- id: meae.congressional.congress18.oh.county
  name: OH 18th Congress
  type: next
#- id: meae.congressional.congress17.national.district
#  name: National 17th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress17.oh.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
    filter(id != "ohs_nca5",
           id != "ohs_nca6",
           id != "ohs_nca7",
           id != "ohs_nca8",
           id != "ohs_nca9") %>% 
  map_counties(height = "650px", congress = 17)
```

</div>

Ohio elected six Democratic-Republicans to the Seventeenth Congress. 

The map for this election is incomplete due to the lack of returns at the town or county level.

Ohio used a district system for electing members to Congress. 

In 1821, a [special election](https://elections.lib.tufts.edu/catalog/tufts:oh.uscongress4.1821) was held in which David Chambers was elected to replace John C. Wright, who had resigned before Congress began their session.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
