---
meae-id: meae.congressional.congress07.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 7
congressordinal: 7th
title: '7th Congress: Delaware 1800'
year: 1800
legend: fed-vs-rep
nnv:
- id: de.uscongress.1800
  name: DE US Congress 1800 At Large
related-maps:
- id: meae.congressional.congress06.de.county
  name: DE 6th Congress
  type: previous
- id: meae.congressional.congress08.de.county
  name: DE 8th Congress
  type: next
- id: meae.congressional.congress07.national.county
  name: National 7th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)
library(sf)

map_id <- "meae.congressional.congress07.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Delaware elected one Federalist to the Seventh Congress.

Delaware used a statewide at-large method for electing members to Congress. Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. The candidate with the most votes was then declared the winner.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
