---
meae-id: meae.staterepresentative.1806.pa.county
type: state-rep
level: state
state: Pennsylvania
geography: county
title: 'Pennsylvania House of Representatives, 1806'
year: 1806
legend: dissrep
nnv:
- id: pa.assembly.adams.1806
  name: PA House of Representatives 1806, Adams County
- id: pa.assembly.alleghenybeaverbutler.1806
  name: PA House of Representatives 1806, Allegheny, Beaver, and Butler Counties
- id: pa.assembly.armstrongindianajeffersonwestmoreland.1806
  name: PA House of Representatives 1806, Armstrong, Indiana, and Westmoreland Counties
- id: pa.assembly.bedford.1806
  name: PA House of Representatives 1806, Bedford County
- id: pa.assembly.berks.1806
  name: PA House of Representatives 1806, Berks County
- id: pa.assembly.bucks.1806
  name: PA House of Representatives 1806, Bucks County
- id: pa.assembly.centre.1806
  name: PA House of Representatives 1806, Centre County
- id: pa.assembly.chester.1806
  name: PA House of Representatives 1806, Chester County
- id: pa.assembly.crawforderiemercervenangowarren.1806
  name: PA House of Representatives 1806, Crawford, Erie, Mercer, and Venango Counties
- id: pa.assembly.cumberland.1806
  name: PA House of Representatives 1806, Cumberland County
- id: pa.assembly.dauphin.1806
  name: PA House of Representatives 1806, Dauphin County
- id: pa.assembly.delaware.1806
  name: PA House of Representatives 1806, Delaware County
- id: pa.assembly.fayette.1806
  name: PA House of Representatives 1806, Fayette County
- id: pa.assembly.franklin.1806
  name: PA House of Representatives 1806, Franklin County 
- id: pa.assembly.huntingdon.1806
  name: PA House of Representatives 1806, Huntingdon County
- id: pa.assembly.lancaster.1806
  name: PA House of Representatives 1806, Lancaster County
- id: pa.assembly.luzerne.1806
  name: PA House of Representatives 1806, Luzerne County
- id: pa.assembly.lycoming.1806
  name: PA House of Representatives 1806, Lycoming County
- id: pa.assembly.mifflin.1806
  name: PA House of Representatives 1806, Mifflin County
- id: pa.assembly.montgomery.1806
  name: PA House of Representatives 1806, Montgomery County
- id: pa.assembly.northamptonwayne.1806
  name: PA House of Representatives 1806, Northamption and Wayne Counties
- id: pa.assembly.northumberland.1806
  name: PA House of Representatives 1806, Northumberland County
- id: pa.assembly.philadelphia.1806
  name: PA House of Representatives 1806, Philadelphia County
- id: pa.assembly.philadelphiacity.1806
  name: PA House of Representatives 1806, City of Philadelphia
- id: pa.assembly.somerset.1806
  name: PA House of Representatives 1806, Somerset County
- id: pa.assembly.washington.1806
  name: PA House of Representatives 1806, Washington County
- id: pa.assembly.york.1806
  name: PA House of Representatives 1806, York County
related-maps:
- id: meae.staterepresentative.1805.pa.county
  name: PA 1805 House of Representatives
  type: previous
- id: meae.congressional.congress10.pa.county
  name: PA 10th Congress
  type: congressional  
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.staterepresentative.1806.pa.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~repfac_percentage, ~federalist_vote, ~demrep_vote, ~repfac_vote,
    "Philadelphia", 39.9526, -75.1652, 0.522, 0.468, 0, 10023, 8998, 0)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_staterep_map_data(state = "PA", election_date = "1806-10-01") %>%
  map_counties(height = "500px", cities = 0) %>%
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city) 
```

</div>

In 1806, Pennsylvania elected at least fourteen Federalists, forty Democratic-Republicans, and twenty-five Republicans who were part of a faction within the party to Pennsylvania’s House of Representatives. In this election, the Republican faction was a coalition of Federalists and moderate Democratic-Republicans (Constitutionalists). This group of candidates was often referred to as Quids. Democratic-Republicans and Quids clashed over impeachments, the governor's appointment powers, and reforms of the constitution and the court system.

While Pennsylvania’s state legislature started out as a unicameral assembly, in 1791, the Pennsylvania General Assembly became a bicameral legislature, with a House of Representatives whose members were elected annually in October and a state Senate whose members were elected to four-year terms.

Pennsylvania used a district system for electing members to Pennsylvania House of Representatives. Districts elected various numbers of Representatives (based on population), and were normally made up of a single county. However, during the early 1800s, numerous new counties were organized, especially in the sparsely settled western and northern part of the state. These new counties, for periods of time, voted with their parent county, and returns were rarely reported for them individually. This resulted in several multiple-county districts. 

In this election the following counties voted together in a single district: Allegheny, Beaver, and Butler Counties. Armstrong, Indiana, Jefferson and Westmoreland Counties voted together. Crawford, Erie, Mercer, Venango, and Warren Counties voted together. The votes cast in Warren County are included in the Venango County totals. Centre and Clearfield Counties voted together. Lycoming, Tioga, and Potter Counties voted together. Northampton and Wayne Counties voted together. The votes cast in Cambria County are included in the Somerset County totals.

In October 1806, elections where held simultaneously for Pennsylvania’s House of Representatives and for Pennsylvania’s delegation to the [Tenth U.S. Congress](https://earlyamericanelections.org/maps/meae.congressional.congress10.pa.county.html). Federalist, Democratic-Republican, and Quid candidates were elected in both contests.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results_state_rep() %>%
  results_to_table_state_rep() %>%
  cat()
```

</div>
