---
title: '5th Congress: Tennessee 1797'
congressnum: 5
congressordinal: 5th
output:
  html_document:
    theme: default
  md_document:
    variant: markdown
layout: maps-show
legend: fed-vs-rep
level: state
meae-id: meae.congressional.congress05.tn.county
nnv:
- id: tn.ushouserepresentatives.1797
  name: TN US Congress 1797 At Large
geography: county
related-maps:
- id: meae.congressional.congress04.tn.county
  name: TN 4th Congress
  type: previous
- id: meae.congressional.congress06.tn.county
  name: TN 6th Congress
  type: next
# - id: meae.congressional.congress05.national.district
#   name: National 5th Congress
#   type: national
state: Tennessee
always_allow_html: yes
type: congressional
year: 1797
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress05.tn.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "300px") %>% 
  setView(lng = -84.85, lat = 36.348, zoom = 8)
```

</div>

Tennessee elected one Democratic-Republican to the Fifth Congress.

Mapping this election is incomplete because of the lack of returns at the town or county level in many areas. 

Tennessee re-elected Andrew Jackson to serve in the Fifth Congress. In September 1797, Jackson resigned from the House of Representatives in order to accept a seat in the US Senate. Tennessee held a special election which elected William Charles Cole Claiborne, which is the election presented here. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
