---
meae-id: meae.congressional.congress01.nh.county
type: congressional
level: state
state: New Hampshire
geography: county
congressnum: 1
congressordinal: 1st
title: '1st Congress: New Hampshire 1789'
year: 1789
legend: fed-vs-anti
nnv:
- id: nh.uscongress.1789
  name: NH US Congress 1789 At Large
related-maps:
- id: meae.congressional.congress02.nh.county
  name: NH 2nd Congress
  type: next
- id: meae.congressional.congress01.national.county
  name: National 1st Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress01.nh.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>% 
  map_counties(height = "700px", congress = 1)
```

</div>

New Hampshire elected three Federalists to the First Congress. 

Mapping this election is not possible because there are insufficient returns at the town and county levels.

New Hampshire used a state-wide at-large system to elect members of Congress. These candidate were elected on the second ballot. Benjamin West declined his election and was replaced by Abiel Foster in a [special election](https://elections.lib.tufts.edu/catalog/tufts:nh.uscongress.special.1789).

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table(keep_percentage = 0.01) %>%
  cat()
```

</div>
