---
meae-id: meae.congressional.congress04.md.county
type: congressional
level: state
state: Maryland
geography: county
congressnum: 4
congressordinal: 4th
title: '4th Congress: Maryland 1794'
year: 1794
legend: fed-vs-rep
nnv:
- id: md.uscongress1.1794
  name: MD US Congress 1794 District 1
- id: md.uscongress2.1794
  name: MD US Congress 1794 District 2
- id: md.uscongress3.1794
  name: MD US Congress 1794 District 3
- id: md.uscongress4.1794
  name: MD US Congress 1794 District 4
- id: md.uscongress5.1794
  name: MD US Congress 1794 District 5
- id: md.uscongress6.1794
  name: MD US Congress 1794 District 6
- id: md.uscongress7.1794
  name: MD US Congress 1794 District 7
- id: md.uscongress8.1794
  name: MD US Congress 1794 District 8
related-maps:
- id: meae.congressional.congress03.md.county
  name: MD 3rd Congress
  type: previous
- id: meae.congressional.congress05.md.county
  name: MD 5th Congress
  type: next
# - id: meae.congressional.congress04.national.district
#   name: National 4th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress04.md.county"
cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~federalist_vote, ~demrep_vote,
  "Baltimore", 39.30021, -76.61052, 0.0, 1.0, 0, 160
)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "425px", cities = FALSE) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                   fillColor = mappingelections:::poli_chrome(cities),
                   opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                   popup = ~paste0("<b>City of ", city, "</b><br/>",
                                   "Congressional District: 5<br/>",
                                   "Federalists: ", federalist_percentage * 100, "% (", 
                                   prettyNum(federalist_vote, big.mark = ","), 
                                   " votes)<br/>",
                                   "Democratic-Republicans: ", demrep_percentage * 100,
                                   "% (", 
                                   prettyNum(demrep_vote, big.mark = ","),
                                   " votes)"),
                   label = ~city) 
```

</div>

Maryland elected five Federalists and three Democratic-Republicans to the Fourth Congress.

Maryland used a district system for electing members to Congress.

In October 1796 a [special election](https://elections.lib.tufts.edu/catalog/tufts:md.uscongress2.special.1796) was held in which Richard Sprigg was elected to replace Gabriel Duvall, who resigned from office.
Another [special election](https://elections.lib.tufts.edu/catalog/tufts:md.uscongress3.special.1796) was held in which William Craik was elected to replace Jeremiah Crabb, who resigned from office.
 
<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
