---
meae-id: meae.congressional.congress10.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 10
congressordinal: 10th
title: '10th Congress: Delaware 1806'
year: 1806
legend: fed-vs-rep
nnv:
- id: de.uscongress.1806
  name: DE US Congress 1806 At Large
related-maps:
- id: meae.congressional.congress09.de.county
  name: DE 9th Congress
  type: previous
- id: meae.congressional.congress11.de.county
  name: DE 11th Congress
  type: next
# - id: meae.congressional.congress10.national.district
#   name: National 10th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress10.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Delaware elected one Federalist to the Tenth Congress.

Delaware used a statewide at-large method for electing members to Congress. Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. The at-large winner was then declared the winner.  This map depicts the initial winner.

In 1807, a [special election](https://elections.lib.tufts.edu/catalog/tufts:de.uscongress.1807) was held in which Federalist Nicholas Van Dyke was elected to replace James M. Broom, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
