---
meae-id: meae.congressional.congress16.ny.county
type: congressional
level: state
state: New York
geography: county
congressnum: 16
congressordinal: 16th
title: '16th Congress: New York 1818'
year: 1818
legend: dissrep
nnv:
- id: ny.uscongress1.1818
  name: NY US Congress 1818 District 1
- id: ny.uscongress2.1818
  name: NY US Congress 1818 District 2
- id: ny.uscongress3.1818
  name: NY US Congress 1818 District 3
- id: ny.uscongress4.1818
  name: NY US Congress 1818 District 4
- id: ny.uscongress5.1818
  name: NY US Congress 1818 District 5
- id: ny.uscongress6.1818
  name: NY US Congress 1818 District 6
- id: ny.uscongress7.1818
  name: NY US Congress 1818 District 7
- id: ny.uscongress8.1818
  name: NY US Congress 1818 District 8
- id: ny.uscongress9.1818
  name: NY US Congress 1818 District 9
- id: ny.uscongress10.1818
  name: NY US Congress 1818 District 10
- id: ny.uscongress11.1818
  name: NY US Congress 1818 District 11
- id: ny.uscongress12.1818
  name: NY US Congress 1818 District 12
- id: ny.uscongress13.1818
  name: NY US Congress 1818 District 13
- id: ny.uscongress14.1818
  name: NY US Congress 1818 District 14
- id: ny.uscongress15.1818
  name: NY US Congress 1818 District 15
- id: ny.uscongress16.1818
  name: NY US Congress 1818 District 16
- id: ny.uscongress17.1818
  name: NY US Congress 1818 District 17
- id: ny.uscongress18.1818
  name: NY US Congress 1818 District 18
- id: ny.uscongress19.1818
  name: NY US Congress 1818 District 19
- id: ny.uscongress20.1818
  name: NY US Congress 1818 District 20
- id: ny.uscongress21.1818
  name: NY US Congress 1818 District 21
related-maps:
- id: meae.congressional.congress15.ny.county
  name: NY 15th Congress
  type: previous
- id: meae.congressional.congress17.ny.county
  name: NY 17th Congress
  type: next
- id: meae.congressional.congress16.national.county
  name: National 16th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress16.ny.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "725px", congress = 16)
```

</div>

New York elected two Federalists and twenty-five Democratic-Republicans to the Sixteenth Congress. Six of the Republicans elected were members of an identifiable faction within the party. In New York, some candidates ran as Clintonians who supported internal improvements and soft money. 

New York used a district system for electing members to Congress. Each district elected one member of Congress, except Districts 1, 2, 12, 15, 20, and 21, which each elected two members.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
