---
meae-id: meae.congressional.congress01.nc.county
type: congressional
level: state
state: North Carolina
geography: county
congressnum: 1
congressordinal: 1st
title: '1st Congress: North Carolina 1790'
year: 1790
legend: fed-vs-anti
nnv:
- id: nc.uscongress1.1790
  name: NC US Congress 1790 District 1
- id: nc.uscongress2.1790
  name: NC US Congress 1790 District 2
- id: nc.uscongress3.1790
  name: NC US Congress 1790 District 3
- id: nc.uscongress4.1790
  name: NC US Congress 1790 District 4
- id: nc.uscongress5.1790
  name: NC US Congress 1790 District 5
related-maps:
- id: meae.congressional.congress02.nc.county
  name: NC 2nd Congress
  type: next
- id: meae.congressional.congress01.national.district
  name: National 1st Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress01.nc.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>% 
  map_counties(height = "400px") %>% 
  setView(-80.10, 35.22, 8)
```

</div>

In the first district, the Anti-Federalist John Baptist Ashe won with only 49 percent of the vote, since the majority of the vote was divided between two candidates without party affiliations, Nathaniel Macon and Stephen Moore.

The third and fourth districts elected Anti-Federalists. In the third district, Anti-Federalist Timothy Bloodworth was elected; however, returns are available only for Onslow County. In the fourth district, the Anti-Federalist John Steele was elected. County level returns within that district are available only for Stokes and Surry Counties, where the majority of the vote when to Steele’s opponent, the Federalist Joseph MacDowell. The remaining counties are displayed as Anti-Federalist, though this must be interpreted cautiously since some of those counties may have voted for the Federalists. ([See NNV returns for North Carolina’s fourth district](http://elections.lib.tufts.edu/catalog/tufts:nc.uscongress4.1790).)

In the fifth district, Federalist John Sevier was elected without opposition. This district became a federal territory before the Second Congress.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
