---
meae-id: meae.congressional.congress12.ny.county
type: congressional
level: state
state: New York
geography: county
congressnum: 12
congressordinal: 12th
title: '12th Congress: New York 1810'
year: 1810
legend: fed-vs-rep
nnv:
- id: ny.uscongress1.1810
  name: NY US Congress 1810 District 1
- id: ny.uscongress2.1810
  name: NY US Congress 1810 District 2
- id: ny.uscongress3.1810
  name: NY US Congress 1810 District 3
- id: ny.uscongress4.1810
  name: NY US Congress 1810 District 4
- id: ny.uscongress5.1810
  name: NY US Congress 1810 District 5
- id: ny.uscongress6.1810
  name: NY US Congress 1810 District 6
- id: ny.uscongress7.1810
  name: NY US Congress 1810 District 7
- id: ny.uscongress8.1810
  name: NY US Congress 1810 District 8
- id: ny.uscongress9.1810
  name: NY US Congress 1810 District 9
- id: ny.uscongress10.1810
  name: NY US Congress 1810 District 10
- id: ny.uscongress11.1810
  name: NY US Congress 1810 District 11
- id: ny.uscongress12.1810
  name: NY US Congress 1810 District 12
- id: ny.uscongress13.1810
  name: NY US Congress 1810 District 13
- id: ny.uscongress14.1810
  name: NY US Congress 1810 District 14
- id: ny.uscongress15.1810
  name: NY US Congress 1810 District 15
related-maps:
- id: meae.congressional.congress11.ny.county
  name: NY 11th Congress
  type: previous
- id: meae.congressional.congress13.ny.county
  name: NY 13th Congress
  type: next
- id: meae.congressional.congress12.national.county
  name: National 12th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress12.ny.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "725px", congress = 12)
```

</div>

New York elected five Federalists and twelve Democratic-Republicans to the Twelfth Congress.

New York used a district system for electing members to Congress. Each district elected one member of Congress except Districts 2 and 6, which each elected two members.

In 1812, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ny.uscongress6.special.1812) was held in which Thomas P. Grosvenor was elected to replace Robert LeRoy Livingston, who had resigned. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
