---
meae-id: meae.congressional.congress01.nj.county
type: congressional
level: state
state: New Jersey
geography: county
congressnum: 1
congressordinal: 1st
title: '1st Congress: New Jersey 1789'
year: 1789
legend: fed-vs-anti
nnv:
- id: nj.uscongress.1789
  name: NJ US Congress 1789 At Large
related-maps:
- id: meae.congressional.congress02.nj.county
  name: NJ 2nd Congress
  type: next
# - id: meae.congressional.congress01.national.district
#   name: National 1st Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress01.nj.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "700px")
```

</div>

The results from Cumberland County were included in the reports from Cape May County.

In an at-large election, New Jersey voters chose two unaffiliated and two Federalist candidates. A local newspaper, *The New-Jersey Journal, and Political Intelligencer*, urged voters to make a "prudent choice” so as to "gain a representation that not only knows, but feels, the wants and wishes of their constituents.” Over forty such men were named by New Jersey voters. Unaffiliated candidates James Schureman and Lambert Cadwallader received the most votes, while Federalist candidates Elias Boudinot and Thomas Sinnickson received enough votes to be elected. In the southern part of the state, votes were split more evenly between the Federalist and unaffiliated candidates. In the northern part of the state (with the exception of Bergen County), voters overwhelming chose unaffiliated candidates. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table(keep_percentage = 0.01) %>%
  cat()
```

</div>
