---
meae-id: meae.congressional.congress01.ga.county
type: congressional
level: state
state: Georgia
geography: county
congressnum: 1
congressordinal: 1st
title: '1st Congress: Georgia 1789'
year: 1789
legend: fed-vs-anti
nnv:
- id: ga.uscongress.lowerdistrict.1789
  name: GA US Congress 1789 District 1
- id: ga.uscongress.middledistrict.1789
  name: GA US Congress 1789 District 2
- id: ga.uscongress.upperdistrict.1789
  name: GA US Congress 1789 District 3
related-maps:
- id: meae.congressional.congress02.ga.county
  name: GA 2nd Congress
  type: next
- id: meae.congressional.congress01.national.district
  name: National 1st Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress01.ga.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px") %>% 
  setView(lng = -81.492, lat = 32.348, zoom = 7)
```

</div>

Georgia’s voters elected three unaffiliated representatives, one from each of the state’s three districts. For the First Congress, Georgia election law called for an at-large election in which each voter selected three candidates, one residing in each district. The candidate from each district that had the most votes statewide, won the election. 

The returns shown here only give the number of votes a candidate received in his home district, even though the election was based on the number of votes a candidate received overall. For example, James Jackson, who was elected to represent the Lower or Eastern (later First) District received 604 votes in his home district, but also received votes from at least one other district.

In addition to Jackson, Abraham Baldwin was elected to represent the Middle or Center (later Second) District, while George Matthews was overwhelmingly elected to represent the Upper or Western (later Third) District. Candidate Henry Osborne, while not elected, was the only candidate to receive more than eight votes in all three districts. None of the candidates in this election were affiliated with a particular political party.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
