---
meae-id: meae.congressional.congress16.ga.county
type: congressional
level: state
state: Georgia
geography: county
congressnum: 16
congressordinal: 16th
title: '16th Congress: Georgia 1818'
year: 1818
legend: fed-vs-rep
nnv:
- id: ga.uscongress.1818
  name: GA US Congress 1818 At Large
related-maps:
- id: meae.congressional.congress15.ga.county
  name: GA 15th Congress
  type: previous
- id: meae.congressional.congress17.ga.county
  name: GA 17th Congress
  type: next
- id: meae.congressional.congress16.national.county
  name: National 16th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress16.ga.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  filter(id != "gas_nca") %>% 
  map_counties(height = "525px")
```

</div>

Georgia elected six Democratic-Republicans to the Sixteenth Congress.

The map for this election is incomplete due to the lack of returns in several counties. 

Georgia used a statewide at-large system for electing members to Congress.

In a January 1819 [special election](https://elections.lib.tufts.edu/catalog/tufts:ga.uscongress.special2.1819), Robert R. Reid was elected to serve for the 16th Congress in place of John Forsyth, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
