---
meae-id: meae.congressional.congress11.oh.county
type: congressional
level: state
state: Ohio
geography: county
congressnum: 11
congressordinal: 11th
title: '11th Congress: Ohio 1808'
year: 1808
legend: dissrep
nnv:
- id: oh.ushouseofrepresentatives.1808
  name: OH US Congress 1808 At Large
related-maps:
- id: meae.congressional.congress10.oh.county
  name: OH 10th Congress
  type: previous
- id: meae.congressional.congress12.oh.county
  name: OH 12th Congress
  type: next
#- id: meae.congressional.congress11.national.district
#  name: National 11th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress11.oh.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  filter(id != "ohs_nca2") %>% 
  map_counties(height = "650px", congress = 11)
```

</div>

Ohio elected a Republican who was part of a faction within the party to the Eleventh Congress. The Republican faction in this election was the Tertium Quids (or just Quids), a coalition of Federalists and moderate Democratic-Republicans.

Mapping this election is incomplete because of the lack of local returns in many areas.

Ohio used a statewide at-large method for electing a member to Congress.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
