---
meae-id: meae.congressional.congress10.ma.county
type: congressional
level: state
state: Massachusetts
geography: county
congressnum: 10
congressordinal: 10th
title: '10th Congress: Massachusetts 1806'
year: 1806
legend: fed-vs-rep
nnv:
- id: ma.uscongress.suffolk.1806
  name: MA US Congress 1806 District 1
- id: ma.uscongress.essexsouth.1806
  name: MA US Congress 1806 District 2
- id: ma.uscongress.essexnorth.1806
  name: MA US Congress 1806 District 3
- id: ma.uscongress.middlesex.1806
  name: MA US Congress 1806 District 4
- id: ma.uscongress.hampshirenorth.1806
  name: MA US Congress 1806 District 6
- id: ma.uscongress.hampshiresouth.1806
  name: MA US Congress 1806 District 6
- id: ma.uscongress.plymouth.1806
  name: MA US Congress 1806 District 7
- id: ma.uscongress.barnstable.1806
  name: MA US Congress 1806 District 8
- id: ma.uscongress.bristol.1806
  name: MA US Congress 1806 District 9
- id: ma.uscongress.worcestersouth.1806
  name: MA US Congress 1806 District 10
- id: ma.uscongress.worcesternorth.1806
  name: MA US Congress 1806 District 11
- id: ma.uscongress.berkshire.1806
  name: MA US Congress 1806 District 12
- id: ma.uscongress.norfolk.1806
  name: MA US Congress 1806 District 13
- id: ma.uscongress.york.1806
  name: MA US Congress 1806 District 14
- id: ma.uscongress.cumberland.1806
  name: MA US Congress 1806 District 15
- id: ma.uscongress.lincoln.1806
  name: MA US Congress 1806 District 16
- id: ma.uscongress.kennebec.1806
  name: MA US Congress 1806 District 17
related-maps:
- id: meae.congressional.congress09.ma.county
  name: MA 9th Congress
  type: previous
- id: meae.congressional.congress11.ma.county
  name: MA 11th Congress
  type: next
# - id: meae.congressional.congress10.national.district
#   name: National 10th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress10.ma.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties() %>% 
  fitBounds(-73.508, 41.186, -69.861, 43.75)
```

</div>

Massachusetts elected six Federalists and eleven Democratic-Republicans to the Tenth Congress.

Massachusetts used the district system for electing members to Congress.

In 1807, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.berkshire.special.1807) was held in which Ezekiel Bacon was elected to replace Barnabas Bidwell, who had resigned from office.

In 1808, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.essexsouth.special.1808) was held in which Joseph Story was elected to replace Jacob Crowninshield, who died while in office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
