---
meae-id: meae.congressional.congress15.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 15
congressordinal: 15th
title: '15th Congress: Delaware 1816'
year: 1816
legend: fed-vs-rep
nnv:
- id: de.uscongress.1816
  name: DE US Congress 1816 At Large
related-maps:
- id: meae.congressional.congress14.de.county
  name: DE 14th Congress
  type: previous
- id: meae.congressional.congress16.de.county
  name: DE 16th Congress
  type: next
#- id: meae.congressional.congress15.national.district
#  name: National 15th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress15.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Delaware elected one Federalist and one Democratic-Republican to the Fifteenth Congress.

Delaware used a statewide at-large system for electing members to Congress. Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. Two at-large winners were elected.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
