---
meae-id: meae.congressional.congress01.sc.county
type: congressional
level: state
state: South Carolina
geography: county
congressnum: 1
congressordinal: 1st
title: '1st Congress: South Carolina 1788'
year: 1788
legend: fed-vs-anti
nnv:
- id: sc.uscongress.district1.1788
  name: SC US Congress 1788 District 1
- id: sc.uscongress.district2.1788
  name: SC US Congress 1788 District 2
- id: sc.uscongress.district3.1788
  name: SC US Congress 1788 District 3
- id: sc.uscongress.district4.1788
  name: SC US Congress 1788 District 4
- id: sc.uscongress.district5.1788
  name: SC US Congress 1788 District 5
related-maps:
- ''
- id: meae.congressional.congress02.sc.county
  name: SC 2nd Congress
  type: next
- id: meae.congressional.congress01.national.district
  name: National 1st Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress01.sc.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~antifederalist_percentage, ~federalist_vote, ~antifederalist_vote, ~other_percentage, ~other_vote,
  "Charleston", 32.7765, -79.9311, NA, NA, NA, NA, 1.0, 664)

```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(cities = FALSE,height = "600px") %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
               fillColor = mappingelections:::poli_chrome(cities),
               opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
               popup = ~paste0("<b>City of ", city, "</b><br/>",
                               "Congressional District: 1<br/>",
                               "Other parties: ", other_percentage * 100, "% (", 
                               prettyNum(other_vote, big.mark = ","), 
                               " votes)"),
               label = ~city) 
```

</div>
South Carolina voters elected five unaffiliated representatives to the First Congress. These representatives came from districts which included the state capital of Charleston and the surrounding lowcountry; many in the state's backcountry were opposed to ratifying the federal Constitution.

In the first district, also known as the Charleston District, William Smith was elected, having captured most of the votes from the capital city. While specific local returns are not available for the second and third districts, Aedanus Burke and Daniel Huger were elected to represent their respective districts. In the fourth and fifth districts, Thomas Sumter and Thomas Tudor Tucker stood unopposed.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
