---
meae-id: meae.congressional.congress07.sc.county
type: congressional
level: state
state: South Carolina
geography: county
congressnum: 7
congressordinal: 7th
title: '7th Congress: South Carolina 1800'
year: 1800
legend: fed-vs-rep
nnv:
- id: sc.uscongress.charleston.1800
  name: SC US Congress 1800 District 1
- id: sc.uscongress.beaufort.1800
  name: SC US Congress 1800 District 2
- id: sc.uscongress.georgetown.1800
  name: SC US Congress 1800 District 3
- id: sc.uscongress.camden.1800
  name: SC US Congress 1800 District 4
- id: sc.uscongress.ninety-six.1800
  name: SC US Congress 1800 District 5
- id: sc.uscongress.washington.1800
  name: SC US Congress 1800 District 6
related-maps:
- id: meae.congressional.congress06.sc.county
  name: SC 6th Congress
  type: previous
- id: meae.congressional.congress08.sc.county
  name: SC 8th Congress
  type: next
# - id: meae.congressional.congress07.national.district
#   name: National 7th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)
library(sf)

map_id <- "meae.congressional.congress07.sc.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  arrange(!is.na(federalist_percentage), !is.na(demrep_percentage)) %>%
  map_counties(height = "600px")
```

</div>

South Carolina elected four Federalists and two Democratic-Republicans to the Seventh Congress.

Mapping this election is incomplete because of the lack of local returns in many areas.

South Carolina used the district system for electing members to Congress.

In 1802, a [special election](https://elections.lib.tufts.edu/catalog/tufts:sc.uscongress.camden.special.1802) was held in which Richard Winn was elected to replace Democratic-Republican Thomas Sumter. Richard Winn ran as a Federalist against Thomas Sumter in 1800 but ran as a Democratic-Republican for his successful reelection in 1803.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
