---
meae-id: meae.congressional.congress18.nc.county
type: congressional
level: state
state: North Carolina
geography: county
congressnum: 18
congressordinal: 18th
title: '18th Congress: North Carolina 1823'
year: 1823
legend: congress-18-19
nnv:
- id: nc.uscongress1.1823
  name: NC US Congress 1823 District 1
- id: nc.uscongress2.1823
  name: NC US Congress 1823 District 2
- id: nc.uscongress3.1823
  name: NC US Congress 1823 District 3
- id: nc.uscongress4.1823
  name: NC US Congress 1823 District 4
- id: nc.uscongress5.1823
  name: NC US Congress 1823 District 5
- id: nc.uscongress6.1823
  name: NC US Congress 1823 District 6
- id: nc.uscongress7.1823
  name: NC US Congress 1823 District 7
- id: nc.uscongress8.1823
  name: NC US Congress 1823 District 8
- id: nc.uscongress9.1823
  name: NC US Congress 1823 District 9
- id: nc.uscongress10.1823
  name: NC US Congress 1823 District 10
- id: nc.uscongress11.1823
  name: NC US Congress 1823 District 11
- id: nc.uscongress12.1823
  name: NC US Congress 1823 District 12
- id: nc.uscongress13.1823
  name: NC US Congress 1823 District 13
related-maps:
- id: meae.congressional.congress17.nc.county
  name: NC 17th Congress
  type: previous
- id: meae.congressional.congress19.nc.county
  name: NC 19th Congress
  type: next
- id: meae.congressional.congress18.national.county
  name: National 18th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress18.nc.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", congress = 18)
```

</div>

North Carolina elected thirteen Democratic-Republicans to the Eighteenth Congress. Two of those Democratic-Republicans were part of a faction led by Andrew Jackson, one of the Democratic-Republicans was part of a faction led by John Quincy Adams and Henry Clay, and nine of the Democratic-Republicans were part of a faction led by William Crawford.

The map for this election is incomplete due to the lack of returns in many counties.

North Carolina used a district system for electing members to Congress. 

In 1825, a [special election](https://elections.lib.tufts.edu/catalog/tufts:nc.uscongress2.specialelection.1825) was held in which George Outlaw was elected to replace Hutchins G. Burton, who had resigned after being elected Governor. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
