---
meae-id: meae.congressional.congress16.ky.county
type: congressional
level: state
state: Kentucky
geography: county
congressnum: 16
congressordinal: 16th
title: '16th Congress: Kentucky 1818'
year: 1818
legend: fed-vs-rep
nnv:
- id: ky.uscongress1.1818
  name: KY US Congress 1818 District 1
- id: ky.uscongress2.1818
  name: KY US Congress 1818 District 2
- id: ky.uscongress3.1818
  name: KY US Congress 1818 District 3
- id: ky.uscongress4.1818
  name: KY US Congress 1818 District 4
- id: ky.uscongress5.1818
  name: KY US Congress 1818 District 5
- id: ky.uscongress6.1818
  name: KY US Congress 1818 District 6
- id: ky.uscongress7.1818
  name: KY US Congress 1818 District 7
- id: ky.uscongress8.1818
  name: KY US Congress 1818 District 8
- id: ky.uscongress9.1818
  name: KY US Congress 1818 District 9
- id: ky.uscongress10.1818
  name: KY US Congress 1818 District 10
related-maps:
- id: meae.congressional.congress15.ky.county
  name: KY 15th Congress
  type: previous
- id: meae.congressional.congress17.ky.county
  name: KY 17th Congress
  type: next
#- id: meae.congressional.congress16.national.district
#  name: National 16th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress16.ky.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Kentucky elected ten Democratic-Republicans to the Sixteenth Congress.

Mapping this election is not possible because of the lack of returns at the town or county level.

Kentucky used a district system for electing members to Congress. 

In 1820, a special election was held in which Francis Johnson was elected to replace David Walker, who had died.

In 1820, a special election was held in which Thomas Montgomery was elected to replace Tunstall Quarles, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
