---
title: '5th Congress: South Carolina 1796'
congressnum: 5
congressordinal: 5th
output:
  html_document:
    theme: default
  md_document:
    variant: markdown
layout: maps-show
legend: fed-vs-rep
level: state
meae-id: meae.congressional.congress05.sc.county
nnv:
- id: sc.uscongress.charleston.1796
  name: SC US Congress 1796 District 1
- id: sc.uscongress.beaufort.1796
  name: SC US Congress 1796 District 2
- id: sc.uscongress.georgetown.1796
  name: SC US Congress 1796 District 3
- id: sc.uscongress.camden.1796
  name: SC US Congress 1796 District 4
- id: sc.uscongress.ninety-six.1796
  name: SC US Congress 1796 District 5
- id: sc.uscongress.washington.1796
  name: SC US Congress 1796 District 6
geography: county
related-maps:
- id: meae.congressional.congress04.sc.county
  name: SC 4th Congress
  type: previous
- id: meae.congressional.congress06.sc.county
  name: SC 6th Congress
  type: next
# - id: meae.congressional.congress05.national.district
#   name: National 5th Congress
#   type: national
state: South Carolina
always_allow_html: yes
type: congressional
year: 1796
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)
library(sf)

map_id <- "meae.congressional.congress05.sc.county"
cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~federalist_vote, ~demrep_vote,
  "Charleston", 32.7765, -79.9311, 0.904, 0.096, 499, 53)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  filter(id != "scs_nca5") %>% 
  arrange(!is.na(federalist_percentage), !is.na(demrep_percentage)) %>%
  map_counties(cities = FALSE,height = "600px") %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
               fillColor = mappingelections:::poli_chrome(cities),
               opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1<br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city) 
```

</div>

South Carolina elected three Federalists and three Democratic-Republicans to the Fifth Congress.

Mapping this election is incomplete because of the lack of local returns in many areas. 

South Carolina used the district system for electing members to Congress. 

In September 1797, South Carolina held a [special election](https://elections.lib.tufts.edu/catalog/tufts:sc.uscongress.specialelection.1797) in which Thomas Pickney was elected to replace William L. Smith, who resigned when he was appointed minister to Portugal.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
