---
meae-id: meae.congressional.congress19.ms.county
type: congressional
level: state
state: Mississippi
geography: county
congressnum: 19
congressordinal: 19th
title: '19th Congress: Mississippi 1824'
year: 1824
legend: congress-18-19
nnv:
- id: ms.uscongress.1824
  name: MS US Congress 1824 At Large
related-maps:
- id: meae.congressional.congress18.ms.county
  name: MS 18th Congress
  type: previous
- id: meae.congressional.congress19.national.county
  name: National 19th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress19.ms.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data(election_date="1824-01-22") %>%
  filter(id != "mss_nca1") %>% 
  map_counties()
```

</div>

Mississippi elected one Democratic-Republican to the Nineteenth Congress. The Democratic-Republican was part of a faction led by Andrew Jackson.

The map for this election is incomplete due to the lack of returns in two counties.

Mississippi used a statewide at-large system for electing members to Congress. 

In 1826, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ms.uscongress.special.1826) was held in which William Haile was elected to replace Christopher Rankin, who had died. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
