---
meae-id: meae.congressional.congress13.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 13
congressordinal: 13th
title: '13th Congress: Delaware 1812'
year: 1812
legend: fed-vs-rep
nnv:
- id: de.uscongress.1812
  name: DE US Congress 1812 At Large
related-maps:
- id: meae.congressional.congress12.de.county
  name: DE 12th Congress
  type: previous
- id: meae.congressional.congress14.de.county
  name: DE 14th Congress
  type: next
#- id: meae.congressional.congress13.national.district
#  name: National 13th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress13.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Delaware elected two Federalist to the Thirteenth Congress.

Delaware was apportioned one more seat in the House of Representatives.

Delaware used a statewide at-large system for electing members to Congress. Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. Two at-large winners were elected.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
