---
meae-id: meae.congressional.congress19.ma.county
type: congressional
level: state
state: Massachusetts
geography: county
congressnum: 19
congressordinal: 19th
title: '19th Congress: Massachusetts 1824'
year: 1824
legend: congress-18-19
nnv:
- id: ma.uscongress.suffolk.1824
  name: MA US Congress 1824 District 1
- id: ma.uscongress.essexsouth.1824
  name: MA US Congress 1824 District 2
- id: ma.uscongress.essexnorth.ballot2.1825
  name: MA US Congress 1825 District 3
- id: ma.uscongress.middlesex.1824
  name: MA US Congress 1824 District 4
- id: ma.uscongress.worcestersouth.ballot4.1825
  name: MA US Congress 1825 District 5
- id: ma.uscongress.worcesternorth.1824
  name: MA US Congress 1824 District 6
- id: ma.uscongress.franklin.ballot2.1825
  name: MA US Congress 1825 District 7
- id: ma.uscongress.hampden.ballot3.1825
  name: MA US Congress 1825 District 8
- id: ma.uscongress.berkshire.1824
  name: MA US Congress 1824 District 9
- id: ma.uscongress.norfolk.ballot3.1825
  name: MA US Congress 1825 District 10
- id: ma.uscongress.plymouth.1824
  name: MA US Congress 1824 District 11
- id: ma.uscongress.bristol.ballot2.1825
  name: MA US Congress 1825 District 12
- id: ma.uscongress.barnstable.1824
  name: MA US Congress 1824 District 13
related-maps:
- id: meae.congressional.congress18.ma.county
  name: MA 18th Congress
  type: previous
#- id: meae.congressional.congress19.national.district
#  name: National 19th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress19.ma.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Massachusetts elected three Federalists and four Democratic-Republicans to the Nineteenth Congress. Three of those Democratic-Republicans were part of a faction led by John Quincy Adams and Henry Clay. In addition, five dissenting Federalists supported Adams and Clay, while one dissenting Federalist supported Andrew Jackson. As the Federalist Party declined in Massachusetts, many Federalists distanced themselves from the main party. Instead, their political affiliation more closely aligned with their choice of candidate for the 1824 presidential election.

Massachusetts used a district system for electing members to Congress. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
