---
meae-id: meae.congressional.congress05.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 5
congressordinal: 5th
title: '5th Congress: Delaware 1796'
year: 1796
legend: fed-vs-rep
nnv:
- id: de.uscongress.1796
  name: DE US Congress 1796 At Large
related-maps:
- id: meae.congressional.congress04.de.county
  name: DE 4th Congress
  type: previous
# - id: meae.congressional.congress06.de.county
#   name: DE 6th Congress
#   type: next
# - id: meae.congressional.congress05.national.district
#   name: National 5th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress05.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Delaware elected one Federalist to the Fifth Congress.

Delaware used a statewide at-large method for electing members to Congress. Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. The at-large winner was then declared the winner. This map depicts the initial winners.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
