---
meae-id: meae.congressional.congress06.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 6
congressordinal: 6th
title: '6th Congress: Delaware 1798'
year: 1798
legend: fed-vs-rep
nnv:
- id: de.uscongress.1798
  name: DE US Congress 1798 At Large
related-maps:
- id: meae.congressional.congress05.de.county
  name: DE 5th Congress
  type: previous
- id: meae.congressional.congress07.de.county
  name: DE 7th Congress
  type: next
# - id: meae.congressional.congress06.national.district
#   name: National 6th Congress
#   type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress06.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

Delaware elected one Federalist to the Sixth Congress.

Delaware used a statewide at-large method for electing members to Congress. Delaware’s election law required that voters select two candidates, with one residing in the voter’s own county, and the other residing in one of the state's other two counties. The at-large winner was then declared the winner.  This map depicts the initial winners.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
