---
meae-id: meae.congressional.congress01.de.county
type: congressional
level: state
state: Delaware
geography: county
congressnum: 1
congressordinal: 1st
title: '1st Congress: Delaware 1789'
year: 1789
legend: fed-vs-anti
nnv:
- id: de.uscongress.1789
  name: DE US Congress 1789 At Large
related-maps:
- id: meae.congressional.congress02.de.county
  name: DE 2nd Congress
  type: next
- id: meae.congressional.congress01.national.district
  name: National 1st Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress01.de.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "450px")
```

</div>

In this election, Delaware voters chose their one and only representative to the first U.S. House of Representatives. Unaffiliated representative John Vining beat out four other unaffiliated candidates in an at-large election in January 1789. According to Delaware election law, voters in each of the state's three counties were required to submit "on one ticket or piece of paper,” the names of two persons they wished to elect. Of these two persons, one was required to be an inhabitant of the voter’s own county and the other needed to be from a different country. The person who received the most votes overall would win the election.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>% 
  results_to_table() %>% 
  cat()
```

</div>
