---
meae-id: meae.congressional.congress18.va.county
type: congressional
level: state
state: Virginia
geography: county
congressnum: 18
congressordinal: 18th
title: '18th Congress: Virginia 1823'
year: 1823
legend: congress-18-19
nnv:
- id: va.congress.1.1823
  name: VA US Congress 1823 District 1
- id: va.congress.2.1823
  name: VA US Congress 1823 District 2
- id: va.congress.3.1823
  name: VA US Congress 1823 District 3
- id: va.congress.4.1823
  name: VA US Congress 1823 District 4
- id: va.congress.5.1823
  name: VA US Congress 1823 District 5
- id: va.congress.6.1823
  name: VA US Congress 1823 District 6
- id: va.congress.7.1823
  name: VA US Congress 1823 District 7
- id: va.congress.8.1823
  name: VA US Congress 1823 District 8
- id: va.congress.9.1823
  name: VA US Congress 1823 District 9
- id: va.congress.10.1823
  name: VA US Congress 1823 District 10
- id: va.congress.11.1823
  name: VA US Congress 1823 District 11
- id: va.congress.12.1823
  name: VA US Congress 1823 District 12
- id: va.congress.13.1823
  name: VA US Congress 1823 District 13
- id: va.congress.14.1823
  name: VA US Congress 1823 District 14
- id: va.congress.15.1823
  name: VA US Congress 1823 District 15
- id: va.congress.16.1823
  name: VA US Congress 1823 District 16
- id: va.congress.17.1823
  name: VA US Congress 1823 District 17
- id: va.congress.18.1823
  name: VA US Congress 1823 District 18
- id: va.congress.19.1823
  name: VA US Congress 1823 District 19
- id: va.congress.20.1823
  name: VA US Congress 1823 District 20
- id: va.congress.21.1823
  name: VA US Congress 1823 District 21
- id: va.congress.22.1823
  name: VA US Congress 1823 District 22
related-maps:
- id: meae.congressional.congress17.va.county
  name: VA 17th Congress
  type: previous
- id: meae.congressional.congress19.va.county
  name: VA 19th Congress
  type: next
- id: meae.congressional.congress18.national.county
  name: National 18th Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress18.va.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "550px", congress = 18)
```

</div>

Virginia elected one Federalist and twenty-one Democratic-Republicans to the Eighteenth Congress. Two of those Democratic-Republicans were part of a faction led by Andrew Jackson, one of the Democratic-Republicans was part of a faction led by John Quincy Adams and Henry Clay, and fourteen of the Democratic-Republicans were part of a faction led by William Crawford. 

The map for this election is incomplete due to the lack of returns in several counties.

Following the 1820 Census, Virginia lost one seat in the House of Representatives.

Virginia used a district system for electing members to Congress.

In 1824, a [special election](https://elections.lib.tufts.edu/catalog/tufts:va.special.uscongress.13.1824) was held in which John Taliaferro was elected to replace William Lee Ball, who had died.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
