---
meae-id: meae.congressional.congress17.pa.county
type: congressional
level: state
state: Pennsylvania
geography: county
congressnum: 17
congressordinal: 17th
title: '17th Congress: Pennsylvania 1820'
year: 1820
legend: fed-vs-rep
nnv:
- id: pa.congress.1.1820
  name: PA US Congress 1820 District 1
- id: pa.congress.2.1820
  name: PA US Congress 1820 District 2
- id: pa.congress.3.1820
  name: PA US Congress 1820 District 3
- id: pa.congress.4.1820
  name: PA US Congress 1820 District 4
- id: pa.congress.5.1820
  name: PA US Congress 1820 District 5
- id: pa.congress.6.1820
  name: PA US Congress 1820 District 6
- id: pa.congress.7.1820
  name: PA US Congress 1820 District 7
- id: pa.congress.8.1820
  name: PA US Congress 1820 District 8
- id: pa.congress.9.1820
  name: PA US Congress 1820 District 9
- id: pa.congress.10.1820
  name: PA US Congress 1820 District 10
- id: pa.congress.11.1820
  name: PA US Congress 1820 District 11
- id: pa.congress.12.1820
  name: PA US Congress 1820 District 12
- id: pa.congress.13.1820
  name: PA US Congress 1820 District 13
- id: pa.congress.14.1820
  name: PA US Congress 1820 District 14
- id: pa.congress.15.1820
  name: PA US Congress 1820 District 15
related-maps:
- id: meae.congressional.congress16.pa.county
  name: PA 16th Congress
  type: previous
- id: meae.congressional.congress18.pa.county
  name: PA 18th Congress
  type: next
#- id: meae.congressional.congress17.national.district
#  name: National 17th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress17.pa.county"

cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~demrep_percentage, ~federalist_vote, ~demrep_vote,
    "Philadelphia", 39.9526, -75.1652, 0.748, 0.252, 13415, 4515)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties(height = "500px", cities = 0, congress = 17) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                 fillColor = mappingelections:::poli_chrome(cities),
                 opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                 popup = ~paste0("<b>City of ", city, "</b><br/>",
                                 "Congressional District: 1<br/>",
                                 "Federalists: ", federalist_percentage * 100, "% (", 
                                 prettyNum(federalist_vote, big.mark = ","), 
                                 " votes)<br/>",
                                 "Democratic-Republicans: ", demrep_percentage * 100,
                                 "% (", 
                                 prettyNum(demrep_vote, big.mark = ","),
                                 " votes)"),
                 label = ~city) 
```

</div>

Pennsylvania elected ten Federalists and twelve Democratic-Republicans to the Seventeenth Congress. 

Mapping this election is incomplete because of the lack of local returns in many areas.

Pennsylvania used a district system for electing members to Congress. District 1 elected four representatives. Districts 2, 3, 5, 6, and 10 each elected two representatives. 

In 1821, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress.10.1821) was held in which Thomas Murray, Jr. was elected to replace William Cox Ellis, who had resigned from office. 

In 1821, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress.5.1821) was held in which John Findlay was elected to replace James Duncan, who had resigned from office. 

In 1822, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress.1.vacancy.1822) was held in which Thomas Forrest was elected to replace William Mimlnor, who had resigned from office. 

In 1822, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress.14.vacancy.1822) was held in which Walter Forward was elected to replace Henry Baldwin, who had resigned from office. 

In 1822, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress.6.vacancy.1822) was held in which Samuel D. Ingham was elected to replace Samuel Moore, who had resigned from office. 

In 1822, a [special election](https://elections.lib.tufts.edu/catalog/tufts:pa.congress.7.vacancy.1822) was held in which Daniel Udree was elected to replace Ludwig Worman, who had died. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
