---
meae-id: meae.congressional.congress01.md.county
type: congressional
level: state
state: Maryland
geography: county
congressnum: 1
congressordinal: 1st
title: '1st Congress: Maryland 1789'
year: 1789
legend_type: fed-vs-anti
nnv:
- id: md.uscongress.1789
  name: MD US Congress 1789 At Large
related-maps:
- id: meae.congressional.congress02.md.county
  name: MD 2nd Congress
  type: next
- id: meae.congressional.congress01.national.district
  name: National 1st Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress01.md.county"
cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~antifederalist_percentage, ~federalist_vote, ~antifederalist_vote,
  "Annapolis", 38.97228, -76.50640, 0.538, 0.462, 731, 627,
  "Baltimore", 39.30021, -76.61052, 0.620, 0.380, 3128, 1920
)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>% 
  map_counties(height = "425px", cities = FALSE) %>% 
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                   fillColor = mappingelections:::poli_chrome(cities),
                   opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                   popup = ~paste0("<b>City of ", city, "</b><br/>",
                                   "Congressional District: At-large<br/>",
                                   "Federalists: ", federalist_percentage * 100, "% (", 
                                   prettyNum(federalist_vote, big.mark = ","), 
                                   " votes)<br/>",
                                   "Anti-Federalists: ", antifederalist_percentage * 100,
                                   "% (", 
                                   prettyNum(antifederalist_vote, big.mark = ","),
                                   " votes)"),
                   label = ~city) 
```

</div>

Votes tallied for the cities of Baltimore and Annapolis are shown separately, and they are in addition to the votes reported for Baltimore County and Anne Arundel County.

Like many states in the early republic, Maryland experimented with voting procedures that were intended to ensure democratic representation. For the first and second Congress, "candidates were elected at-large but had to be residents of a specific district with the statewide vote determining winners from each district." Both the Federalists and the Anti-Federalists advanced six candidates each who met the residency requirements. The state of Maryland was heavily Federalist, and so six Federalists received the most votes in the at-large state election and were thus elected. But one of those candidates represented a district which contained Baltimore County, and another represented a district which contained Anne Arundel County and Annapolis. Had the voting been tallied district by district, the district containing Baltimore County would have had a narrow majority for Anti-Federalists, and the district containing Anne Arundel County would have been within 50 votes of an Anti-Federalist majority. The process of at-large elections with residency requirements thus had the unintended effect of solidifying state-wide rather than more local majorities. 

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table(keep_percentage = 0.005) %>%
  cat()
```

</div>
