---
meae-id: meae.congressional.congress13.ga.county
type: congressional
level: state
state: Georgia
geography: county
congressnum: 13
congressordinal: 13th
title: '13th Congress: Georgia 1812'
year: 1812
legend: fed-vs-rep
nnv:
- id: ga.uscongress.1812
  name: GA US Congress 1812 At Large
related-maps:
- id: meae.congressional.congress12.ga.county
  name: GA 12th Congress
  type: previous
- id: meae.congressional.congress14.ga.county
  name: GA 14th Congress
  type: next
#- id: meae.congressional.congress13.national.district
#  name: National 13th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress13.ga.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  filter(id != "gas_nca") %>% 
  map_counties(height = "525px")
```

</div>

Georgia elected six Democratic-Republicans to the Thirteenth Congress.

The map for this election is incomplete due to the lack of returns for Twiggs County.

Following the 1810 Census, Georgia gained two more seats in the House of Representatives.

Georgia used a statewide at-large system for electing members to Congress.

In 1813, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ga.uscongress.special.1813) was held in which Alfred Cuthbert was elected to replace William W. Bibb, who had resigned from office.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
