---
meae-id: meae.congressional.congress13.ma.county
type: congressional
level: state
state: Massachusetts
geography: county
congressnum: 13
congressordinal: 13th
title: '13th Congress: Massachusetts 1812'
year: 1812
legend: fed-vs-rep
nnv:
- id: ma.uscongress.suffolk.1812
  name: MA US Congress 1812 District 1
- id: ma.uscongress.essexsouth.1812
  name: MA US Congress 1812 District 2
- id: ma.uscongress.essexnorth.1812
  name: MA US Congress 1812 District 3
- id: ma.uscongress.middlesex.1812
  name: MA US Congress 1812 District 4
- id: ma.uscongress.hampshiresouth.1812
  name: MA US Congress 1812 District 5
- id: ma.uscongress.hampshirenorth.1812
  name: MA US Congress 1812 District 6
- id: ma.uscongress.plymouth.1812
  name: MA US Congress 1812 District 7
- id: ma.uscongress.barnstable.1812
  name: MA US Congress 1812 District 8
- id: ma.uscongress.bristol.1812
  name: MA US Congress 1812 District 9
- id: ma.uscongress.worcestersouth.1812
  name: MA US Congress 1812 District 10
- id: ma.uscongress.worcesternorth.1812
  name: MA US Congress 1812 District 11
- id: ma.uscongress.berkshire.1812
  name: MA US Congress 1812 District 12
- id: ma.uscongress.norfolk.1812
  name: MA US Congress 1812 District 13
- id: ma.uscongress.eastern1.1812
  name: MA US Congress 1812 District 14
- id: ma.uscongress.eastern2.1812
  name: MA US Congress 1812 District 15
- id: ma.uscongress.eastern3.1812
  name: MA US Congress 1812 District 16
- id: ma.uscongress.eastern4.1812
  name: MA US Congress 1812 District 17
- id: ma.uscongress.eastern5.1812
  name: MA US Congress 1812 District 18
- id: ma.uscongress.eastern6.ballot2.1813
  name: MA US Congress 1813 District 19
- id: ma.uscongress.eastern7.1812
  name: MA US Congress 1812 District 20
related-maps:
- id: meae.congressional.congress12.ma.county
  name: MA 12th Congress
  type: previous
- id: meae.congressional.congress14.ma.county
  name: MA 14th Congress
  type: next
#- id: meae.congressional.congress13.national.district
#  name: National 13th Congress
#  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show

---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress13.ma.county"
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>%
  map_counties() %>% 
  fitBounds(-73.508, 41.186, -69.861, 43.75)
```

</div>

Massachusetts elected sixteen Federalists and four Democratic-Republicans to the Thirteenth Congress.

Following the 1810 Census, Massachusetts gained three more seats in the House of Representatives.

Massachusetts used a district system for electing members to Congress. 

In 1814, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.berkshire.special.1814) was held in which John W. Hulbert was elected to replace Daniel Dewey, who had resigned. 

In 1814, a [special election](https://elections.lib.tufts.edu/catalog/tufts:ma.uscongress.middlesex.special.1814) was held in which Samuel Dana was elected to replace William M. Richardson, who had resigned.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table() %>%
  cat()
```

</div>
