---
meae-id: meae.congressional.congress01.md.county
type: congressional
level: state
state: Maryland
geography: county
congressnum: 1
congressordinal: 1st
title: '1st Congress: Maryland 1789'
year: 1789
legend: fed-vs-anti
nnv:
- id: md.uscongress.1789
  name: MD US Congress 1789 At Large
related-maps:
- id: meae.congressional.congress02.md.county
  name: MD 2nd Congress
  type: next
- id: meae.congressional.congress01.national.county
  name: National 1st Congress
  type: national
output:
  md_document:
    variant: markdown
  html_document:
    theme: default
always_allow_html: yes
layout: maps-show
---

```{r setup, include = FALSE}
library(leaflet)
library(tidyverse)
library(USAboundaries)
library(mappingelections)

map_id <- "meae.congressional.congress01.md.county"
cities <- tribble(
  ~city, ~lat, ~lng, ~federalist_percentage, ~antifederalist_percentage, ~federalist_vote, ~antifederalist_vote,
  "Annapolis", 38.97228, -76.50640, 0.538, 0.462, 731, 627,
  "Baltimore", 39.30021, -76.61052, 0.620, 0.380, 3128, 1920
)
```

<div class="map">

```{r election-map, echo = FALSE}
map_id %>%
  get_county_map_data() %>% 
  map_counties(height = "450px", cities = FALSE) %>%
  addCircleMarkers(data = cities, lat = ~lat, lng = ~lng, color = "black",
                   fillColor = mappingelections:::poli_chrome(cities),
                   opacity = 1, fillOpacity = 0.8, radius = 8, weight = 3,
                   popup = ~paste0("<b>City of ", city, "</b><br/>",
                                   "Congressional District: At-large<br/>",
                                   "Federalists: ", federalist_percentage * 100, "% (", 
                                   prettyNum(federalist_vote, big.mark = ","), 
                                   " votes)<br/>",
                                   "Anti-Federalists: ", antifederalist_percentage * 100,
                                   "% (", 
                                   prettyNum(antifederalist_vote, big.mark = ","),
                                   " votes)"),
                   label = ~city) 
```

</div>

Maryland elected six Federalists to the First Congress. The Federalists swept the election with a large margin of victory.

Maryland used a state-wide at-large system to elect members of Congress. Candidates had to be residents of a specific Congressional district. 

Votes tallied for the cities of Baltimore and Annapolis are shown separately, and they are in addition to the votes reported for Baltimore County and Anne Arundel County.

<div class="results-table">

```{r election-results, echo = FALSE, results='asis'}
map_id %>%
  candidate_results() %>%
  results_to_table(keep_percentage = 0.005) %>%
  cat()
```

</div>
